---
title: "CS Structure in Single-Gene Regions (LDL)"
author: "Xinhe Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/project/xinhe/xsun/multi_group_ctwas/23.multi_group_0515/")
library(ctwas)
library(data.table)
library(DT)
library(ggplot2)
```

## Overview

For regions reporting exactly one gene (combined_pip > 0.8), we examine the credible set (CS) structure to understand the number and nature of independent signals supporting that gene.

- **Case 1**: Multiple CS, but supporting the same gene. Multiple independent molecular signals converge on the same gene.
- **Case 2**: Multiple CS, some CS supports the gene, others are variants (SNP-only).
- **Case 3**: Multiple CS, some support the gene, some support other genes (but with combined PIP < 0.8), and others are variants if there are others.
- **Case 4**: No CS. Genes achieve high combined PIP by accumulating small contributions across multiple sets without entering any single credible set.
- **Case 5**: Single CS.

## Load data and combine gene PIPs

```{r load_data}
trait <- "LDL-ukb-d-30780_irnt"
folder_results <- "snakemake_outputs/"

mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
mapping_munro <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
mapping_ed <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/mapping_edqtl.RDS")
mapping_all <- rbind(mapping_predictdb, mapping_munro, mapping_ed)
mapping_dt <- as.data.table(mapping_all)

finemap_res <- readRDS(paste0(folder_results, trait, "/", trait, ".3qtls.thin1.shared_all.L5.regionmerge_with_mappingtable_finemap_res.RDS"))
susie_alpha_res <- readRDS(paste0(folder_results, trait, "/", trait, ".3qtls.thin1.shared_all.L5.regionmerge_with_mappingtable_susie_alpha_res.RDS"))
```

```{r combine_pip}
ctwas_gene_anno <- anno_susie_alpha_res(
  susie_alpha_res,
  mapping_table = mapping_all,
  map_by = "molecular_id",
  drop_unmapped = TRUE
)

gene_pip_df <- combine_gene_pips(
  ctwas_gene_anno,
  group_by = "gene_name",
  by = "type",
  method = "combine_cs",
  filter_cs = FALSE,
  include_cs_id = TRUE,
  include_set_id = TRUE
)

set_ids <- gene_pip_df$combined_set_id
first_set <- sub(",.*$", "", set_ids)
gene_pip_df$region_id <- sub("\\.L[0-9]+$", "", first_set)
```

## Identify single-gene regions

```{r single_gene_regions}
sig_genes <- gene_pip_df[gene_pip_df$combined_pip > 0.8, ]
sig_dt <- as.data.table(sig_genes)
genes_per_region <- sig_dt[, .(n_genes = uniqueN(gene_name)), by = region_id]

cat("Total genes with combined_pip > 0.8:", nrow(sig_genes), "\n")
cat("Total regions with significant genes:", nrow(genes_per_region), "\n")
```

```{r gene_per_region_table}
knitr::kable(as.data.frame(table(genes_per_region$n_genes)),
             col.names = c("Genes per region", "Number of regions"),
             caption = "Distribution of significant genes per region")
```

```{r}
single_gene_regions <- genes_per_region[n_genes == 1]
cat("Single-gene regions:", nrow(single_gene_regions), "\n")
```

## Analyze CS structure in single-gene regions

```{r analyze_cs}
finemap_dt <- as.data.table(finemap_res)

results <- list()

for (i in seq_len(nrow(single_gene_regions))) {
  rid <- single_gene_regions$region_id[i]
  gene_name_val <- sig_dt[region_id == rid, unique(gene_name)]

  region_fm <- finemap_dt[region_id == rid]
  region_cs <- region_fm[!is.na(cs)]

  if (nrow(region_cs) == 0) {
    results[[i]] <- list(
      region_id = rid, gene_name = gene_name_val,
      n_cs = 0L, n_cs_mol = 0L, n_cs_snp = 0L,
      n_cs_sig = 0L, n_cs_other_gene = 0L,
      max_mol_pip = NA_real_, all_mol_below_08 = NA,
      case = "case4_no_cs", cs_details = ""
    )
    next
  }

  ucs <- unique(region_cs$cs)
  n_cs <- length(ucs)

  # Classify each CS: SNP-only, mol for sig gene, or mol for other gene
  cs_type <- sapply(ucs, function(cv) {
    ents <- region_cs[cs == cv]
    mol <- ents[type != "SNP"]
    if (nrow(mol) == 0) return("snp_only")
    mol_ids <- unique(mol$molecular_id)
    mapped_genes <- unique(mapping_dt[molecular_id %in% mol_ids, gene_name])
    if (gene_name_val %in% mapped_genes) return("sig_gene")
    return("other_gene")
  })

  n_cs_snp <- sum(cs_type == "snp_only")
  n_cs_sig <- sum(cs_type == "sig_gene")
  n_cs_other_gene <- sum(cs_type == "other_gene")
  n_cs_mol <- n_cs_sig + n_cs_other_gene

  details <- sapply(ucs, function(cv) {
    ents <- region_cs[cs == cv]
    mol <- ents[type != "SNP"]
    if (nrow(mol) > 0) {
      types_found <- unique(mol$type)
      contexts_found <- unique(mol$context)
      mol_ids <- unique(mol$molecular_id)
      mapped_genes <- unique(mapping_dt[molecular_id %in% mol_ids, gene_name])
      gene_str <- paste(mapped_genes, collapse = ", ")
      paste0(cv, ": ", paste(types_found, collapse = "/"),
             " (", paste(contexts_found, collapse = ", "),
             ") [genes: ", gene_str, "]")
    } else {
      paste0(cv, ": SNP-only (n=", nrow(ents), ")")
    }
  })

  # Max mol PIP for traits mapping to sig gene only
  mol_entries_sig <- region_cs[type != "SNP"]
  if (nrow(mol_entries_sig) > 0) {
    sig_mol_ids <- mapping_dt[gene_name == gene_name_val, unique(molecular_id)]
    mol_for_sig <- mol_entries_sig[molecular_id %in% sig_mol_ids]
    if (nrow(mol_for_sig) > 0) {
      max_mol_pip <- max(mol_for_sig$susie_pip)
      all_mol_below_08 <- all(mol_for_sig$susie_pip < 0.8)
    } else {
      max_mol_pip <- NA_real_
      all_mol_below_08 <- NA
    }
  } else {
    max_mol_pip <- NA_real_
    all_mol_below_08 <- NA
  }

  if (n_cs == 1) {
    cl <- "case5_single_cs"
  } else if (n_cs_sig > 1) {
    cl <- "case1_multi_cs_same_gene"
  } else if (n_cs_sig == 1 & n_cs_other_gene > 0) {
    cl <- "case3_sig_gene_plus_other_genes"
  } else if (n_cs_sig == 1 & n_cs_other_gene == 0 & n_cs_snp >= 1) {
    cl <- "case2_one_cs_gene_rest_snp"
  } else if (n_cs_sig == 0) {
    cl <- "case4_no_cs"
  } else {
    cl <- "other"
  }

  results[[i]] <- list(
    region_id = rid, gene_name = gene_name_val,
    n_cs = n_cs, n_cs_mol = n_cs_mol, n_cs_snp = n_cs_snp,
    n_cs_sig = n_cs_sig, n_cs_other_gene = n_cs_other_gene,
    max_mol_pip = max_mol_pip, all_mol_below_08 = all_mol_below_08,
    case = cl, cs_details = paste(details, collapse = " | ")
  )
}

results_df <- rbindlist(results)
```

## Summary

```{r summary_table}
case_labels <- c(
  "case1_multi_cs_same_gene" = "Case 1: Multiple CS, supporting same gene",
  "case2_one_cs_gene_rest_snp" = "Case 2: Multiple CS, gene + variants",
  "case3_sig_gene_plus_other_genes" = "Case 3: Multiple CS, gene + other genes (+variants)",
  "case4_no_cs" = "Case 4: No CS",
  "case5_single_cs" = "Case 5: Single CS"
)

case_order <- c("case1_multi_cs_same_gene", "case2_one_cs_gene_rest_snp",
                "case3_sig_gene_plus_other_genes", "case4_no_cs", "case5_single_cs")

case_counts <- as.data.frame(table(factor(results_df$case, levels = case_order)))
colnames(case_counts) <- c("Case", "Count")
case_counts$Description <- case_labels[as.character(case_counts$Case)]
case_counts <- case_counts[, c("Case", "Description", "Count")]

knitr::kable(case_counts, row.names = FALSE,
             caption = "Breakdown of CS structure in single-gene regions")
```

```{r summary_plot, fig.width=8, fig.height=4}
plot_df <- results_df[, .(count = .N), by = case]
plot_df[, label := case_labels[case]]
label_order <- case_labels[case_order]
plot_df[, label := factor(label, levels = rev(label_order))]

ggplot(plot_df, aes(x = label, y = count, fill = label)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = count), hjust = -0.2, size = 4) +
  coord_flip() +
  labs(x = "", y = "Number of regions", title = paste0(trait, ": CS structure in single-gene regions")) +
  theme_minimal(base_size = 14) +
  theme(axis.text.y = element_text(color = "black")) +
  ylim(0, max(plot_df$count) * 1.15)
```

## Case 1: Multiple CS, supporting the same gene

These regions have multiple CS, and more than one CS supports molecular traits mapping to the same significant gene (e.g., eQTL in one tissue/CS, sQTL in another CS).

```{r case1_table}
c1 <- results_df[case == "case1_multi_cs_same_gene",
                 .(Gene = gene_name, Region = region_id,
                   `Total CS` = n_cs, `CS Sig Gene` = n_cs_sig,
                   `CS Other Gene` = n_cs_other_gene, `CS SNP` = n_cs_snp,
                   `Max Mol PIP` = max_mol_pip, `All Mol PIP < 0.8` = all_mol_below_08,
                   `CS Details` = cs_details)]
DT::datatable(c1, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 1: Multiple CS supporting the same gene")
```

### Case 1 sub-classification: individual PIP check

For Case 1 genes, we check whether all individual molecular trait PIPs (susie_pip) are below 0.8 before combining. Genes where all individual PIPs < 0.8 are truly "multi-signal" — they only reach significance by combining evidence across multiple independent credible sets. Genes where at least one molecular trait already has PIP >= 0.8 would have been identified even without combining.

```{r case1_subclass}
c1_res <- results_df[case == "case1_multi_cs_same_gene"]

cat("Case 1 genes where ALL individual molecular PIPs < 0.8:", sum(c1_res$all_mol_below_08, na.rm = TRUE), "\n")
cat("Case 1 genes where some individual molecular PIP >= 0.8:", sum(!c1_res$all_mol_below_08, na.rm = TRUE), "\n")
```

#### Case 1a: All individual molecular PIPs < 0.8 (truly multi-signal)

These genes only reach combined_pip > 0.8 by aggregating evidence across multiple CS — no single molecular trait is individually significant.

```{r case1a_table}
c1a <- results_df[case == "case1_multi_cs_same_gene" & all_mol_below_08 == TRUE,
                  .(Gene = gene_name, Region = region_id,
                    `Total CS` = n_cs, `Mol CS` = n_cs_mol,
                    `Max Mol PIP` = round(max_mol_pip, 4),
                    `CS Details` = cs_details)]

c1a <- merge(c1a, sig_dt[, .(gene_name, combined_pip)],
             by.x = "Gene", by.y = "gene_name", all.x = TRUE)
setnames(c1a, "combined_pip", "Combined PIP")
c1a[, `Combined PIP` := round(`Combined PIP`, 4)]

DT::datatable(c1a, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 1a: All individual molecular PIPs < 0.8")
```

#### Case 1b: At least one individual molecular PIP >= 0.8

These genes already have at least one molecular trait with high individual PIP — the multi-CS structure provides additional support but is not required for identification.

```{r case1b_table}
c1b <- results_df[case == "case1_multi_cs_same_gene" & all_mol_below_08 == FALSE,
                  .(Gene = gene_name, Region = region_id,
                    `Total CS` = n_cs, `Mol CS` = n_cs_mol,
                    `Max Mol PIP` = round(max_mol_pip, 4),
                    `CS Details` = cs_details)]

c1b <- merge(c1b, sig_dt[, .(gene_name, combined_pip)],
             by.x = "Gene", by.y = "gene_name", all.x = TRUE)
setnames(c1b, "combined_pip", "Combined PIP")
c1b[, `Combined PIP` := round(`Combined PIP`, 4)]

DT::datatable(c1b, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 1b: At least one molecular PIP >= 0.8")
```

### Case 1 details

```{r case1_details, results='asis'}
c1_df <- results_df[case == "case1_multi_cs_same_gene"]

for (j in seq_len(nrow(c1_df))) {
  rid <- c1_df$region_id[j]
  gn <- c1_df$gene_name[j]

  cat(sprintf("\n#### %s (region: %s)\n\n", gn, rid))

  region_fm <- finemap_dt[region_id == rid & !is.na(cs)]
  mol_entries <- region_fm[type != "SNP", .(id, type, context, group, cs, susie_pip, z)]
  mol_entries <- mol_entries[order(cs, -susie_pip)]

  if (nrow(mol_entries) > 0) {
    print(knitr::kable(mol_entries, digits = 4,
                       caption = paste0("Molecular traits in CS for ", gn)))
    cat("\n")
  }
}
```

## Case 2: Multiple CS, gene + variants

These regions have multiple CS. Some CS support the significant gene's molecular traits, while the others contain only SNP variants.

```{r case2_table}
c2 <- results_df[case == "case2_one_cs_gene_rest_snp",
                 .(Gene = gene_name, Region = region_id,
                   `Total CS` = n_cs, `Mol CS` = n_cs_mol, `SNP CS` = n_cs_snp,
                   `CS Details` = cs_details)]
DT::datatable(c2, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 2: One CS with molecular traits, rest SNP-only")
```

### Case 2 details

```{r case2_details, results='asis'}
c2_df <- results_df[case == "case2_one_cs_gene_rest_snp"]

for (j in seq_len(nrow(c2_df))) {
  rid <- c2_df$region_id[j]
  gn <- c2_df$gene_name[j]

  cat(sprintf("\n#### %s (region: %s)\n\n", gn, rid))

  region_fm <- finemap_dt[region_id == rid & !is.na(cs)]

  # Molecular traits CS
  mol_entries <- region_fm[type != "SNP", .(id, type, context, group, cs, susie_pip, z)]
  mol_entries <- mol_entries[order(cs, -susie_pip)]

  if (nrow(mol_entries) > 0) {
    cat("**Molecular traits in CS:**\n\n")
    print(knitr::kable(mol_entries, digits = 4))
    cat("\n")
  }

  # SNP-only CS summary
  snp_cs <- region_fm[type == "SNP"]
  snp_cs_summary <- snp_cs[, .(`N SNPs` = .N,
                                `Max PIP` = max(susie_pip),
                                `Max |z|` = max(abs(z))), by = cs]
  snp_cs_summary <- snp_cs_summary[!snp_cs_summary$cs %in% mol_entries$cs]

  if (nrow(snp_cs_summary) > 0) {
    cat("**SNP-only CS:**\n\n")
    print(knitr::kable(snp_cs_summary, digits = 4))
    cat("\n")
  }
}
```

## Case 3: Multiple CS, gene + other genes (+variants)

These regions have multiple CS. Some CS support the significant gene's molecular traits, some CS contain molecular traits mapping to other genes (with combined PIP < 0.8), and the remaining CS (if any) are SNP-only variants.

```{r case3_table}
c3 <- results_df[case == "case3_sig_gene_plus_other_genes",
                 .(Gene = gene_name, Region = region_id,
                   `Total CS` = n_cs, `CS Sig Gene` = n_cs_sig,
                   `CS Other Gene` = n_cs_other_gene, `CS SNP` = n_cs_snp,
                   `CS Details` = cs_details)]
DT::datatable(c3, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 3: Sig gene CS + other gene CS")
```

### Case 3 details

```{r case3_details, results='asis'}
c3_df <- results_df[case == "case3_sig_gene_plus_other_genes"]

for (j in seq_len(nrow(c3_df))) {
  rid <- c3_df$region_id[j]
  gn <- c3_df$gene_name[j]

  cat(sprintf("\n#### %s (region: %s)\n\n", gn, rid))

  region_fm <- finemap_dt[region_id == rid & !is.na(cs)]

  # Molecular traits mapping to sig gene
  sig_mol_ids <- mapping_dt[gene_name == gn, unique(molecular_id)]
  mol_sig <- region_fm[type != "SNP" & molecular_id %in% sig_mol_ids,
                       .(id, type, context, cs, susie_pip, z)]
  mol_sig <- mol_sig[order(cs, -susie_pip)]

  if (nrow(mol_sig) > 0) {
    cat(sprintf("**Molecular traits mapping to %s:**\n\n", gn))
    print(knitr::kable(mol_sig, digits = 4))
    cat("\n")
  }

  # Molecular traits mapping to other genes
  mol_other <- region_fm[type != "SNP" & !molecular_id %in% sig_mol_ids,
                         .(id, molecular_id, type, context, cs, susie_pip, z)]
  if (nrow(mol_other) > 0) {
    mol_other_mapped <- merge(mol_other,
                              unique(mapping_dt[, .(molecular_id, gene_name)]),
                              by = "molecular_id", all.x = TRUE)
    mol_other_mapped <- mol_other_mapped[, .(id, gene_name, type, context, cs, susie_pip, z)]
    mol_other_mapped <- mol_other_mapped[order(cs, -susie_pip)]

    cat("**Molecular traits mapping to other genes:**\n\n")
    print(knitr::kable(mol_other_mapped, digits = 4))
    cat("\n")
  }

  # SNP-only CS summary
  snp_cs <- region_fm[type == "SNP"]
  all_mol_cs <- unique(region_fm[type != "SNP", cs])
  snp_only_cs <- snp_cs[!cs %in% all_mol_cs]
  if (nrow(snp_only_cs) > 0) {
    snp_cs_summary <- snp_only_cs[, .(`N SNPs` = .N,
                                       `Max PIP` = max(susie_pip),
                                       `Max |z|` = max(abs(z))), by = cs]
    cat("**SNP-only CS:**\n\n")
    print(knitr::kable(snp_cs_summary, digits = 4))
    cat("\n")
  }
}
```

## Case 4: No CS

Genes with combined_pip > 0.8 but no CS membership in the finemap result. These genes achieve high combined PIP by accumulating small contributions across multiple sets without entering any single credible set.

```{r case4_table}
c4 <- results_df[case == "case4_no_cs",
                 .(Gene = gene_name, Region = region_id)]

c4_pip <- merge(c4, sig_dt[, .(gene_name, combined_pip, eQTL_pip, sQTL_pip, stQTL_pip)],
                by.x = "Gene", by.y = "gene_name", all.x = TRUE)

DT::datatable(c4_pip, options = list(pageLength = 20, scrollX = TRUE),
              caption = "Case 4: No CS — gene PIP breakdown")
```

## Case 5: Single CS

Regions where only one credible set exists.

```{r case5_table}
c5 <- results_df[case == "case5_single_cs",
                 .(Gene = gene_name, Region = region_id,
                   `CS Details` = cs_details)]
DT::datatable(c5, options = list(pageLength = 50, scrollX = TRUE),
              caption = "Case 5: Single CS regions")
```

## Full results table

```{r full_table}
full_tbl <- results_df[, .(Gene = gene_name, Region = region_id,
                            Case = case, `Total CS` = n_cs,
                            `CS Sig Gene` = n_cs_sig, `CS Other Gene` = n_cs_other_gene,
                            `CS SNP` = n_cs_snp,
                            `Max Mol PIP` = round(max_mol_pip, 4),
                            `All Mol PIP < 0.8` = all_mol_below_08)]
full_tbl <- merge(full_tbl,
                  sig_dt[, .(gene_name, combined_pip)],
                  by.x = "Gene", by.y = "gene_name", all.x = TRUE)
setnames(full_tbl, "combined_pip", "Combined PIP")
full_tbl <- full_tbl[order(Case, -`Combined PIP`)]

DT::datatable(full_tbl, options = list(pageLength = 80, scrollX = TRUE),
              caption = "All single-gene regions with CS structure")
```
