---
title: "CS Structure in Single-Gene Regions — All Traits"
author: "Xinhe Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/project/xinhe/xsun/multi_group_ctwas/23.multi_group_0515/")
library(ctwas)
library(data.table)
library(DT)
library(ggplot2)
```

## Overview

For regions reporting exactly one gene (combined_pip > 0.8), we examine the credible set (CS) structure across all traits. Each CS is classified by whether its molecular traits map to the significant gene, a different gene, or SNP-only.

- **Case 1**: Multiple CS, but supporting the same gene.
- **Case 2**: Multiple CS, some CS supports the gene, others are variants.
- **Case 3**: Multiple CS, some support the gene, some support other genes (but with combined PIP < 0.8), and others are variants if there are others.
- **Case 4**: No CS.
- **Case 5**: Single CS.

## Load mapping tables

```{r load_mapping}
mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
mapping_munro <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
mapping_ed <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/mapping_edqtl.RDS")
mapping_all <- rbind(mapping_predictdb, mapping_munro, mapping_ed)
mapping_dt <- as.data.table(mapping_all)
```

## Define analysis function

```{r define_function}
folder_results <- "snakemake_outputs/"

analyze_trait_cs <- function(trait, mapping_dt, folder_results) {
  base <- file.path(folder_results, trait, paste0(trait, ".3qtls.thin1.shared_all.L5"))

  file_finemap_ldmismatch  <- paste0(base, ".ldmismatch_with_mappingtable_noLD_finemap_regions_res.RDS")
  file_finemap_regionmerge <- paste0(base, ".regionmerge_with_mappingtable_finemap_res.RDS")
  file_finemap_original    <- paste0(base, ".finemap_regions_res.RDS")

  file_alpha_ldmismatch  <- paste0(base, ".ldmismatch_with_mappingtable_noLD_susie_alpha_res.RDS")
  file_alpha_regionmerge <- paste0(base, ".regionmerge_with_mappingtable_susie_alpha_res.RDS")
  file_alpha_original    <- paste0(base, ".finemap_regions_res.RDS")

  if (file.exists(file_finemap_ldmismatch)) {
    finemap_res <- readRDS(file_finemap_ldmismatch)
  } else if (file.exists(file_finemap_regionmerge)) {
    finemap_res <- readRDS(file_finemap_regionmerge)
  } else if (file.exists(file_finemap_original)) {
    raw <- readRDS(file_finemap_original)
    finemap_res <- if (!is.null(raw$finemap_res)) raw$finemap_res else raw
  } else {
    return(NULL)
  }

  if (file.exists(file_alpha_ldmismatch)) {
    susie_alpha_res <- readRDS(file_alpha_ldmismatch)
  } else if (file.exists(file_alpha_regionmerge)) {
    susie_alpha_res <- readRDS(file_alpha_regionmerge)
  } else if (file.exists(file_alpha_original)) {
    raw <- readRDS(file_alpha_original)
    susie_alpha_res <- if (!is.null(raw$susie_alpha_res)) raw$susie_alpha_res else return(NULL)
  } else {
    return(NULL)
  }

  finemap_dt <- as.data.table(finemap_res)

  ctwas_gene_anno <- anno_susie_alpha_res(
    susie_alpha_res,
    mapping_table = mapping_dt,
    map_by = "molecular_id",
    drop_unmapped = TRUE
  )

  gene_pip_df <- combine_gene_pips(
    ctwas_gene_anno,
    group_by = "gene_name",
    by = "type",
    method = "combine_cs",
    filter_cs = FALSE,
    include_cs_id = TRUE,
    include_set_id = TRUE
  )

  set_ids <- gene_pip_df$combined_set_id
  first_set <- sub(",.*$", "", set_ids)
  gene_pip_df$region_id <- sub("\\.L[0-9]+$", "", first_set)

  sig_genes <- gene_pip_df[gene_pip_df$combined_pip > 0.8, ]
  if (nrow(sig_genes) == 0) return(NULL)

  sig_dt <- as.data.table(sig_genes)
  genes_per_region <- sig_dt[, .(n_genes = uniqueN(gene_name)), by = region_id]
  single_gene_regions <- genes_per_region[n_genes == 1]

  if (nrow(single_gene_regions) == 0) return(NULL)

  results <- list()

  for (i in seq_len(nrow(single_gene_regions))) {
    rid <- single_gene_regions$region_id[i]
    gene_name_val <- sig_dt[region_id == rid, unique(gene_name)]

    region_fm <- finemap_dt[region_id == rid]
    region_cs <- region_fm[!is.na(cs)]

    if (nrow(region_cs) == 0) {
      results[[i]] <- data.table(
        trait = trait, region_id = rid, gene_name = gene_name_val,
        n_cs = 0L, n_cs_sig = 0L, n_cs_other_gene = 0L, n_cs_snp = 0L,
        case = "case4_no_cs"
      )
      next
    }

    ucs <- unique(region_cs$cs)
    n_cs <- length(ucs)

    cs_type <- sapply(ucs, function(cv) {
      ents <- region_cs[cs == cv]
      mol <- ents[type != "SNP"]
      if (nrow(mol) == 0) return("snp_only")
      mol_ids <- unique(mol$molecular_id)
      mapped_genes <- unique(mapping_dt[molecular_id %in% mol_ids, gene_name])
      if (gene_name_val %in% mapped_genes) return("sig_gene")
      return("other_gene")
    })

    n_cs_snp <- sum(cs_type == "snp_only")
    n_cs_sig <- sum(cs_type == "sig_gene")
    n_cs_other_gene <- sum(cs_type == "other_gene")

    if (n_cs == 1) {
      cl <- "case5_single_cs"
    } else if (n_cs_sig > 1) {
      cl <- "case1_multi_cs_same_gene"
    } else if (n_cs_sig == 1 & n_cs_other_gene > 0) {
      cl <- "case3_sig_gene_plus_other_genes"
    } else if (n_cs_sig == 1 & n_cs_other_gene == 0 & n_cs_snp >= 1) {
      cl <- "case2_one_cs_gene_rest_snp"
    } else if (n_cs_sig == 0) {
      cl <- "case4_no_cs"
    } else {
      cl <- "other"
    }

    results[[i]] <- data.table(
      trait = trait, region_id = rid, gene_name = gene_name_val,
      n_cs = n_cs, n_cs_sig = n_cs_sig, n_cs_other_gene = n_cs_other_gene,
      n_cs_snp = n_cs_snp, case = cl
    )
  }

  rbindlist(results)
}
```

## Run analysis for all traits

```{r run_all_traits}
all_traits <- c(
  "LDL-ukb-d-30780_irnt",
  "IBD-ebi-a-GCST004131",
  "aFib-ebi-a-GCST006414",
  "SBP-ukb-a-360",
  "T1D-GCST90014023",
  "T2D-panukb",
  "ATH_gtexukb",
  "BMI-panukb",
  "HB-panukb",
  "Height-panukb",
  "HTN-panukb",
  "PLT-panukb",
  "RBC-panukb",
  "WBC-ieu-b-30",
  "SCZ-ieu-b-5102"
)

all_results <- list()
for (trait in all_traits) {
  cat("Processing:", trait, "\n")
  res <- analyze_trait_cs(trait, mapping_dt, folder_results)
  if (!is.null(res)) all_results[[trait]] <- res
}

all_results_df <- rbindlist(all_results)

cat("\nTraits processed:", length(all_results), "\n")
cat("Total single-gene regions across all traits:", nrow(all_results_df), "\n")
```

## Summary across all traits

```{r case_labels}
case_labels <- c(
  "case1_multi_cs_same_gene" = "Case 1: Multiple CS, supporting same gene",
  "case2_one_cs_gene_rest_snp" = "Case 2: Multiple CS, gene + variants",
  "case3_sig_gene_plus_other_genes" = "Case 3: Multiple CS, gene + other genes (+variants)",
  "case4_no_cs" = "Case 4: No CS",
  "case5_single_cs" = "Case 5: Single CS"
)

case_order <- c("case1_multi_cs_same_gene", "case2_one_cs_gene_rest_snp",
                "case3_sig_gene_plus_other_genes", "case4_no_cs", "case5_single_cs")
```

### Overall counts

```{r overall_summary}
overall <- all_results_df[, .(count = .N), by = case]
overall[, label := case_labels[case]]
overall[, label := factor(label, levels = case_labels[case_order])]
overall <- overall[order(label)]

knitr::kable(overall[, .(Case = label, Count = count)],
             caption = "CS structure across all traits (total)")
```

```{r overall_plot, fig.width=9, fig.height=4}
overall[, label := factor(label, levels = rev(case_labels[case_order]))]

ggplot(overall, aes(x = label, y = count, fill = label)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = count), hjust = -0.2, size = 4) +
  coord_flip() +
  labs(x = "", y = "Number of regions",
       title = "CS structure in single-gene regions (all traits combined)") +
  theme_minimal(base_size = 14) +
  theme(axis.text.y = element_text(color = "black")) +
  ylim(0, max(overall$count) * 1.15)
```

### Per-trait counts table

```{r per_trait_table}
trait_case_ct <- dcast(all_results_df, trait ~ case, value.var = "gene_name",
                       fun.aggregate = length, fill = 0)

# Reorder columns
cols_present <- intersect(case_order, colnames(trait_case_ct))
trait_case_ct <- trait_case_ct[, c("trait", cols_present), with = FALSE]

# Rename columns
for (co in cols_present) {
  setnames(trait_case_ct, co, case_labels[co])
}

trait_case_ct[, Total := rowSums(.SD), .SDcols = intersect(unname(case_labels), colnames(trait_case_ct))]

DT::datatable(trait_case_ct, options = list(pageLength = 25, scrollX = TRUE),
              caption = "CS structure counts per trait")
```

## Per-trait barplots {.tabset}

```{r per_trait_plots, results='asis', fig.width=9, fig.height=4}
trait_list <- sort(unique(all_results_df$trait))

for (tr in trait_list) {
  cat(sprintf("\n### %s\n\n", tr))

  trait_df <- all_results_df[trait == tr]
  plot_df <- trait_df[, .(count = .N), by = case]
  plot_df[, label := case_labels[case]]

  # Ensure all cases appear
  all_cases_dt <- data.table(case = case_order, label = case_labels[case_order])
  plot_df <- merge(all_cases_dt, plot_df[, .(case, count)], by = "case", all.x = TRUE)
  plot_df[is.na(count), count := 0]
  plot_df[, label := factor(label, levels = rev(case_labels[case_order]))]

  p <- ggplot(plot_df, aes(x = label, y = count, fill = label)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = count), hjust = -0.2, size = 4) +
    coord_flip() +
    labs(x = "", y = "Number of regions",
         title = paste0(tr, ": CS structure in single-gene regions")) +
    theme_minimal(base_size = 14) +
    theme(axis.text.y = element_text(color = "black")) +
    ylim(0, max(plot_df$count) * 1.15 + 1)

  print(p)
  cat("\n\n")
}
```

## Per-trait stacked barplot

```{r stacked_plot, fig.width=12, fig.height=7}
stacked_df <- all_results_df[, .(count = .N), by = .(trait, case)]
stacked_df[, label := case_labels[case]]
stacked_df[, label := factor(label, levels = rev(case_labels[case_order]))]
stacked_df[, trait := factor(trait, levels = rev(sort(unique(trait))))]

ggplot(stacked_df, aes(x = trait, y = count, fill = label)) +
  geom_col() +
  coord_flip() +
  labs(x = "", y = "Number of regions", fill = "",
       title = "CS structure in single-gene regions by trait") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 10)) +
  guides(fill = guide_legend(nrow = 3, reverse = TRUE))
```

## Per-trait proportion plot

```{r proportion_plot, fig.width=12, fig.height=7}
prop_df <- all_results_df[, .(count = .N), by = .(trait, case)]
prop_df[, total := sum(count), by = trait]
prop_df[, prop := count / total]
prop_df[, label := case_labels[case]]
prop_df[, label := factor(label, levels = rev(case_labels[case_order]))]
prop_df[, trait := factor(trait, levels = rev(sort(unique(trait))))]

ggplot(prop_df, aes(x = trait, y = prop, fill = label)) +
  geom_col() +
  coord_flip() +
  labs(x = "", y = "Proportion of regions", fill = "",
       title = "CS structure proportions in single-gene regions by trait") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 10)) +
  guides(fill = guide_legend(nrow = 3, reverse = TRUE)) +
  scale_y_continuous(labels = scales::percent_format())
```

## Full results table

```{r full_table}
DT::datatable(all_results_df[, .(Trait = trait, Gene = gene_name, Region = region_id,
                                  Case = case_labels[case],
                                  `Total CS` = n_cs, `CS Sig Gene` = n_cs_sig,
                                  `CS Other Gene` = n_cs_other_gene, `CS SNP` = n_cs_snp)],
              options = list(pageLength = 25, scrollX = TRUE),
              filter = "top",
              caption = "All single-gene regions across all traits")
```
