---
title: "APA QTL analysis (using APA FUSION models by Chen et al.)"
author: "XSun"
date: "2024-05-07"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Data Overview

The paper: https://www.nature.com/articles/s41467-024-46064-7#Sec2

The data is downloaded from http://bioinfo.szbl.ac.cn/TCGD/download.php

Many non-zero weight SNPs have NA as ID

```{r}
load("/project2/xinhe/shared_data/multigroup_ctwas/weights/apa.stat.rdata")
print(sprintf("%s tissues included", nrow(sum)))

colnames(sum) <- c("#of genes","average # of non-zero weights_lasso","average # of NA ID for non-zero weights SNPs_lasso","average # of non-zero weights_enet","average # of NA ID for non-zero weights SNPs_enet")
DT::datatable(sum,caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;','Missing RS id'),options = list(pageLength = 5))
```

Some APA targets has NA lasso weights. For Adipose_Subcutaneous, there are 3844 APA targets, 180 of them have NA lasso weights (around 5%), none of these targets has NA enet weights. 

Below is one example

```{r}
load("/project2/xinhe/shared_data/multigroup_ctwas/weights/apa_models/Adipose_Subcutaneous/Adipose_Subcutaneous/Adipose_Subcutaneous.NM_000049.4.wgt.RDat")

DT::datatable(wgt.matrix[1:10,],caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;','Weights for NM_000049.4 (10 of 4000 are shown here)'),options = list(pageLength = 5))
```






# Analysis 

## Settings 

- Fusion Model: enet model, all SNPs with non-zero weights

## Results summary 

```{r}
load("/project/xinhe/xsun/multi_group_ctwas/3.apa_testing/summary/para_pip08.rdata")

DT::datatable(para_sum,caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;','parameter estimation'),options = list(pageLength = 5))

load("/project/xinhe/xsun/multi_group_ctwas/3.apa_testing/summary/genedetails_cs_pip08.rdata")

DT::datatable(gene_table_cut_cs,caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;','genes with pip > 0.8 & in credible sets'),options = list(pageLength = 5))
```
