---
title: "Compare different settings: cs index filter or not"
author: "XSun"
date: "2025-04-28"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---


```{r warning=F, message=FALSE}
library(dplyr)
library(scales)
library(tidyr)
library(ggplot2)
library(eulerr)
library(patchwork)
library(ctwas)
library(EnsDb.Hsapiens.v86)

ens_db <- EnsDb.Hsapiens.v86

source("/project/xinhe/xsun/multi_group_ctwas/14.comparing_diff_settings/0.functions.R")

traits_silver <- c("T2D","LDL","BMI","RBC","IBD","SCZ","aFib")
names(traits_silver) <- c("T2D-panukb","LDL-ukb-d-30780_irnt","BMI-panukb","RBC-panukb","IBD-ebi-a-GCST004131","SCZ-ieu-b-5102","aFib-ebi-a-GCST006414")

traits <- c("LDL-ukb-d-30780_irnt","IBD-ebi-a-GCST004131","BMI-panukb","RBC-panukb","SCZ-ieu-b-5102","aFib-ebi-a-GCST006414","T2D-panukb")
db <- "GO_Biological_Process_2023"

mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
mapping_munro <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
mapping_two <- rbind(mapping_predictdb,mapping_munro)

snp_map <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/LD_region_info/snp_map.RDS")

folder_results <- "/project/xinhe/xsun/multi_group_ctwas/15.susie_weights/snakemake_outputs/"

create_summary_plot_withTP <- function(df, columns_to_plot, x_var = "setting", x_order = NULL, title = NULL) {

  # Reshape data
  df_long <- df %>%
    pivot_longer(
      cols = all_of(columns_to_plot),
      names_to = "variable",
      values_to = "value"
    )
  
  # Convert to factor with specified order if x_order is provided
  if (!is.null(x_order)) {
    df_long <- df_long %>%
      mutate(across(all_of(x_var), ~factor(., levels = x_order)))
  }
  
  # Identify the max value for scaling
  max_main <- max(df_long$value[df_long$variable != "TP_rate"], na.rm = TRUE)
  max_tp_rate <- max(df_long$value[df_long$variable == "TP_rate"], na.rm = TRUE)
  
  if(max_tp_rate ==0) {
    max_tp_rate <- 1
  }
  
  # Rescale TP_rate
  df_long <- df_long %>%
    mutate(scaled_value = ifelse(variable == "TP_rate", 
                                 value * (max_main / max_tp_rate), value))
  
  # Create plot
  ggplot(df_long, aes(x = .data[[x_var]], y = scaled_value, color = variable, shape = variable)) +
    #geom_point(size = 3, position = position_jitter(width = 0.2)) +
    geom_point(size = 3) + 
    scale_y_continuous(
      name = "Count",
      sec.axis = sec_axis(~ . * (max_tp_rate / max_main), name = "TP Rate")
    ) +
    labs(x = "Settings", title = title) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
      legend.position = "right",
      legend.title = element_blank()
    ) +
    scale_color_brewer(palette = "Set1")
}

DT::datatable(matrix())


thin <- 1
var_struc <- "shared_all"
L <- 5
st <- "with_susieST"
```

# The number of genes at PIP > 0.8

```{r warning=F, message=FALSE, fig.height=5, fig.width=15}


setting_names <- c()
num_gene_pip08_all <- c()
num_silver_pip08_all <- c()
num_bystander_pip08_all <- c()
go_num_fdr005 <- c()
for (trait in traits) {
  for (cs in c("CS_filtered","CS_NOT_filtered")){

    if(cs == "CS_filtered"){
      cs_setting <- NULL
    }else{
      cs_setting <- "_csF"
    }

    setting_names <- c(setting_names, paste0(traits_silver[trait],"-",cs))

    # num_gene_pip08 -- cs filtered
    combined_pip_by_group <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final",cs_setting,".RDS"))
    combined_pip_sig <- combined_pip_by_group[combined_pip_by_group$combined_pip > 0.8,]

    num_gene_pip08_all <- c(num_gene_pip08_all, nrow(combined_pip_sig))

    # silver_standard genes
    known <- readRDS(paste0("/project/xinhe/xsun/multi_group_ctwas/data/silverstandard/known_annotations_",traits_silver[trait],".RDS"))
    bystander <- readRDS(paste0("/project/xinhe/xsun/multi_group_ctwas/data/silverstandard/bystanders_",traits_silver[trait],".RDS"))

    num_silver_pip08_all <- c(num_silver_pip08_all,sum(combined_pip_sig$gene_name %in% known))
    num_bystander_pip08_all <- c(num_bystander_pip08_all,sum(combined_pip_sig$gene_name %in% bystander))

    file_go <- paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_",cs,".RDS")
    if(!file.exists(file_go)){
      go_num_fdr005 <- c(go_num_fdr005,0)
    }else{
      go <- readRDS(paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_",cs,".RDS"))
      go_num_fdr005 <- c(go_num_fdr005,nrow(go))
    }


  }
}

df <- data.frame(setting = setting_names,
                 num_gene_pip08 = num_gene_pip08_all,
                 num_silver_pip08 = num_silver_pip08_all,
                 num_bystander_pip08 = num_bystander_pip08_all,
                 TP_rate = num_silver_pip08_all/(num_silver_pip08_all+num_bystander_pip08_all),
                 go_num_fdr005 = go_num_fdr005)

create_summary_plot_withTP(df,x_order = setting_names,
                    columns_to_plot = c("num_gene_pip08","num_silver_pip08","TP_rate"))

create_summary_plot_withTP(df,x_order = setting_names,
                    columns_to_plot = c("go_num_fdr005"), title = "Number of GO terms at p.adjust < 0.05")


DT::datatable(df,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;',''),options = list(pageLength = 10) )
```



# Number of GO terms at adjusted.p < 0.05

```{r results='asis', warning=F, message=FALSE, fig.height=4, fig.width=4}

traits <- c("LDL-ukb-d-30780_irnt","IBD-ebi-a-GCST004131")

for (trait in traits) {

  file_go_filtered <- paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_CS_filtered.RDS")
  if(!file.exists(file_go_filtered)){
    go_filtered <- NULL
  }else{
    go_filtered <- readRDS(file_go_filtered)
  }



  file_go_nofiltered <- paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_CS_NOT_filtered.RDS")
  if(!file.exists(file_go_nofiltered)){
    go_nofiltered <- NULL
  }else{
    go_nofiltered <- readRDS(file_go_nofiltered)
  }

  set1 <- unique(go_filtered$Term)
  set2 <- unique(go_nofiltered$Term)

  venn_input <- list(
    Filtered = set1,
    NoFiltered = set2
  )

  fit <- euler(venn_input)

  print(plot(fit,
       fills = c("skyblue", "orange"),
       labels = TRUE,
       quantities = TRUE,
       main = trait))


}

```


```{r results='asis', warning=F, message=FALSE, fig.height=4, fig.width=4}

traits <- c("LDL-ukb-d-30780_irnt","IBD-ebi-a-GCST004131")

for (trait in traits) {

  file_go_filtered <- paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_CS_filtered.RDS")
  if(!file.exists(file_go_filtered)){
    go_filtered <- NULL
  }else{
    go_filtered <- readRDS(file_go_filtered)
  }



  file_go_nofiltered <- paste0(folder_results,trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".enrichr_",db,"_CS_NOT_filtered.RDS")
  if(!file.exists(file_go_nofiltered)){
    go_nofiltered <- NULL
  }else{
    go_nofiltered <- readRDS(file_go_nofiltered)
  }


  cat("\n\n")
  cat(knitr::knit_print(DT::datatable(go_filtered[!go_filtered$Term %in% go_nofiltered$Term,], caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;',paste0("Unique GO terms at p.adjust < 0.05 -- ",trait, "--CS_filtered")),options = list(pageLength = 5))))
  cat("\n\n")

  cat("\n\n")
  cat(knitr::knit_print(DT::datatable(go_nofiltered[!go_nofiltered$Term %in% go_filtered$Term,], caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;',paste0("Unique GO terms at p.adjust < 0.05 -- ",trait, "--CS_NOT_filtered")),options = list(pageLength = 5))))
  cat("\n\n")



}

```



# Comparing PIPs at gene-level


## LDL-ukb-d-30780_irnt

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "LDL-ukb-d-30780_irnt"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```



| Gene      | Involvement in LDL/Lipid Metabolism                           | Evidence Level |
|-----------|---------------------------------------------------------------|----------------|
| KIF13B    | Enhances LDL uptake via LRP1                                  | Strong         |
| TTC39B    | Regulates cholesterol homeostasis via LXR degradation         | Strong         |
| USP53     | Modulates SR-A ubiquitination affecting LDL clearance         | Moderate       |
| ACVR1C    | Influences adipose lipid metabolism                           | Moderate       |
| LRRK2     | Affects lipid storage and lysosomal function                  | Moderate       |
| ACP6      | Involved in LPA metabolism; indirect link to LDL              | Limited        |
| CD163L1   | Scavenger receptor; unclear role in LDL metabolism            | Limited        |
| KDSR      | Sphingolipid biosynthesis; indirect association with LDL      | Limited        |
| ZNF518A   | Function not well-characterized; no direct link to LDL        | Limited        |



```{r results='asis',warning=F, message=FALSE, fig.height=10, fig.width=10}
file_ctwas_result <- get_ctwas_file(trait, tissue = NULL, folder_results,st,thin, var_struc, L)
ctwas_res <- readRDS(file_ctwas_result)
weights <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".preprocessed.weights.RDS"))

finemap_res <- ctwas_res$finemap_res
finemap_res$molecular_id <- get_molecular_ids(finemap_res)
finemap_res <- anno_finemap_res(finemap_res,
                                snp_map = snp_map,
                                mapping_table = mapping_two,
                                add_gene_annot = TRUE,
                                map_by = "molecular_id",
                                drop_unmapped = TRUE,
                                add_position = TRUE,
                                use_gene_pos = "mid")

finemap_res <- finemap_res[complete.cases(finemap_res$id),]

make_locusplot(finemap_res,
               region_id = "8_28304875_29470379",
               ens_db = ens_db,
               weights = weights,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = F,
               focal_gene = "KIF13B",
               color_pval_by = "cs",
               color_pip_by = "cs",
               label.text.size = 6,
               axis.text.size = 16,
               axis.title.size = 16,
               legend.text.size = 16,
               point.sizes = c(3,5,5,5))

make_locusplot(finemap_res,
               region_id = "9_14836365_16659657",
               ens_db = ens_db,
               weights = weights,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = F,
               focal_gene = "TTC39B",
               color_pval_by = "cs",
               color_pip_by = "cs",
               label.text.size = 6,
               axis.text.size = 16,
               axis.title.size = 16,
               legend.text.size = 16,
               point.sizes = c(3,5,5,5))

make_locusplot(finemap_res,
               region_id = "4_119012357_119471529",
               ens_db = ens_db,
               weights = weights,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = F,
               focal_gene = "USP53",
               color_pval_by = "cs",
               color_pip_by = "cs",
               label.text.size = 6,
               axis.text.size = 16,
               axis.title.size = 16,
               legend.text.size = 16,
               point.sizes = c(3,5,5,5))

make_locusplot(finemap_res,
               region_id = "2_156704123_157676706",
               ens_db = ens_db,
               weights = weights,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = F,
               focal_gene = "ACVR1C",
               color_pval_by = "cs",
               color_pip_by = "cs",
               label.text.size = 6,
               axis.text.size = 16,
               axis.title.size = 16,
               legend.text.size = 16,
               point.sizes = c(3,5,5,5))

```


## IBD-ebi-a-GCST004131

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "IBD-ebi-a-GCST004131"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```




| Gene       | Evidence of Association with IBD                                                                 | Evidence Level |
|------------|--------------------------------------------------------------------------------------------------|----------------|
| SLC26A3    | Identified as an IBD susceptibility gene; downregulation impairs epithelial barrier and increases inflammation. | Strong         |
| MAST2      | Regulates NF-κB signaling; involved in inflammatory response modulation.                         | Moderate       |
| DOCK8      | Deficiency leads to immune dysregulation with IBD-like enteropathy and colitis.                  | Moderate       |
| FOXN2      | Regulates REG Iβ, which is upregulated in IBD mucosa.                                            | Limited        |
| ACBD3      | No direct link to IBD; studied more in cancer and viral replication contexts.                    | Limited        |
| TMEM151B   | No known evidence linking it to IBD.                                                             | None           |



## BMI-panukb

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "BMI-panukb"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```



## RBC-panukb

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "RBC-panukb"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```

## SCZ-ieu-b-5102

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "SCZ-ieu-b-5102"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```

## aFib-ebi-a-GCST006414

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "aFib-ebi-a-GCST006414"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```




```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
traits <- c("LDL-ukb-d-30780_irnt","IBD-ebi-a-GCST004131","BMI-panukb","RBC-panukb","SCZ-ieu-b-5102","aFib-ebi-a-GCST006414","T2D-panukb")

p <- list()
for (trait in traits) {
  
  combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
  combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
  colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")
  
  combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
  combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
  colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

  combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
  combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
  combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]
  
  df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
  df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1
  
  p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
    geom_point() + 
    labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
    geom_abline(slope = 1, intercept = 0, col = "Red") +
    ggtitle(trait) +
    theme_minimal()
  
  print("PIP = 1.1 means PIP = NA when filtering CS")
  print(p)
  
  # Merge the two data frames by 'gene_name' with suffixes to distinguish columns
  merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                     by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)
  
  # List of columns to process (excluding 'gene_name')
  original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")
  
  # Iterate over each column and concatenate values from both data frames
  for (col in original_cols) {
    notfiltered_col <- paste0(col, "_NOTfiltered")
    filtered_col <- paste0(col, "_filtered")
    merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
  }
  
  # Select the relevant columns to match the original structure
  df <- merged_df[, c("gene_name", original_cols)]
  
  cat("\n\n")
  cat(knitr::knit_print(DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))))
  cat("\n\n")

  
}

#wrap_plots(lapply(p, wrap_elements), ncol = 4)
```


LDL: 


| Gene      | Involvement in LDL/Lipid Metabolism                           | Evidence Level |
|-----------|---------------------------------------------------------------|----------------|
| KIF13B    | Enhances LDL uptake via LRP1                                  | Strong         |
| TTC39B    | Regulates cholesterol homeostasis via LXR degradation         | Strong         |
| USP53     | Modulates SR-A ubiquitination affecting LDL clearance         | Moderate       |
| ACVR1C    | Influences adipose lipid metabolism                           | Moderate       |
| LRRK2     | Affects lipid storage and lysosomal function                  | Moderate       |
| ACP6      | Involved in LPA metabolism; indirect link to LDL              | Limited        |
| CD163L1   | Scavenger receptor; unclear role in LDL metabolism            | Limited        |
| KDSR      | Sphingolipid biosynthesis; indirect association with LDL      | Limited        |
| ZNF518A   | Function not well-characterized; no direct link to LDL        | Limited        |





## T2D-panukb

```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4}
trait <- "T2D-panukb"

combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS"))
combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")]
colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered")

combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS"))
combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")]
colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered")

combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,]
combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,]

df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T)
df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1

p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) +
  geom_point() + 
  labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") +
  geom_abline(slope = 1, intercept = 0, col = "Red") +
  ggtitle(trait) +
  theme_minimal()

print("PIP = 1.1 means PIP = NA when filtering CS")
print(p)

# Merge the two data frames by 'gene_name' with suffixes to distinguish columns
merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered, 
                   by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T)

# List of columns to process (excluding 'gene_name')
original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name")

# Iterate over each column and concatenate values from both data frames
for (col in original_cols) {
  notfiltered_col <- paste0(col, "_NOTfiltered")
  filtered_col <- paste0(col, "_filtered")
  merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-")
}

# Select the relevant columns to match the original structure
df <- merged_df[, c("gene_name", original_cols)]

DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5))


```




<!-- ```{r results='asis',warning=F, message=FALSE, fig.height=4, fig.width=4} -->
<!-- traits <- c("LDL-ukb-d-30780_irnt","IBD-ebi-a-GCST004131","BMI-panukb","RBC-panukb","SCZ-ieu-b-5102","aFib-ebi-a-GCST006414","T2D-panukb") -->

<!-- p <- list() -->
<!-- for (trait in traits) { -->

<!--   combined_pip_filtered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csincluded.RDS")) -->
<!--   combined_pip_filtered_plot <- combined_pip_filtered[,c("gene_name","combined_pip")] -->
<!--   colnames(combined_pip_filtered_plot) <- c("gene_name","combined_pip_csfiltered") -->

<!--   combined_pip_NOTfiltered <- readRDS(paste0(folder_results,"/",trait,"/",trait,".",st,".thin",thin,".",var_struc,".L",L, ".combined_pip_bygroup_final_csF.RDS")) -->
<!--   combined_pip_NOTfiltered_plot <- combined_pip_NOTfiltered[,c("gene_name","combined_pip")] -->
<!--   colnames(combined_pip_NOTfiltered_plot) <- c("gene_name","combined_pip_csNOTfiltered") -->

<!--   combined_pip_filtered_sig <- combined_pip_filtered[combined_pip_filtered$combined_pip > 0.8,] -->
<!--   combined_pip_NOTfiltered_sig <- combined_pip_NOTfiltered[combined_pip_NOTfiltered$combined_pip > 0.8,] -->
<!--   combined_pip_NOTfiltered_sig_plot <- combined_pip_NOTfiltered_plot[combined_pip_NOTfiltered_plot$combined_pip > 0.8,] -->

<!--   df_merge <- merge(combined_pip_NOTfiltered_sig_plot, combined_pip_filtered_plot, by = "gene_name", all.x = T) -->
<!--   df_merge$combined_pip_csfiltered[is.na(df_merge$combined_pip_csfiltered)] <- 1.1 -->

<!--   p <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) + -->
<!--   #p[[trait]] <-ggplot(data = df_merge,aes(x = combined_pip_csfiltered, y = combined_pip_csNOTfiltered)) + -->
<!--     geom_point() +  -->
<!--     labs(x = "Combined PIP -- CS filtered", y = "Combined PIP -- CS NOT filtered") + -->
<!--     geom_abline(slope = 1, intercept = 0, col = "Red") + -->
<!--     ggtitle(trait) + -->
<!--     theme_minimal() -->

<!--   print("PIP = 1.1 means PIP = NA when filtering CS") -->
<!--   print(p) -->

<!--   # Merge the two data frames by 'gene_name' with suffixes to distinguish columns -->
<!--   merged_df <- merge(combined_pip_NOTfiltered_sig, combined_pip_filtered,  -->
<!--                      by = "gene_name", suffixes = c("_NOTfiltered", "_filtered"),all.x=T) -->

<!--   # List of columns to process (excluding 'gene_name') -->
<!--   original_cols <- setdiff(names(combined_pip_NOTfiltered_sig), "gene_name") -->

<!--   # Iterate over each column and concatenate values from both data frames -->
<!--   for (col in original_cols) { -->
<!--     notfiltered_col <- paste0(col, "_NOTfiltered") -->
<!--     filtered_col <- paste0(col, "_filtered") -->
<!--     merged_df[[col]] <- paste(round(merged_df[[notfiltered_col]],digits = 5), round(merged_df[[filtered_col]],digits = 5), sep = "-") -->
<!--   } -->

<!--   # Select the relevant columns to match the original structure -->
<!--   df <- merged_df[, c("gene_name", original_cols)] -->

<!--   cat("\n\n") -->
<!--   cat(knitr::knit_print(DT::datatable(df, caption = htmltools::tags$caption( style = 'font-size: 150%; caption-side: topleft; text-align = left; color:black;', trait),options = list(pageLength = 5)))) -->
<!--   cat("\n\n") -->


<!-- } -->

<!-- #wrap_plots(lapply(p, wrap_elements), ncol = 4) -->
<!-- ``` -->


