---
title: "Validation for multi-tissue results"
author: "XSun"
date: "2024-01-11"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---


# Overview

We validate [genes with susie pip > 0.8](https://sq-96.github.io/multigroup_ctwas_analysis/multi_tissue_ldmerge.html) by some trait-related pathways. Pathways are selected using MAGMA. Due to the correlation among candidate pathways, we employ SuSiE and logistic SuSiE to fine-map the pathways.

## Model

The model is $y=X*w$

y is an n-dimensional vector representing gene-trait associations (n = number of genes). 

 - For SuSiE, y consists of z-scores computed by MAGMA
 - for logistic SuSiE, y is a binary vector indicating gene-trait relationships (genes with FDR < 0.05 as per MAGMA are marked 1).

X is an n×m matrix (m = number of pathways) indicating gene membership in specific pathways.

## Benchmarks

The model fitting results in pathway weights, from which we predict gene labels $\hat{y}$. We then categorize genes based on these new labels. 

- For SuSiE, we compute the p-values from the new labels(z-scores), then compute FDR. Genes with FDR < 0.05 are considered benchmarks. 
- For logistic SuSiE, genes with labels > 0.5 are considered benchmarks.

## Testing genes

Genes from ctwas results are divided into two groups based on their SuSiE PIPs: high (>0.8) and moderate (0.8 > PIP > 0.5). 

## Fisher exact test

We assess whether high-PIP genes are more enriched in our benchmarks than moderate-PIP genes using Fisher exact tests. 

The testing matrix is: 

```{r}

fisher_matrix <- matrix(c("n1","n2","n3","n4"),nrow = 2,ncol = 2)
rownames(fisher_matrix) <- c("#included","#notincluded")
colnames(fisher_matrix) <- c("pip08","pip05")

print(fisher_matrix)
```

## Pathways

The pathways are from Go Biological Process (gobp), Go Molecular Function (gomf), Go Cellular Component (gocc) and KEGG.


## Functions

```{r warning=F,message=FALSE}
library(gseasusie)
library(tidyverse)
library(GO.db)


# coeftable_linear<- function(linear_fit) {
#   coef <- susieR::coef.susie(linear_fit)
#   coef <- as.data.frame(cbind(names(coef), coef))
#   colnames(coef) <- c("pwy", "beta")
#   rownames(coef) <- seq(1,nrow(coef),by=1)
#   DT::datatable(coef, 
#                 caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
#                                                   'Correct coef for linear fitting'), 
#                 options = list(pageLength = 5))
# }

color_sign = function(value) {
  if (value > 0) {
    color <- "#008000"
  } else if (value < 0) {
    color <- "#e00000"
  } else {
    color <- "#777"
  }
  list(color = color)
}


getGOTermName <- function(go_id) {
  result <- try(Term(GOTERM[[go_id]]), silent = TRUE)
  if (class(result) == "try-error") {
    return(NA)
  } else {
    return(result)
  }
}

getKEGGPathwayName <- function(kegg_id) {
  result <- try(KEGGREST::keggGet(kegg_id)[[1]]$NAME, silent = TRUE)
  if (class(result) == "try-error") {
    return(NA)
  } else {
    return(result)
  }
}

interactive_table_linear_susie <- function(fit, ora) {
  
  fit <- fit
  ora <- ora
  
  res <- gseasusie:::get_gene_set_summary(fit) %>%
    dplyr::left_join(ora)
  
  coef <- susieR::coef.susie(fit)
  coef <- as.data.frame(cbind(names(coef), coef))
  colnames(coef) <- c("pwy", "beta")
  rownames(coef) <- seq(1,nrow(coef),by=1)
  
  res_updated <- res %>%
    # Ensure 'beta' in 'res' is of type double
    mutate(beta = as.numeric(beta)) %>%
    left_join(coef %>%
                # Ensure 'beta' in 'coef' is of type double
                mutate(beta = as.numeric(beta)), 
              by = c("geneSet" = "pwy")) %>%
    # Combine the two 'beta' columns, choosing 'coef' values first
    mutate(beta = coalesce(beta.y, beta.x)) %>%
    # Explicitly use `select` from `dplyr`
    dplyr::select(-beta.y, -beta.x)
  
  res <- res_updated
  
  csdat <- gseasusie:::get_credible_set_summary(fit) %>%
    dplyr::left_join(ora) %>%
    dplyr::filter(in_cs, active_cs) %>%
    dplyr::select(geneSet, component, in_cs) %>%
    distinct()
  
  dt <- res %>% 
    dplyr::filter(overlap > 0) %>%
    dplyr::mutate(
      logOddsRatio = log(oddsRatio),
      nlog10pFishersExact = -log10(pFishersExact)
    ) %>%
    dplyr::left_join(csdat) %>%
    dplyr::arrange(dplyr::desc(nlog10pFishersExact)) %>%
    dplyr::mutate(
      fisherRank = dplyr::row_number(),
      in_cs = dplyr::if_else(is.na(in_cs), FALSE, in_cs)) %>%
    dplyr::select(geneSet, beta, pip, overlap, geneSetSize, logOddsRatio, nlog10pFishersExact, in_cs, component, fisherRank) %>%
    dplyr::mutate(dplyr::across(!where(is.numeric) , as.factor))
  
  
  if(grepl("GO",dt$geneSet[1])) {
      dt <- dt %>%
      dplyr::filter(!is.na(component)) %>% #### only show CS
      dplyr::mutate(goTermName = sapply(as.character(geneSet), getGOTermName)) %>% # extract Go term names
      dplyr::select(geneSet, goTermName, everything()) # re-order
  }else if (grepl("hsa",dt$geneSet[1])) {
      dt <- dt %>%
      dplyr::filter(!is.na(component)) %>% #### only show CS
      dplyr::mutate(KEGGPathwayName = sapply(as.character(geneSet), getKEGGPathwayName)) %>% # extract Go term names
      dplyr::select(geneSet, KEGGPathwayName, everything()) # re-order
  }
  
  # dt %>%
  #   dplyr::select(-c(in_cs)) %>%
  #   reactable::reactable(
  #     filterable=TRUE,
  #     minRows=1,
  #     columns = list(
  #       pip = reactable::colDef(format = reactable::colFormat(digits = 3)),
  #       logOddsRatio = reactable::colDef(style= function(value){color_sign(value)},
  #                                        format = reactable::colFormat(digits = 3)),
  #       beta = reactable::colDef(style= function(value){color_sign(value)},
  #                                format = reactable::colFormat(digits = 3)),
  #       nlog10pFishersExact = reactable::colDef(format = reactable::colFormat(digits = 3))
  #     ),
  #     rowStyle = function(index){
  #       if(dt$in_cs[index] == TRUE){
  #         list(background = "#e5f5e0")
  #       }
  #     },
  #     defaultSorted = list(nlog10pFishersExact='desc')
  #   )
  # 
  DT::datatable(dt,options = list(pageLength=10))
  
}

interactive_table_logistic_susie <- function(fit, ora) {
  
  fit <- fit
  ora <- ora
  
  res <- gseasusie:::get_gene_set_summary(fit) %>%
    dplyr::left_join(ora)
  
  csdat <- gseasusie:::get_credible_set_summary(fit) %>%
    dplyr::left_join(ora) %>%
    dplyr::filter(in_cs, active_cs) %>%
    dplyr::select(geneSet, component, in_cs) %>%
    distinct()
  
  dt <- res %>% 
    dplyr::filter(overlap > 0) %>%
    dplyr::mutate(
      logOddsRatio = log(oddsRatio),
      nlog10pFishersExact = -log10(pFishersExact)
    ) %>%
    dplyr::left_join(csdat) %>%
    dplyr::arrange(dplyr::desc(nlog10pFishersExact)) %>%
    dplyr::mutate(
      fisherRank = dplyr::row_number(),
      in_cs = dplyr::if_else(is.na(in_cs), FALSE, in_cs)) %>%
    dplyr::select(geneSet, beta, pip, overlap, geneSetSize, logOddsRatio, nlog10pFishersExact, in_cs, component, fisherRank) %>%
    dplyr::mutate(dplyr::across(!where(is.numeric) , as.factor))
  
  
  if(grepl("GO",dt$geneSet[1])) {
      dt <- dt %>%
      dplyr::filter(!is.na(component)) %>% #### only show CS
      dplyr::mutate(goTermName = sapply(as.character(geneSet), getGOTermName)) %>% # extract Go term names
      dplyr::select(geneSet, goTermName, everything()) # re-order
  }else if (grepl("hsa",dt$geneSet[1])) {
      dt <- dt %>%
      dplyr::filter(!is.na(component)) %>% #### only show CS
      dplyr::mutate(KEGGPathwayName = sapply(as.character(geneSet), getKEGGPathwayName)) %>% # extract Go term names
      dplyr::select(geneSet, KEGGPathwayName, everything()) # re-order
  }
  
  # dt %>%
  #   dplyr::select(-c(in_cs)) %>%
  #   reactable::reactable(
  #     filterable=TRUE,
  #     minRows=10,
  #     columns = list(
  #       pip = reactable::colDef(format = reactable::colFormat(digits = 3)),
  #       logOddsRatio = reactable::colDef(style= function(value){color_sign(value)},
  #                                        format = reactable::colFormat(digits = 3)),
  #       beta = reactable::colDef(style= function(value){color_sign(value)},
  #                                format = reactable::colFormat(digits = 3)),
  #       nlog10pFishersExact = reactable::colDef(format = reactable::colFormat(digits = 3))
  #     ),
  #     rowStyle = function(index){
  #       if(dt$in_cs[index] == TRUE){
  #         list(background = "#e5f5e0")
  #       }
  #     },
  #     defaultSorted = list(nlog10pFishersExact='desc')
  #   )
  DT::datatable(dt,options = list(pageLength=10))
}
```


# aFib-ebi-a-GCST006414

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_aFib-ebi-a-GCST006414_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_aFib-ebi-a-GCST006414_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# IBD-ebi-a-GCST004131
## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_IBD-ebi-a-GCST004131_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_IBD-ebi-a-GCST004131_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# LDL-ukb-d-30780_irnt
## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_LDL-ukb-d-30780_irnt_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_LDL-ukb-d-30780_irnt_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# SBP-ukb-a-360

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SBP-ukb-a-360_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SBP-ukb-a-360_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```



# SCZ-ieu-b-5102

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SCZ-ieu-b-5102_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SCZ-ieu-b-5102_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# WBC-ieu-b-30

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)


interactive_table_linear_susie(fit = linear.fit, ora = linear.ora)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
interactive_table_logistic_susie(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_WBC-ieu-b-30_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_WBC-ieu-b-30_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


