---
title: "ctwas POPs analysis"
output: html_document
date: '2025-8-2'
editor_options: 
  chunk_output_type: console
---

### Method
1. For each trait, select regions with at lease one high PIP expression/splicing trait (PIP>0.8)
- based on multi-cTWAS results with three molecular traits (eQTL,sQTL,stQTL) from five tissues.
2. Run coloc with eQTL and sQTL full summary statistics from five tissues
- no stQTL full summary statistics
3. Comparing the number of expression and splicing molecular traits identified by coloc (PP4>0.8), single-cTWAS (PIP>0.8) and multi-cTWAS (PIP>0.8)
- don't include stability traits identified by multi-cTWAS

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(data.table)
traits <- c(
  "SBP-ukb-a-360", "LDL-ukb-d-30780_irnt", "aFib-ebi-a-GCST006414",
  "WBC-ieu-b-30", "IBD-ebi-a-GCST004131", "SCZ-ieu-b-5102", "BMI-panukb",
  "PLT-panukb", "RBC-panukb", "HB-panukb", "HTN-panukb", "Height-panukb",
  "T2D-panukb", "MDD-ieu-b-102", "BIP-ieu-b-5110",#"T1D-GCST90014023",
  "ASD-ieu-a-1185", "PD-ieu-b-7", "NS-ukb-a-230","ATH_gtexukb"
)

plot_pops_by_pip_bin <- function(df,trait_name) {
  # Define pip bins
  df$bin <- cut(
    df$combined_pip,
    #breaks = c(0, 0.01, 0.25, 0.5, 0.7, 0.9, 1),
    breaks = c(0, 0.01, 0.25, 0.5, 0.8, 1),
    include.lowest = TRUE,
    #labels = c("[0–0.01]", "[0.01–0.25]", "[0.25–0.5]", "[0.5–0.7]", "[0.7–0.9]", "[0.9–1]")
    labels = c("[0–0.01]", "[0.01–0.25]", "[0.25–0.5]", "[0.5–0.8]", "[0.8–1]")
  )
  
  # Load required libraries
  library(dplyr)
  library(ggplot2)
  
  # Compute summary statistics
  summary_df <- df %>%
    group_by(bin) %>%
    summarise(
      avg_pops = mean(PoPS_Score, na.rm = TRUE),
      se_pops = sd(PoPS_Score, na.rm = TRUE) / sqrt(sum(!is.na(PoPS_Score)))
    ) %>%
    ungroup()
  
  # Plot
  ggplot(summary_df, aes(x = bin, y = avg_pops)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    geom_errorbar(aes(ymin = avg_pops - se_pops, ymax = avg_pops + se_pops), width = 0.2) +
    labs(
      title = trait_name,
      x = "PIP Bin",
      y = "Average PoPS Score"
    ) +
    theme_minimal()
}
```

### POPS score across all traits
```{r echo=FALSE, message=FALSE, warning=FALSE}
plot_df <- data.frame()
for(i in traits){
  pops <- fread(paste0("/project/xinhe/shengqian/pops/pops_UKB_output1/",i,"_pops/",i,".preds"))
  pop_anno <- fread("/project/xinhe/shengqian/pops/example/data/utils/gene_annot_jun10.txt")
  pops_pred <- merge(pops, pop_anno, by = "ENSGID", all.x = TRUE)
  pops_pred <- pops_pred[,c("PoPS_Score","NAME")]
  ctwas_res <- readRDS(paste0("/project/xinhe/xsun/multi_group_ctwas/23.multi_group_0515/snakemake_outputs/",i,"/",i,".3qtls.combined_pip_bytype_final.RDS"))
  ctwas_res <- ctwas_res[,c("gene_name","combined_pip")]
  merged_df <- merge(ctwas_res, pops_pred, by.x = "gene_name", by.y = "NAME", all.x = TRUE)
  plot_df <- rbind(plot_df,merged_df)
  print(dim(plot_df))
}
plot_df <- na.omit(plot_df)
plot_pops_by_pip_bin(plot_df,"Across all traits")
```

### POPS score of individual trait
```{r echo=FALSE, message=FALSE, warning=FALSE}
for(i in traits){
  pops <- fread(paste0("/project/xinhe/shengqian/pops/pops_UKB_output1/",i,"_pops/",i,".preds"))
  pop_anno <- fread("/project/xinhe/shengqian/pops/example/data/utils/gene_annot_jun10.txt")
  pops_pred <- merge(pops, pop_anno, by = "ENSGID", all.x = TRUE)
  pops_pred <- pops_pred[,c("PoPS_Score","NAME")]
  ctwas_res <- readRDS(paste0("/project/xinhe/xsun/multi_group_ctwas/23.multi_group_0515/snakemake_outputs/",i,"/",i,".3qtls.combined_pip_bytype_final.RDS"))
  ctwas_res <- ctwas_res[,c("gene_name","combined_pip")]
  merged_df <- merge(ctwas_res, pops_pred, by.x = "gene_name", by.y = "NAME", all.x = TRUE)
  merged_df <- na.omit(merged_df)
  print(plot_pops_by_pip_bin(merged_df,paste0(i,", # of genes ",dim(merged_df)[1])))
}
```