---
title: "Training stability weights using munro's RNA data"
author: "XSun"
date: "2025-03-14"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

## Data source

Normalized RNA phenotype were shared by Munro et al

Covariates are downloaded from https://pantry.pejlab.org/

Genotype are from gtex v8, we imputed the missing genotype using `beagle` 

## Workflow

### Cross validation

For each RNA phenotype in each tissue, we partitioned the available samples into training (80%) and testing (20%) datasets.  

- Training Phase  

For each RNA molecular, we performed the following steps:  

1. **Variant Selection:** We defined a ±50 kb window around the transcription start site (TSS) of each gene, following Munro et al. Variants located within this window were selected for analysis.  
2. **Preprocessing:** Covariates were regressed out from both the RNA phenotype and the genotype matrix containing the selected variants. The residuals from this regression were used as inputs for subsequent analysis.  (as susie tutorial described)
3. **Fine-Mapping with SuSiE:** We applied SuSiE with `L = 1` and `L = 5` to the residualized data and identified the top variants from the credible sets.  
4. **Effect Size Estimation:** For the selected variants, we re-fitted a multiple linear regression model:  
   
   ```
   model <- lm(scaled_RNA_phenotype ~ SNPs_centered + covariates_scaled)
   effect_sizes <- coef(model)
   ```  
   
   where `scaled_RNA_phenotype` represents the scaled RNA phenotype, `SNPs_centered` denotes the centered SNP genotype matrix, and `covariates_scaled` represents scaled covariates. The estimated coefficients from this model were used as effect sizes for the selected SNPs.  

- Testing Phase  

Using the trained effect sizes, we predicted RNA phenotypes in the testing dataset and evaluated model performance.  

- Evaluation

We used MSE, r2 to evaluate the performance of the prediction model 

r2

$$ R^2 = 1 - \frac{\sum (y_{\text{test}} - y_{\text{pred}})^2}{\sum (y_{\text{test}} - \bar{y}_{\text{test}})^2} $$

- \(y_{\text{test}}\): Observed values in the test set,
- \(y_{\text{pred}}\): Predicted values,
- \(\bar{y}_{\text{test}}\): Mean of the test set observed values.

MSE

$$ \text{MSE} = \frac{1}{n} \sum_{i=1}^n (y_i - \hat{y}_i)^2 $$

- \( y_i \): Observed value for the \(i\)-th sample,
- \( \hat{y}_i \): Predicted value for the \(i\)-th sample,
- \( n \): Total number of samples.

```{r}
library(RSQLite)
library(ggplot2)
library(gridExtra)

name_mapping <- read.table("/project2/xinhe/shared_data/multigroup_ctwas/weights/files_Munro/Munro_name_mapping.txt")
colnames(name_mapping) <- c("Munro_name","gtex_name")
```

# Results

## Comparing L=1 and L=5

### RNA stability

```{r}
qtl = "stability"

L=1
folder_pred_L1 <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights_L1<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample_L1<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

L=5
folder_pred_L5 <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights_L5<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample_L5<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")



```


```{r fig.height=40, fig.width=10, warning=F, message=FALSE}

sum <- c()
p <- list()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ## sample size 
  sample_test <- nrow(read.table(paste0(folder_sample_L1,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample_L1,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ## L=1
  rsq_L1 <- readRDS(paste0(folder_pred_L1, tissue, "_rsq_all_fusion.RDS"))
  n_withcs_L1 <- length(rsq_L1)
  n_posrsq_L1 <- sum(rsq_L1>0,na.rm = T)
  
  ## L=5
  rsq_L5 <- readRDS(paste0(folder_pred_L5, tissue, "_rsq_all_fusion.RDS"))
  n_withcs_L5 <- length(rsq_L5)
  n_posrsq_L5 <- sum(rsq_L5>0,na.rm = T)
  
  n_overlap_withcs <- sum(names(rsq_L1) %in% names(rsq_L5))
  n_overlap_posrsq <- sum(names(rsq_L1[rsq_L1 > 0]) %in% names(rsq_L5[rsq_L5 > 0]))
  
  ## total rna & average qtl
  weights <- readRDS(paste0(folder_weights_L5, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  weights_nonnull <- Filter(Negate(is.null), weights)
  avg_qtl <- mean(unlist(lapply(weights_nonnull,length)),na.rm = T)
  
  tmp_tissue <- c(tissue_gtex,sample_total, n_rna, n_withcs_L1, n_withcs_L5, round(avg_qtl,digits = 4), n_overlap_withcs, n_posrsq_L1, n_posrsq_L5, n_overlap_posrsq)
  sum <- rbind(sum, tmp_tissue)
  
  rsq_L1 <- data.frame(id = names(rsq_L1), rsq_L1 = rsq_L1)
  rsq_L5 <- data.frame(id = names(rsq_L5), rsq_L5 = rsq_L5)
  
  rsq_merge <- merge(rsq_L1, rsq_L5 , by = "id")
  
   p[[tissue_gtex]] <-  ggplot(rsq_merge, aes(x=rsq_L1, y=rsq_L5)) + 
    geom_point() +
    labs(x = "rsq-L1", y="rsq-L5") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()
  
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total", "n_rna_total", "n_rna_withcs_L1", "n_rna_withcs_L5", "avg_qtl_L5","n_overlap_withcs", "n_rna_rsq+_L1", "n_rna_rsq+_L5", "n_overlap_rsq+")
sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

grid.arrange(grobs = p, ncol = 4)

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Comparing L=1 & L=5'),options = list(pageLength = 10) )
```




### alt_polyA

```{r}
qtl = "alt_polyA"

L=1
folder_pred_L1 <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights_L1<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample_L1<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

L=5
folder_pred_L5 <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights_L5<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample_L5<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")



```


```{r fig.height=40, fig.width=10, warning=F, message=FALSE}

sum <- c()
p <- list()
for (tissue in name_mapping$Munro_name) {
  

  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ## sample size 
  sample_test <- nrow(read.table(paste0(folder_sample_L1,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample_L1,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ## L=1
  rsq_L1 <- readRDS(paste0(folder_pred_L1, tissue, "_rsq_all_fusion.RDS"))
  n_withcs_L1 <- length(rsq_L1)
  n_posrsq_L1 <- sum(rsq_L1>0,na.rm = T)
  
  ## L=5
  rsq_L5 <- readRDS(paste0(folder_pred_L5, tissue, "_rsq_all_fusion.RDS"))
  n_withcs_L5 <- length(rsq_L5)
  n_posrsq_L5 <- sum(rsq_L5>0,na.rm = T)
  
  n_overlap_withcs <- sum(names(rsq_L1) %in% names(rsq_L5))
  n_overlap_posrsq <- sum(names(rsq_L1[rsq_L1 > 0]) %in% names(rsq_L5[rsq_L5 > 0]))
  
  ## total rna & average qtl
  weights <- readRDS(paste0(folder_weights_L5, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  weights_nonnull <- Filter(Negate(is.null), weights)
  avg_qtl <- mean(unlist(lapply(weights_nonnull,length)),na.rm = T)
  
  tmp_tissue <- c(tissue_gtex,sample_total, n_rna, n_withcs_L1, n_withcs_L5, round(avg_qtl,digits = 4), n_overlap_withcs, n_posrsq_L1, n_posrsq_L5, n_overlap_posrsq)
  sum <- rbind(sum, tmp_tissue)
  
  rsq_L1 <- data.frame(id = names(rsq_L1), rsq_L1 = rsq_L1)
  rsq_L5 <- data.frame(id = names(rsq_L5), rsq_L5 = rsq_L5)
  
  rsq_merge <- merge(rsq_L1, rsq_L5 , by = "id")
  
   p[[tissue_gtex]] <-  ggplot(rsq_merge, aes(x=rsq_L1, y=rsq_L5)) + 
    geom_point() +
    labs(x = "rsq-L1", y="rsq-L5") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()
  
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total", "n_rna_total", "n_rna_withcs_L1", "n_rna_withcs_L5", "avg_qtl_L5","n_overlap_withcs", "n_rna_rsq+_L1", "n_rna_rsq+_L5", "n_overlap_rsq+")
sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

grid.arrange(grobs = p, ncol = 4)

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Comparing L=1 & L=5'),options = list(pageLength = 10) )
```



## Comparing with Munro's prediction model

### RNA stability -- L=1

```{r}
qtl = "stability"
L=1
```


```{r}

folder_pred <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

sum <- c()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  
  weights <- readRDS(paste0(folder_weights, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  mse <- readRDS(paste0(folder_pred, tissue, "_mse_rna.RDS"))
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  n_withcs <- length(mse)
  n_posrsq <- sum(rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- nrow(read.table(paste0(folder_sample,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  ### overlap
  n_overlap_withcs <- sum(names(rsq) %in% df_munro$id)
  n_overlap_posrsq <- sum(names(rsq[rsq > 0]) %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=10, warning=F, message=FALSE}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  rsq <- data.frame(id = names(rsq), rsq = rsq)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  
  p[[tissue_gtex]] <-   ggplot(merged_df, aes(x=rsq, y=lasso.r2)) + 
    geom_point() +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()

}

grid.arrange(grobs = p, ncol = 4)

```


### RNA stability -- L=5

```{r}
qtl = "stability"
L=5
```


```{r}

folder_pred <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

sum <- c()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  
  weights <- readRDS(paste0(folder_weights, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  mse <- readRDS(paste0(folder_pred, tissue, "_mse_rna.RDS"))
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  n_withcs <- length(mse)
  n_posrsq <- sum(rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- nrow(read.table(paste0(folder_sample,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  ### overlap
  n_overlap_withcs <- sum(names(rsq) %in% df_munro$id)
  n_overlap_posrsq <- sum(names(rsq[rsq > 0]) %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=10}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  rsq <- data.frame(id = names(rsq), rsq = rsq)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  
  p[[tissue_gtex]] <-   ggplot(merged_df, aes(x=rsq, y=lasso.r2)) + 
    geom_point() +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()

}

grid.arrange(grobs = p, ncol = 4)

```



### alt_polyA -- L=1

```{r}
qtl = "alt_polyA"
L=1
```


```{r}

folder_pred <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

sum <- c()
for (tissue in name_mapping$Munro_name) {

  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  
  weights <- readRDS(paste0(folder_weights, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  mse <- readRDS(paste0(folder_pred, tissue, "_mse_rna.RDS"))
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  n_withcs <- length(mse)
  n_posrsq <- sum(rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- nrow(read.table(paste0(folder_sample,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  
  ### overlap
  n_overlap_withcs <- sum(names(rsq) %in% df_munro$id)
  n_overlap_posrsq <- sum(names(rsq[rsq > 0]) %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=10, warning=F, message=FALSE}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  rsq <- data.frame(id = names(rsq), rsq = rsq)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  
  p[[tissue_gtex]] <-   ggplot(merged_df, aes(x=rsq, y=lasso.r2)) + 
    geom_point() +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()

}

grid.arrange(grobs = p, ncol = 4)

```


### alt_polyA -- L=5

```{r}
qtl = "alt_polyA"
L=5
```


```{r}

folder_pred <- paste0("/project/xinhe/xsun/weights_training/cv/prediction_refitwcovar/",qtl,"/L",L,"/")
folder_weights<- paste0("/project/xinhe/xsun/weights_training/cv/weights_train_refitwcovar/",qtl,"/L",L,"/")
folder_sample<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

sum <- c()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  
  weights <- readRDS(paste0(folder_weights, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  mse <- readRDS(paste0(folder_pred, tissue, "_mse_rna.RDS"))
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  n_withcs <- length(mse)
  n_posrsq <- sum(rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- nrow(read.table(paste0(folder_sample,tissue,"_sample_test.txt")))
  sample_train <- nrow(read.table(paste0(folder_sample,tissue,"_sample_training.txt")))
  sample_total <- sample_test + sample_train
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  ### overlap
  n_overlap_withcs <- sum(names(rsq) %in% df_munro$id)
  n_overlap_posrsq <- sum(names(rsq[rsq > 0]) %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=10}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
for (tissue in name_mapping$Munro_name) {
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_all_fusion.RDS"))
  rsq <- data.frame(id = names(rsq), rsq = rsq)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  
  p[[tissue_gtex]] <-   ggplot(merged_df, aes(x=rsq, y=lasso.r2)) + 
    geom_point() +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    theme_minimal()

}

grid.arrange(grobs = p, ncol = 4)

```
