---
title: "Training stability weights using FUSION pipeline"
author: "XSun"
date: "2025-04-01"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

## Data source

Normalized RNA phenotype were shared by Munro et al

Covariates are downloaded from https://pantry.pejlab.org/

Genotype are from gtex v8, we imputed the missing genotype using `beagle` 

## Workflow

### Scaling and covariates

We first regressed out the covariates from both the phenotype and genotype matrices. Afterward, we scaled the matrices to ensure comparability across samples.

### Cross validation

We utilized the processed RNA phenotype and genotype data for cross-validation.

For RNA phenotype in each tissue, we partitioned the available samples into training (80%) and testing (20%) datasets.  

**The analysis was limited to the RNA phenotypes that are included in the Munro's weights**

- Training Phase  

For each RNA molecular, we performed the following steps:  

1. **Variant Selection:** We defined a ±50 kb window around the transcription start site (TSS) of each gene, following Munro et al. Variants located within this window were selected for analysis.  
3. **Fine-Mapping with SuSiE:** We applied SuSiE on with `L = 1` and `L = 5` to the processed RNA phenotype and genotype and identified the top variants from the credible sets.  
4. **Effect Size Estimation:** 

We employed two methods to estimate effect sizes:

    **Linear Regression:**

    For the selected variants, we re-fitted a multiple linear regression model:  
   
   ```
   model <- lm(rna_select_train ~ geno_snpselect_train)
   effect_sizes <- coef(model)
   ```  
  
    **Elastic-Net Model:**

    This method was applied only to RNA phenotypes with more than one QTL:

  ```
  enet = cv.glmnet(
  x = geno_snpselect_train,  
  y = rna_select_train,
  alpha = 0.5,
  nfolds = 10,
  standardize = FALSE,
  penalty.factor = (1 - snp_pip)
  )
  
  effect_sizes <- coef(enet)
  ```


The estimated coefficients from this model were used as effect sizes for the selected SNPs.  

- Testing Phase  

Using the trained effect sizes, we predicted RNA phenotypes in the testing dataset and evaluated model performance.  

- Evaluation

We used r2 to evaluate the performance of the prediction model 

r2

$$ R^2 = 1 - \frac{\sum (y_{\text{test}} - y_{\text{pred}})^2}{\sum (y_{\text{test}} - \bar{y}_{\text{test}})^2} $$

- \(y_{\text{test}}\): Observed values in the test set,
- \(y_{\text{pred}}\): Predicted values,
- \(\bar{y}_{\text{test}}\): Mean of the test set observed values.

**We pooled all cross-validated predictions into a single vector to get a global $R^2$ for each RNA phenotype.**



<!-- MSE -->

<!-- $$ \text{MSE} = \frac{1}{n} \sum_{i=1}^n (y_i - \hat{y}_i)^2 $$ -->

<!-- - \( y_i \): Observed value for the \(i\)-th sample, -->
<!-- - \( \hat{y}_i \): Predicted value for the \(i\)-th sample, -->
<!-- - \( n \): Total number of samples. -->


```{r message=F, warning=F}
library(RSQLite)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(tidyr)

name_mapping <- read.table("/project2/xinhe/shared_data/multigroup_ctwas/weights/files_Munro/Munro_name_mapping.txt")
colnames(name_mapping) <- c("Munro_name","gtex_name")

```

## Comparing L=1 and L=5

### RNA stability

```{r}
qtl = "stability"

L=1
folder_pred_L1 <- paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale_allqtl/",qtl,"/L",L,"/rsq_summary_fusionscale_allqtl/")
folder_sample_L1<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")

L=5
folder_pred_L5 <- paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale_allqtl/",qtl,"/L",L,"/rsq_summary_fusionscale_allqtl/")
folder_sample_L5<- paste0("/project/xinhe/xsun/weights_training/cv/samples/",qtl,"/")
folder_round1 <- paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale/",qtl,"/L",L,"/round1/")
```


```{r fig.height=40, fig.width=12, warning=F, message=FALSE}

sum <- c()
p <- list()
for (tissue in name_mapping$Munro_name) {
  
  if(!file.exists(paste0(folder_pred_L1,tissue,"_rsq_fusion_lm.RDS")) | !file.exists(paste0(folder_pred_L5,tissue,"_rsq_fusion_lm.RDS"))) next
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ## sample size 
  sample_test <- readRDS(paste0(folder_round1,tissue,"_samples_testing.RDS"))
  sample_test <- length(sample_test)
  sample_train <- readRDS(paste0(folder_round1,tissue,"_samples_training.RDS"))
  sample_train <- length(sample_train)
  sample_total <- sample_test + sample_train 
  
  ## L=1
  rsq_L1 <- readRDS(paste0(folder_pred_L1, tissue, "_rsq_fusion_lm.RDS"))
  n_withcs_L1 <- nrow(rsq_L1)
  n_posrsq_L1 <- sum(rsq_L1$rsq>0,na.rm = T)
  
  ## L=5
  rsq_L5 <- readRDS(paste0(folder_pred_L5, tissue, "_rsq_fusion_lm.RDS"))
  n_withcs_L5 <- nrow(rsq_L5)
  n_posrsq_L5 <- sum(rsq_L5$rsq>0,na.rm = T)
  
  n_overlap_withcs <- sum(rsq_L1$gene %in% rsq_L5$gene)
  n_overlap_posrsq <- sum(rsq_L1$gene[rsq_L1$rsq > 0] %in% rsq_L1$gene[rsq_L5$rsq > 0])
  
  ## total rna & average qtl
  weights <- readRDS(paste0(folder_round1, tissue, "_training_effectsizes.RDS"))
  n_rna <- length(weights)
  
  weights_nonnull <- Filter(Negate(is.null), weights)
  avg_qtl <- mean(unlist(lapply(weights_nonnull,length)),na.rm = T)
  
  tmp_tissue <- c(tissue_gtex,sample_total, n_rna, n_withcs_L1, n_withcs_L5,round(avg_qtl,digits = 4), n_overlap_withcs, n_posrsq_L1, n_posrsq_L5, n_overlap_posrsq)
  sum <- rbind(sum, tmp_tissue)
  
  rsq_L1_df <- data.frame(id = rsq_L1$gene, rsq_L1 = rsq_L1$rsq, count_L1 = rsq_L1$count)
  rsq_L5_df <- data.frame(id = rsq_L5$gene, rsq_L5 = rsq_L5$rsq, count_L5 = rsq_L5$count)
  
  rsq_merge <- merge(rsq_L1_df, rsq_L5_df , by = "id")
  
  p[[tissue_gtex]] <-  ggplot(rsq_merge, aes(x=rsq_L1, y=rsq_L5, color=factor(count_L5))) + 
    geom_point(size =1) +
    labs(x = "rsq-L1", y="rsq-L5", color = "Count_L5") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    scale_color_brewer(palette = "Set1") +
    theme_minimal()
  
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total", "n_rna_total", "n_rna_withcs_L1", "n_rna_withcs_L5", "avg_qtl_L5", "n_overlap_withcs", "n_rna_rsq+_L1", "n_rna_rsq+_L5", "n_overlap_rsq+")
sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

grid.arrange(grobs = p, ncol = 4)

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Comparing L=1 & L=5'),options = list(pageLength = 10) )
```




## Comparing with Munro's prediction model

### RNA stability -- L=1

```{r}
qtl = "stability"
L=1
```


```{r}

folder_pred <-  paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale_allqtl/",qtl,"/L",L,"/rsq_summary_fusionscale_allqtl/")
folder_round1<- paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale/",qtl,"/L",L,"/round1/")

sum <- c()
for (tissue in name_mapping$Munro_name) {
  
   if(!file.exists(paste0(folder_pred,tissue,"_rsq_fusion_lm.RDS"))) next
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  file_rna_pheno <- paste0("/project/xinhe/xsun/weights_training/data/rna_pheno_norm/",tissue,".",qtl,".norm.bed.gz")
  n_rna <- as.integer(system(sprintf("zcat %s | wc -l", file_rna_pheno), intern = TRUE)) - 1
  
  weights <- readRDS(paste0(folder_round1, tissue, "_training_effectsizes.RDS"))
  
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_fusion_lm.RDS"))
  n_withcs <- nrow(rsq)
  n_posrsq <- sum(rsq$rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- readRDS(paste0(folder_round1,tissue,"_samples_testing.RDS"))
  sample_test <- length(sample_test)
  sample_train <- readRDS(paste0(folder_round1,tissue,"_samples_training.RDS"))
  sample_train <- length(sample_train)
  sample_total <- sample_test + sample_train 
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  ### overlap
  n_overlap_withcs <- sum(rsq$gene %in% df_munro$id)
  n_overlap_posrsq <- sum(rsq$gene[rsq$rsq>0] %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=12, warning=F, message=FALSE}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
p2 <- list()
for (tissue in name_mapping$Munro_name) {
  
  if(!file.exists(paste0(folder_pred,tissue,"_rsq_fusion_lm.RDS"))) next
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_fusion_lm.RDS"))
  rsq <- data.frame(id = rsq$gene, rsq = rsq$rsq, count=rsq$count)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  merged_df <- merged_df %>% 
    filter(!is.na(rsq) & !is.na(lasso.r2) & !is.na(count) & is.finite(rsq) & is.finite(lasso.r2))
  
  p[[tissue_gtex]] <- ggplot(merged_df, aes(x=rsq, y=lasso.r2, color=factor(count))) + 
    geom_point(size =1) +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro", color ="Count") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    scale_color_brewer(palette = "Set1") + 
    theme_minimal()
  
  df <- merged_df %>% pivot_longer(cols = c("rsq","lasso.r2"), names_to = "variable", values_to = "value") %>%
    mutate(variable = recode(variable,
                             rsq = "rsq_susie",
                             lasso.r2 = "rsq_lasso_munro"))
  
  p2[[tissue_gtex]] <- ggplot(df, aes(x=variable, y=value)) + 
    geom_boxplot() +
    labs(x="", y ="rsq", title = tissue_gtex) +
    theme_minimal()
  
}

grid.arrange(grobs = p, ncol = 4)
grid.arrange(grobs = p2, ncol = 4)
```




### RNA stability -- L=5

```{r}
qtl = "stability"
L=5
```


```{r}

folder_pred <-  paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale_allqtl/",qtl,"/L",L,"/rsq_summary_fusionscale_allqtl/")
folder_round1<- paste0("/project/xinhe/xsun/weights_training/cv/multiplesets_fusionscale/",qtl,"/L",L,"/round1/")

sum <- c()
for (tissue in name_mapping$Munro_name) {
  
   if(!file.exists(paste0(folder_pred,tissue,"_rsq_fusion_lm.RDS"))) next
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights
  file_rna_pheno <- paste0("/project/xinhe/xsun/weights_training/data/rna_pheno_norm/",tissue,".",qtl,".norm.bed.gz")
  n_rna <- as.integer(system(sprintf("zcat %s | wc -l", file_rna_pheno), intern = TRUE)) - 1
  
  weights <- readRDS(paste0(folder_round1, tissue, "_training_effectsizes.RDS"))
  
  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_fusion_lm.RDS"))
  n_withcs <- nrow(rsq)
  n_posrsq <- sum(rsq$rsq>0,na.rm = T)
  
  ### sample size 
  sample_test <- readRDS(paste0(folder_round1,tissue,"_samples_testing.RDS"))
  sample_test <- length(sample_test)
  sample_train <- readRDS(paste0(folder_round1,tissue,"_samples_training.RDS"))
  sample_train <- length(sample_train)
  sample_total <- sample_test + sample_train 
  
  ### Munro's weights
  df_munro <- read.table(paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/",tissue,".",qtl,".twas_weights.profile"), header = T)
  n_rna_withweights_munro <- nrow(df_munro)
  ### overlap
  n_overlap_withcs <- sum(rsq$gene %in% df_munro$id)
  n_overlap_posrsq <- sum(rsq$gene[rsq$rsq>0] %in% df_munro$id,na.rm=T)

  tmp_tissue <- c(tissue_gtex,sample_total,n_rna,n_rna_withweights_munro, n_withcs,n_overlap_withcs,n_posrsq,n_overlap_posrsq)
  
  sum <- rbind(sum, tmp_tissue)
}

sum <- as.data.frame(sum)
rownames(sum) <- NULL
colnames(sum) <- c("tissue","sample_size_total","n_rna_total","n_munro_weights","n_rna_withsusie_cs","overlap_cs_munro","n_rna_rsq+","overlap_rsq+_munro")

sum <- sum[order(as.numeric(sum$sample_size_total),decreasing = T),]

DT::datatable(sum,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Summary for the prediction models'),options = list(pageLength = 10) )
```


```{r fig.height=40, fig.width=12, warning=F, message=FALSE}

folder_munroweights<- paste0("/project/xinhe/xsun/weights_training/data/weights_munro/",qtl,"/")

p <- list()
p2 <- list()
for (tissue in name_mapping$Munro_name) {
  
  if(!file.exists(paste0(folder_pred,tissue,"_rsq_fusion_lm.RDS"))) next
  
  tissue_gtex <- name_mapping$gtex_name[which(name_mapping$Munro_name == tissue)]
  
  ### our weights

  rsq <- readRDS(paste0(folder_pred, tissue, "_rsq_fusion_lm.RDS"))
  rsq <- data.frame(id = rsq$gene, rsq = rsq$rsq, count=rsq$count)
  
  ### Munro's weights
  
  summary_munro <- read.table(paste0(folder_munroweights,tissue,".",qtl,".twas_weights.profile"),header = T)
  
  merged_df <- merge(rsq, summary_munro, by= "id")
  merged_df <- merged_df %>% 
    filter(!is.na(rsq) & !is.na(lasso.r2) & !is.na(count) & is.finite(rsq) & is.finite(lasso.r2))
  
  p[[tissue_gtex]] <- ggplot(merged_df, aes(x=rsq, y=lasso.r2, color=factor(count))) + 
    geom_point(size =1) +
    labs(x = "rsq-topsnpfromsusie", y="rsq-lasso-munro", color ="Count") +
    geom_abline(slope = 1, intercept = 0, col="red") + 
    ggtitle(tissue_gtex) + 
    scale_color_brewer(palette = "Set1") + 
    theme_minimal()
  
  df <- merged_df %>% pivot_longer(cols = c("rsq","lasso.r2"), names_to = "variable", values_to = "value") %>%
    mutate(variable = recode(variable,
                             rsq = "rsq_susie",
                             lasso.r2 = "rsq_lasso_munro"))
  
  p2[[tissue_gtex]] <- ggplot(df, aes(x=variable, y=value)) + 
    geom_boxplot() +
    labs(x="", y ="rsq", title = tissue_gtex) +
    theme_minimal()

}

grid.arrange(grobs = p, ncol = 4)
grid.arrange(grobs = p2, ncol = 4)
```

