---
title: "Four expression traits simulation"
author: "shengqian"
date: "2024-5-6"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

This four expression traits simulation study is conducted to evaluate our new cTWAS software performance (parameter estimation, PIP calibration ...). Four expression traits from PredictDB are used in this study, which are Liver, Adipose, Lung and stomach. Liver and Adipose are selected as causal tissues, each with 3% PVE and 0.9% prior. Lung and stomach are non-causal tissues with 0% PVE. Two types of LD between weight SNPs (calculating gene z score) are used and compared in this study. And their performance are very close because most genes only have one weight SNP.  

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ctwas)
library(data.table)
source("/project/xinhe/shengqian/cTWAS_simulation/help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_ctwas_plots.R")
#source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")

plot_PIP <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_merged <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type,".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined_csindex <- function(configtag, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined_merged_csindex <- function(configtag, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}
```


## Simulation 1: Expression trait in liver with 3% PVE and 0.9% Prior

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(1, 1:5, sep = "-")
param_GTEX_df <- load_parameters(results_dir, runtag, simutags, "GTEXLD")
param_UKBB_df <- load_parameters(results_dir, runtag, simutags, "UKBBLD")
```

### Number of causal genes detected (GTEX LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "GTEXLD", PIP_threshold = 0.8)
```

### Number of causal genes detected (UKBB LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
```

### Estimated Prior Inclusion Probability and PVE (GTEX LD)
`````{r, fig.width= 12, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_GTEX_df$`prior_eQTL|Liver`
y2 <- param_GTEX_df$`prior_eQTL|Adipose`
y3 <- param_GTEX_df$`prior_eQTL|Lung`
y4 <- param_GTEX_df$`prior_eQTL|Stomach`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_GTEX_df$`pve_eQTL|Liver`
y2 <- param_GTEX_df$`pve_eQTL|Adipose`
y3 <- param_GTEX_df$`pve_eQTL|Lung`
y4 <- param_GTEX_df$`pve_eQTL|Stomach`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_GTEX_df$`enrichment_eQTL|Liver`
y2 <- param_GTEX_df$`enrichment_eQTL|Adipose`
y3 <- param_GTEX_df$`enrichment_eQTL|Lung`
y4 <- param_GTEX_df$`enrichment_eQTL|Stomach`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### Estimated Prior Inclusion Probability and PVE (UKBB LD)
`````{r, fig.width= 12, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_UKBB_df$`prior_eQTL|Liver`
y2 <- param_UKBB_df$`prior_eQTL|Adipose`
y3 <- param_UKBB_df$`prior_eQTL|Lung`
y4 <- param_UKBB_df$`prior_eQTL|Stomach`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_UKBB_df$`pve_eQTL|Liver`
y2 <- param_UKBB_df$`pve_eQTL|Adipose`
y3 <- param_UKBB_df$`pve_eQTL|Lung`
y4 <- param_UKBB_df$`pve_eQTL|Stomach`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_UKBB_df$`enrichment_eQTL|Liver`
y2 <- param_UKBB_df$`enrichment_eQTL|Adipose`
y3 <- param_UKBB_df$`enrichment_eQTL|Lung`
y4 <- param_UKBB_df$`enrichment_eQTL|Stomach`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0))
est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### PIP attribution among tissues (UKBBLD)
```{r, echo=FALSE, fig.width= 5, fig.height= 4, warning=FALSE}
f1 <- pip_partition_across_tissue(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
f1
```

### PIP Calibration Plot of expression traits (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot of expression traits with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_merged(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_merged(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot of gene level PIP (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined_csindex(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined_csindex(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot of gene level PIP with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined_csindex(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined_csindex(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol =2)
```
