---
title: "Enrichment analysis using fractional model"
author: "XSun"
date: "2024-10-14"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

We do the enrichment analysis using fractional logit model, for the results here: https://sq-96.github.io/multigroup_ctwas_analysis/multi_group_compare_decidingweights_4traits_ess.html


The model is:  `glm(PIP ~ gene set membership, family = quasibinomial('logit'))`. We do this regression for one gene set at a time.

The PIP vector contains: 

-  all genes within the credible set: we use their actual PIPs
-  genes without the credible set & PIP < 0.1:  we set the PIPs as `0.5*min(gene pip within credible set)`


# e + s + st QTL

## LDL-ukb-d-30780_irnt - Liver

### GO biological process

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "LDL-ukb-d-30780_irnt"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gobp.rdata"))

sprintf("the number of pathways included: %s", nrow(summary))

summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```

## IBD-ebi-a-GCST004131 - Colon_Transverse

### GO biological process

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "IBD-ebi-a-GCST004131"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```


## SBP-ukb-a-360 - Artery_Tibial

### GO biological process

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "SBP-ukb-a-360"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```

## WBC-ieu-b-30 - Whole_Blood

### GO biological process

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "WBC-ieu-b-30"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_ess_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```


# e + s QTL

## LDL-ukb-d-30780_irnt - Liver

### GO biological process

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "LDL-ukb-d-30780_irnt"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```

## IBD-ebi-a-GCST004131 - Colon_Transverse

### GO biological process

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "IBD-ebi-a-GCST004131"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```


## SBP-ukb-a-360 - Artery_Tibial

### GO biological process

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "SBP-ukb-a-360"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```

## WBC-ieu-b-30 - Whole_Blood

### GO biological process

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

trait <- "WBC-ieu-b-30"

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gobp.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO biological process, top 50 are shown'),options = list(pageLength = 10) )

```

### GO cellular component 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gocc.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO cellular component, top 50 are shown'),options = list(pageLength = 10) )

```


### GO molecular function 

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_gomf.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for GO molecular function , top 50 are shown'),options = list(pageLength = 10) )

```


### KEGG

```{r, echo=T, mespredage=FALSE, warning=FALSE, fig.width=5, fig.height=5}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/9.deciding_weights_4traits/postprocess/enrichment_espred_", trait, "_kegg.rdata"))
sprintf("the number of pathways included: %s", nrow(summary))
summary <- summary[order(summary$fdr, decreasing = F),]
summary <- summary[1:50,]

DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Enrichment results for KEGG, top 50 are shown'),options = list(pageLength = 10) )

```