---
title: "Predictdb sQTL from Liver"
author: "XSun"
date: "2024-09-25"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

We run `susie_rss` from `susieR` to compare with the ctwas finemapping function here. 

We run with uniform prior. 

# Results 

## Run with ctwas processed zscores

|    | standard susie (PIP_CS) |               |                 |                                                          | ctwas finemapping (PIP_CS) |               |                 |                                                         |
|----|-------------------------|---------------|-----------------|----------------------------------------------------------|----------------------------|---------------|-----------------|---------------------------------------------------------|
|    | PIP_rs6062496(sQTL)     | PIP_rs6089961 | PIP_rs202143810 | othersnps                                                | PIP_rs6062496(sQTL)        | PIP_rs6089961 | PIP_rs202143810 | othersnps                                               |
| L  |                         |               |                 |                                                          |                            |               |                 |                                                         |
| 1  | 1_1                     |               |                 |                                                          | 1_1                        |               |                 |                                                         |
| 2  |                         | 1_1           | 1_2             |                                                          |                            | 1_1           | 1_2             |                                                         |
| 3  |                         | 1_3           | 1_2             | rs112662625 0.89_1;rs113365193 0.06_1                    | 1_1                        | 1_3           | 1_2             |                                                         |
| 4  |                         | 1_1           | 1_2             |                                                          |                            | 1_1           | 1_2             |                                                         |
| 5  |                         | 1_3           | 1_2             | rs112662625 0.90_1;rs113365193 0.06_1                    | 1_1                        | 1_3           | 1_2             |                                                         |
| 6  |                         | 1_1           | 1_2             |                                                          |                            | 1_1           | 1_2             | rs35201382 0.14_1                                       |
| 7  |                         | 1_3           | 1_2             | rs112662625 0.90_1;rs113365193 0.06_1                    | 1_1                        | 1_3           | 1_2             | rs35201382 0.13_3                                       |
| 8  |                         | 1_1           | 1_2             | rs35201382 0.22_1                                        |                            | 1_1           | 1_2             | rs35201382 0.30_1                                       |
| 9  |                         | 1_5           | 1_2             | rs35201382 0.21_5, rs112662625 0.90_1;rs113365193 0.07_1 | 1_1                        | 1_3           | 1_2             | rs35201382 0.29_3                                       |
| 10 |                         | 1_5           | 1_2             | rs35201382 0.2_5, rs367993153 0.91_1, rs1295810 0.08_1   |                            | 1_1           | 1_2             | rs35201382 0.27_1, rs1295810 0.94_9, rs367993153 0.03_9 |


```{r}
load("/project/xinhe/xsun/multi_group_ctwas/8.deciding_weights/data/R2_topsnp.rdata")
DT::datatable(R2,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','R2 for the SNPs above'),options = list(pageLength = 10) )
```


## Run with raw zscores

For standard susie, if we run with raw zscores computed from the origin vcf file: 

L=1~10, rs6062496 is the only SNP with PIP > 0.8 & in CS. The PIP for this SNP is 1. For the other two SNPs, rs6089961 and rs202143810, the highest PIP is 0.002.

## Compare the z_scores 

```{r}
load("/project/xinhe/xsun/multi_group_ctwas/8.deciding_weights/data/z_snp_merge.rdata")
z_snp_merge$z_computefromvcf <- z_snp_merge$ES_raw/z_snp_merge$SE_raw

DT::datatable(z_snp_merge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','z_snp'),options = list(pageLength = 10) )
plot(z_snp_merge$z_ctwasprocess,z_snp_merge$z_computefromvcf)

index <- which(z_snp_merge$z_computefromvcf != -z_snp_merge$z_ctwasprocess)
DT::datatable(z_snp_merge[index,],caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','The outlier SNPs'),options = list(pageLength = 10) )
```




