---
title: "methylation_analysis"
output: html_document
date: '2024-10-22'
---

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(ggplot2)
library(ggVennDiagram)
library(gridExtra)
library(data.table)
library(ctwas)
library(data.table)
library(tidyverse)
library(RSQLite)
library(dplyr)
library(magrittr)
library(pheatmap)

plot_piechart <- function(ctwas_parameters, colors, by) {
  # Create the initial data frame
  data <- data.frame(
    category = names(ctwas_parameters$prop_heritability),
    percentage = ctwas_parameters$prop_heritability
  )
  
  # Split the category into context and type
  data <- data %>%
    mutate(
      context = sub("\\|.*", "", category),
      type = sub(".*\\|", "", category)
    )
  
  # Aggregate the data based on the 'by' parameter
  if (by == "type") {
    data <- data %>%
      group_by(type) %>%
      summarize(percentage = sum(percentage)) %>%
      mutate(category = type)  # Use type as the new category
  } else if (by == "context") {
    data <- data %>%
      group_by(context) %>%
      summarize(percentage = sum(percentage)) %>%
      mutate(category = context)  # Use context as the new category
  } else {
    stop("Invalid 'by' parameter. Use 'type' or 'context'.")
  }
  
  # Calculate percentage labels for the chart
  data$percentage_label <- paste0(round(data$percentage * 100, 1), "%")
  
  # Create the pie chart
  pie <- ggplot(data, aes(x = "", y = percentage, fill = category)) +
    geom_bar(stat = "identity", width = 1) +
    coord_polar("y", start = 0) +
    theme_void() +  # Remove background and axes
    geom_text(aes(label = percentage_label), 
              position = position_stack(vjust = 0.5), size = 3) +  # Adjust size as needed
    scale_fill_manual(values = colors) +  # Custom colors
    labs(fill = "Category") +  # Legend title
    ggtitle("Percent of Heritability")  # Title
  
  return(pie)
}

draw_gene_piechart_type <- function(data, colors) {
  # Filter data based on combined_pip
  data <- data[data$combined_pip > 0.8, ]
  
  # Count occurrences by eQTL, sQTL, and stQTL
  byeQTL <- nrow(data[data$eQTL_pip / data$combined_pip > 0.8, ])
  bysQTL <- nrow(data[data$sQTL_pip / data$combined_pip > 0.8, ])
  bystQTL <- nrow(data[data$stQTL_pip / data$combined_pip > 0.8, ])
  
  # Count occurrences for combined sQTL and stQTL
  bysQTLstQTL <- nrow(data[((data$stQTL_pip + data$sQTL_pip) / data$combined_pip) > 0.8 &
                             data$stQTL_pip / data$combined_pip < 0.8 &
                             data$sQTL_pip / data$combined_pip < 0.8, ])
  
  # Count unspecified
  unspecified <- nrow(data) - byeQTL - bysQTL - bystQTL - bysQTLstQTL
  
  # Create vectors for plotting
  n <- c(byeQTL, bysQTL, bystQTL, bysQTLstQTL, unspecified)
  prop <- round(n / nrow(data), 3)
  labels = c("by eQTL", "by sQTL", "by stQTL", "by sQTL+stQTL", "unspecified")
  lab.ypos = cumsum(prop) - 0.5 * prop
  
  # Prepare the data frame for plotting
  df <- data.frame("n" = n,
                   "class" = labels,
                   "prop" = prop,
                   "lab.ypos" = lab.ypos)
  
  # Generate the pie chart
  ggplot(df, aes(x = "", y = prop, fill = class)) +
    geom_bar(width = 1, stat = "identity", color = "white") +
    coord_polar("y", start = 0) +
    geom_text(aes(label = n),
              position = position_stack(vjust = 0.5)) +
    scale_fill_manual(values = colors) +  # Ensure 'palette' is defined
    theme_void()
}

draw_gene_piechart_tissue <- function(data, colors){
  
  data <- data[data$combined_pip>0.8,]
  tissues <- colnames(data)[3:7]
  tissues <- sub("_pip$", "", tissues)
  colnames(data)[3:7] <- paste0("tissue",c(1:5))
  
  
  bytissue1 <- nrow(data[data$tissue1/data$combined_pip>0.8,])
  bytissue2 <- nrow(data[data$tissue2/data$combined_pip>0.8,])
  bytissue3 <- nrow(data[data$tissue3/data$combined_pip>0.8,])
  bytissue4 <- nrow(data[data$tissue4/data$combined_pip>0.8,])
  bytissue5 <- nrow(data[data$tissue5/data$combined_pip>0.8,])
  unspecified <- nrow(data)-bytissue1-bytissue2-bytissue3-bytissue4-bytissue5
  
  n <- c(bytissue1,bytissue2,bytissue3,bytissue4,bytissue5,unspecified)
  
  prop <- round(n/nrow(data),3)
  labels = c(tissues,"unspecified")
  lab.ypos = cumsum(prop) - 0.5*prop
  df <- data.frame("n" = n,
                   "class" = labels,
                   "prop" = prop,
                   "lab.ypos" = lab.ypos)
  p <- ggplot(df, aes(x = "", y = prop, fill = class)) +
    geom_bar(width = 1, stat = "identity", color = "white") +
    coord_polar("y", start = 0)+
    geom_text(aes(label = n),
              position = position_stack(vjust = 0.5))+
    scale_fill_manual(values = colors) +
    theme_void()
  
  return(p)
}

plot_heatmap <- function(heatmap_data, main) {
  
  rownames(heatmap_data) <- heatmap_data$gene_name
  heatmap_data <- heatmap_data %>% dplyr::select(-gene_name, -combined_pip)
  
  if(nrow(heatmap_data) ==1){
    
    heatmap_data <- rbind(heatmap_data,rep(0,ncol(heatmap_data)))
    rownames(heatmap_data)[2] <- "fake_gene_for_plotting"
    
  }
  
  heatmap_matrix <- as.matrix(heatmap_data)
  
  p <- pheatmap(heatmap_matrix,
                cluster_rows = F,   # Cluster the rows (genes)
                cluster_cols = F,   # Cluster the columns (QTL types)
                color = colorRampPalette(c("white", "red"))(50), # Color gradient
                display_numbers = TRUE, # Display numbers in cells
                main = main,labels_row = rownames(heatmap_data), silent = T)
  
  return(p)
}
```
### Fusion Lasso model of DNA methylation

I built lasso model of DNA methylation with FUSION for Whole Blood and Colon Transverse. Similar to meQTL mapping, for each CpG site, I extracted surrounding 500kb genptypes and train lasso models with cross validation. With heritability cutoff p<0.001, I have about 10,500 and 37,500 CpG sites in whole blood and colon transverse. Among which, 2452 and 28505 CpG sites are also in QTL mapping. Colon have more overlaps than whole blood. The average cross-validation R2 for lasso in whole blood and colon transverse are 0.260 and 0.231. In the single QTL approach (qval < 0.001), we have 7,720 and 91,466 CpG sites.

```{r, echo=FALSE, warning=FALSE}
# Arrange the two plots side by side
library(ggplot2)
library(ggVennDiagram)
library(gridExtra)
library(data.table)
library(ctwas)
fusion_model <- fread("/project2/xinhe/shengqian/fusion_twas-master/methylationwholeblood.profile",sep='\t')
fusion_model <- fusion_model[!is.na(fusion_model$lasso.r2),]
QTL_data <- fread("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mqtl/WholeBlood.regular.perm.fdr.txt")
QTL_data <- QTL_data[QTL_data$qval<0.001,]

venn1 <- ggVennDiagram(list(QTL = QTL_data$cpg_id, FUSION = fusion_model$id),category.names=c("","")) +
  ggtitle("Whole Blood") + theme(legend.position = "none") + scale_fill_gradient(low = NA, high = NA) + annotate("text", x = 0, y = - 2.5, label = "QTL", size = 5) +
  annotate("text", x = 0, y = 6.5, label = "FUSION", size = 5)

fusion_model <- fread("/project2/xinhe/shengqian/fusion_twas-master/methylation_colon.profile",sep='\t')
fusion_model <- fusion_model[!is.na(fusion_model$lasso.r2),]
QTL_data <- fread("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mqtl/ColonTransverse.regular.perm.fdr.txt")
QTL_data <- QTL_data[QTL_data$qval<0.001,]

venn2 <- ggVennDiagram(list(QTL = QTL_data$cpg_id, FUSION = fusion_model$id),category.names=c("","")) +
  ggtitle("Colon Transverse") + theme(legend.position = "none") + scale_fill_gradient(low = NA, high = NA) + annotate("text", x = 0, y = - 2.5, label = "QTL", size = 5) +
  annotate("text", x = 0, y = 6.5, label = "FUSION", size = 5)

grid.arrange(
  grobs = list(venn1, venn2),
  ncol = 2
)
```

### cTWAS parameters with methylation lasso models
```{r, echo=FALSE, fig.width=12, fig.height=8}
param <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi/ibd_multi.param.RDS")
gwas_n <- 59957
colors <- c(  "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728",  "#9467bd", "#8c564b", "#e377c2", "#7f7f7f",  "#bcbd22",  "#17becf",  "#f7b6d2",  "#c5b0d5",  "#9edae5", "#ffbb78",  "#98df8a",  "#ff9896" )
make_convergence_plots(param, gwas_n,colors = colors)
```
### Percent of heritability with methylation lasso models
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
ctwas_parameters <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi_top/ibd_multi_top.ctwas_parameters.RDS")
pve_pie_by_type_multi <- plot_piechart(ctwas_parameters = ctwas_parameters, colors = colors, by = "type")
pve_pie_by_context_multi <- plot_piechart(ctwas_parameters = ctwas_parameters, colors = colors, by = "context")
gridExtra::grid.arrange(pve_pie_by_type_multi,pve_pie_by_context_multi, ncol = 2)
```

### Top cTWAS genes with methylation lasso models
```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
gwas_n <- 59957
finemap_res <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi/ibd_multi.finemap_regions_res.RDS")
gene_annot <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_E_S_M_mapping.RDS")
susie_alpha_res <- anno_susie_alpha_res(finemap_res$susie_alpha_res,
                                        mapping_table = gene_annot,
                                        map_by = "molecular_id",
                                        drop_unmapped = TRUE)


combined_pip_by_type <- combine_gene_pips(susie_alpha_res, 
                                             group_by = "gene_name",
                                             by = "type",
                                             method = "combine_cs",
                                             filter_cs = TRUE,
                                             include_cs_id = FALSE)

combined_pip_by_context <- combine_gene_pips(susie_alpha_res, 
                                             group_by = "gene_name",
                                             by = "context",
                                             method = "combine_cs",
                                             filter_cs = TRUE,
                                             include_cs_id = FALSE)

DT::datatable(combined_pip_by_type[combined_pip_by_type$combined_pip>0.8,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Combined PIP by omics'),options = list(pageLength = 10) )

DT::datatable(combined_pip_by_context[combined_pip_by_context$combined_pip>0.8,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Combined PIP by tissue'),options = list(pageLength = 10) )
```

### cTWAS parameters with methylation single QTL models
```{r, echo=FALSE, fig.width=12, fig.height=8}
param <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi_top/ibd_multi_top.param.RDS")
gwas_n <- 59957
colors <- c(  "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728",  "#9467bd", "#8c564b", "#e377c2", "#7f7f7f",  "#bcbd22",  "#17becf",  "#f7b6d2",  "#c5b0d5",  "#9edae5", "#ffbb78",  "#98df8a",  "#ff9896" )
make_convergence_plots(param, gwas_n,colors = colors)
```
### Percent of heritability with methylation single QTL models
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
ctwas_parameters <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi/ibd_multi.ctwas_parameters.RDS")
pve_pie_by_type_multi <- plot_piechart(ctwas_parameters = ctwas_parameters, colors = colors, by = "type")
pve_pie_by_context_multi <- plot_piechart(ctwas_parameters = ctwas_parameters, colors = colors, by = "context")
gridExtra::grid.arrange(pve_pie_by_type_multi,pve_pie_by_context_multi, ncol = 2)
```

### Top cTWAS genes with methylation single QTL models
```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
gwas_n <- 59957
finemap_res <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ibd_multi_top/ibd_multi_top.finemap_regions_res.RDS")
gene_annot <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_E_S_M_mapping.RDS")

susie_alpha_res <- anno_susie_alpha_res(finemap_res$susie_alpha_res,
                                        mapping_table = gene_annot,
                                        map_by = "molecular_id",
                                        drop_unmapped = TRUE)


combined_pip_by_type <- combine_gene_pips(susie_alpha_res, 
                                          group_by = "gene_name",
                                          by = "type",
                                          method = "combine_cs",
                                          filter_cs = TRUE,
                                          include_cs_id = FALSE)

combined_pip_by_context <- combine_gene_pips(susie_alpha_res, 
                                             group_by = "gene_name",
                                             by = "context",
                                             method = "combine_cs",
                                             filter_cs = TRUE,
                                             include_cs_id = FALSE)

DT::datatable(combined_pip_by_type[combined_pip_by_type$combined_pip>0.8,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Combined PIP by omics'),options = list(pageLength = 10) )

DT::datatable(combined_pip_by_context[combined_pip_by_context$combined_pip>0.8,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Combined PIP by tissue'),options = list(pageLength = 10) )
```
