---
title: "Enrichment analysis -- enriched pathways"
author: "XSun"
date: "2024-01-08"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Overview

We performed gene set enrichment analysis for the [genes with susie pip > 0.8](https://sq-96.github.io/multigroup_ctwas_analysis/multi_tissue_ldmerge.html) using logistic susie(https://karltayeb.github.io/logistic-susie-gsea/index.html) and susie. 

## Logistic Susie

We binarize the response variable Y based on our selected gene list(genes with susie pip>0.8 from multi-tissue ctwas analysis). Y is a n*1 vector (n=#of genes)

The explanatory variable X indicate if the gene is part of a specific pathway. X is a n*m matrix, n=#of genes, m=# of pathways

## Susie

The response variable Y is the outcome of MAGMA (z-scores of the genes with susie pip > 0.8).

The explanatory variable X is the same with logistic susie

## Pathways 

The pathways are from Go Biological Process (gobp), Go Molecular Function (gomf), Go Cellular Component (gocc) and KEGG.

## Functions

```{r warning=F,message=FALSE}
library(gseasusie)
library(tidyverse)
create_pip_datatable <- function(linear_fit) {
  pip <- linear_fit$pip
  pip <- as.data.frame(cbind(names(pip), pip))
  rownames(pip) <- seq(1, nrow(pip), by = 1)
  pip <- pip[order(as.numeric(pip$pip), decreasing = TRUE), ]
  colnames(pip) <- c("pwy", "PIP")

  DT::datatable(pip, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Susie PIPs'), 
                options = list(pageLength = 10))
}


```

# aFib

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/aFib-ebi-a-GCST006414_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}

create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/aFib-ebi-a-GCST006414_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/aFib-ebi-a-GCST006414_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/aFib-ebi-a-GCST006414_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


# IBD

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/IBD-ebi-a-GCST004131_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/IBD-ebi-a-GCST004131_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/IBD-ebi-a-GCST004131_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/IBD-ebi-a-GCST004131_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```



# LDL

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/LDL-ukb-d-30780_irnt_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/LDL-ukb-d-30780_irnt_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/LDL-ukb-d-30780_irnt_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/LDL-ukb-d-30780_irnt_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```



# SBP

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SBP-ukb-a-360_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SBP-ukb-a-360_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SBP-ukb-a-360_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SBP-ukb-a-360_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```



# SCZ

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SCZ-ieu-b-5102_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SCZ-ieu-b-5102_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SCZ-ieu-b-5102_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/SCZ-ieu-b-5102_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```



# WBC

## Go Biological Process

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/WBC-ieu-b-30_cutoff08_gobp.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Go Molecular Function

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/WBC-ieu-b-30_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```


## Cellular Component

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/WBC-ieu-b-30_cutoff08_gocc.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

## KEGG

### Logistice Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie_old/WBC-ieu-b-30_cutoff08_kegg.rdata")
gseasusie::enrichment_volcano(logistic.fit, ora)
gseasusie::interactive_table(logistic.fit, ora)
```

### Susie

```{r warning=F,message=FALSE}
create_pip_datatable(linear_fit = linear.fit.subset)
```

