---
title: "Enrichment analysis for 6 Traits, 5 tissues, eQTL + sQTL + stQTL -- compute ukbb LD, eqtl, sqtl from predictdb; stQTL from Munro et al"
author: "XSun"
date: "2024-06-13"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

  
```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
library(tidyr)
library(dplyr)
library(VennDiagram)
library(ggplot2)

traits <- c("LDL-ukb-d-30780_irnt","SBP-ukb-a-360","WBC-ieu-b-30","aFib-ebi-a-GCST006414","SCZ-ieu-b-5102","IBD-ebi-a-GCST004131")
dbs <- c("GO_Biological_Process_2023","GO_Cellular_Component_2023","GO_Molecular_Function_2023")

trait<- "LDL-ukb-d-30780_irnt"
db <- "GO_Biological_Process_2023"

```


# Methods 

We do enrichment analysis for the genes with PIP > 0.8 here: https://sq-96.github.io/multigroup_ctwas_analysis/multi_group_6traits_15weights_ess.html

The gene set membership was downloaded here: https://maayanlab.cloud/Enrichr/#libraries
  
  
  ## Background genes 
  
  For Fractional model and Fisher exact test, we selected 2 kind of backgroud genes

- All genes used in ctwas
- All genes in the selected geneset database.

For enrichR, the background genes are not modifiable. The background genes are all genes in the selected geneset database


## Remove the redundant 

## Using EnrichR package.

This package was used in our earlier ctwas paper. 

- It takes a list of genes(genes with PIP > 0.8) as input and returns the enriched GO terms with adjusted p-values.

## Fractional model 

The model is:  `glm(PIP ~ gene set membership, family = quasibinomial('logit'))`. We do this regression for one gene set at a time.

The PIP vector contains: 
  
  -  all genes within the credible set: we use their actual PIPs
-  genes without the credible set & PIP < 0.1:  we set the PIPs as `0.5*min(gene pip within credible set)`

The 2 different baselines: 
  
  1. All genes from ctwas. Here, `genes without the credible set & PIP < 0.1` includes only the genes used in ctwas.
2. All genes from the geneset database. Here, `genes without the credible set & PIP < 0.1` includes the union of all genes from the GO terms in the geneset database.


## Fisher exact test

We assign 1 to the genes with PIP > 0.5/0.8 & in cs and 0 for others. We name this vector as binarized_PIP. We test the association between the binarized_PIP and geneset_membership. 

The testing matrix is: 
  
  | geneset_membership | 0   | 1   |
  |--------------------|-----|-----|
  | **binarized_pip 0**|  a  |  b  |
  | **binarized_pip 1**|  c  |  d  |
  
  Where:
  
  - `a` is the count where `binarized_pip = 0` and `geneset_membership = 0`.
- `b` is the count where `binarized_pip = 0` and `geneset_membership = 1`.
- `c` is the count where `binarized_pip = 1` and `geneset_membership = 0`.
- `d` is the count where `binarized_pip = 1` and `geneset_membership = 1`.

The 2 different baselines: 
  
  1. All genes from ctwas. Here, `geneset_membership` matrix includes only the genes used in ctwas.
2. All genes from the geneset database. Here, `geneset_membership` matrix includes the union of all genes from the GO terms in the geneset database.



# Summary for the number of Go terms with p-values < 0.001

```{r echo=T, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
load("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_summary_for_all_redundant_p.rdata")
DT::datatable(summary,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Number of enriched GO terms under different settings'),options = list(pageLength = 20) )
```


  
  
# Comparing the p-values from Enrichr and Fisher exact test -- baseline genes are all genes from gene sets
  
```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

p_enrichr <- c()
p_fet <- c()

#compare_diff <- c()
for (trait in traits) {
  for (db in dbs) {
    
    file_enrichr <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_redundant_",trait,"_",db,".rdata")
    if(file.exists(file_enrichr)) {
      load(file_enrichr)
      load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_fisher_blgeneset_pip08_",trait,"_",db,".rdata"))
      
      merged <- merge(db_enrichment, summary, by.x = "Term", by.y = "GO")
      p_enrichr <- c(p_enrichr, merged$P.value)
      p_fet <- c(p_fet, merged$pvalue)
      
      #compare_diff <- rbind(compare_diff, merged)
    }
    
  }
}


p_enrichr <- as.numeric(p_enrichr)
p_fet <- as.numeric(p_fet)

df <- data.frame(p_enrichr = p_enrichr, p_fet = p_fet)

# Fit a linear model to calculate the slope
fit <- lm(p_fet ~ p_enrichr)
slope <- coef(fit)[2]
intercept <- coef(fit)[1]

ggplot(df, aes(x = p_enrichr, y = p_fet)) +
  geom_point() +  # Add points
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +  # y = x line
  geom_smooth(method = "lm", se = FALSE, color = "blue") +  # Best-fit line
  annotate("text", x = max(p_enrichr) * 0.8, y = max(p_fet) * 0.9, 
           label = paste0("Slope: ", round(slope, 3)),
           color = "blue") +  # Slope text
  annotate("text", x = max(p_enrichr) * 0.8, y = max(p_enrichr) * 0.8, 
           label = "y = x", color = "red", size = 5, hjust = -0.1, vjust = -0.5) +  # y = x text near the line
  ggtitle("Comparison of p-values between enrichr and FET, baseline -- all genes from gene sets") +  # Add title
  xlab("Enrichr p-values") +  # x-axis label
  ylab("FET p-values") +  # y-axis label
  theme_minimal()

```


# Comparing the GO terms reported by FET and Fractional model -- p-values < 0.001, baseline genes are genes used in ctwas, redundant terms NOT removed


```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

pval <- 0.001

all_fractional <- c()
all_fet <- c()
for (trait in traits) {
  for (db in dbs) {
    
    file_fet <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_fisher_blctwas_pip08_",trait,"_",db,".rdata")
    load(file_fet)
    all_fet <- rbind(all_fet,summary[as.numeric(summary$pvalue) < pval,])
    
    
    file_fractional <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_fractional_",trait,"_",db,".rdata")
    load(file_fractional)
    summary$trait <- trait
    summary$db <- db
    all_fractional <- rbind(all_fractional,summary[as.numeric(summary$pvalue) < pval,])
    
  }
}

all_fractional <- all_fractional[complete.cases(all_fractional),]
all_fractional$id <- paste0(all_fractional$trait,"-",all_fractional$db,"-",all_fractional$GO)
all_fet$id <- paste0(all_fet$trait,"-",all_fet$db,"-",all_fet$GO)


venn.plot <- draw.pairwise.venn(
  area1 = nrow(all_fractional),          # Size of Group A
  area2 = nrow(all_fet),          # Size of Group B
  cross.area = sum(all_fractional$id %in% all_fet$id),     # Overlap between Group A and Group B
  category = c("Fractional", "FET"),  # Labels for the groups
  fill = c("red", "blue"),             # Colors for the groups
  lty = "blank",                       # Line type for the circles
  cex = 2,                             # Font size for the numbers
  cat.cex = 2                          # Font size for the labels
)

all_fractional <- all_fractional[,c("trait","db","GO","pvalue","fdr","id")]
DT::datatable(all_fractional[!all_fractional$id %in% all_fet$id,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Unique GO terms for fractional model'),options = list(pageLength = 10) )

DT::datatable(all_fet[!all_fet$id %in% all_fractional$id,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Unique GO terms for FET'),options = list(pageLength = 10) )

```


# Comparing the GO terms reported by FET and Fractional model -- p-values < 0.001, baseline genes are all genes from gene sets, redundant terms NOT removed


```{r, echo=T, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}

pval <- 0.001

all_fractional <- c()
all_fet <- c()
for (trait in traits) {
  for (db in dbs) {
    
    file_fet <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_fisher_blgeneset_pip08_",trait,"_",db,".rdata")
    load(file_fet)
    all_fet <- rbind(all_fet,summary[as.numeric(summary$pvalue) < pval,])
    
    
    file_fractional <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/postprocess/enrichment_fractional_blgeneset_",trait,"_",db,".rdata")
    load(file_fractional)
    summary$trait <- trait
    summary$db <- db
    all_fractional <- rbind(all_fractional,summary[as.numeric(summary$pvalue) < pval,])
    
  }
}

all_fractional <- all_fractional[complete.cases(all_fractional),]
all_fractional$id <- paste0(all_fractional$trait,"-",all_fractional$db,"-",all_fractional$GO)
all_fet$id <- paste0(all_fet$trait,"-",all_fet$db,"-",all_fet$GO)


venn.plot <- draw.pairwise.venn(
  area1 = nrow(all_fractional),          # Size of Group A
  area2 = nrow(all_fet),          # Size of Group B
  cross.area = sum(all_fractional$id %in% all_fet$id),     # Overlap between Group A and Group B
  category = c("Fractional", "FET"),  # Labels for the groups
  fill = c("red", "blue"),             # Colors for the groups
  lty = "blank",                       # Line type for the circles
  cex = 2,                             # Font size for the numbers
  cat.cex = 2                          # Font size for the labels
)


all_fractional <- all_fractional[,c("trait","db","GO","pvalue","fdr","id")]
DT::datatable(all_fractional[!all_fractional$id %in% all_fet$id,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Unique GO terms for fractional model'),options = list(pageLength = 10) )

DT::datatable(all_fet[!all_fet$id %in% all_fractional$id,],caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Unique GO terms for FET'),options = list(pageLength = 10) )
```
