---
title: "6 Traits, 5 tissues, eQTL + sQTL + stQTL – compute ukbb LD, eqtl, sqtl from predictdb; stQTL from Munro et al; post-processing"
author: "XSun"
date: "2024-12-09"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

We compare post-processed results with the original results: https://sq-96.github.io/multigroup_ctwas_analysis/multi_group_6traits_15weights_ess.html

The post-processing steps include the following:

1. **Region Merging**  

   For the regions with `susie_pip > 0.5` 
   
2. **LD Mismatch Fixing**

-   Regions were selected where nonSNP_PIP > 0.5.
-   For genes with `susie_pip > thresholds` (0.5 and 0.2), we performed LD mismatch diagnosis.
-   To address LD mismatches, two strategies were employed:
    -   Fine-mapping the region without LD.
    -   Removing mismatched SNPs, updating gene Z-scores, and re-fine-mapping with LD.

```{r message=FALSE, warning=FALSE}
library(ctwas)
library(EnsDb.Hsapiens.v86)
library(ggplot2)
library(gridExtra)
library(dplyr)

ens_db <- EnsDb.Hsapiens.v86

mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
mapping_munro <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
mapping_two <- rbind(mapping_predictdb,mapping_munro)
# 
# 
# compute_pip_per_cs <- function(combined_data, susie_data) {
#   # Initialize an empty list to store results
#   details <- list()
#   
#   # Iterate over each unique gene name in the combined data
#   unique_genes <- unique(combined_data$gene_name)
#   
#   for (genename in unique_genes) {
#     # dplyr::filter susie data for the current gene
#     susie_alpha_res_multi_per_gene <- susie_data %>%
#       dplyr::filter(gene_name == genename)
#     
#     # Get all unique credible sets for the current gene
#     cs_all <- unique(susie_alpha_res_multi_per_gene$susie_set[susie_alpha_res_multi_per_gene$in_cs])
#     
#     if (length(cs_all) > 1) {
#       # dplyr::filter complete cases and those in credible sets
#       susie_alpha_res_multi_per_gene <- susie_alpha_res_multi_per_gene %>%
#         dplyr::filter(complete.cases(cs), in_cs)
#       
#       # Summarize the data
#       summed_alpha_with_details <- susie_alpha_res_multi_per_gene %>%
#         group_by(susie_set) %>%
#         summarise(
#           total_susie_alpha = round(sum(susie_alpha, na.rm = TRUE), digits = 3),
#           num_molecular_traits = n(),
#           ids_pip = paste0(id, "(", round(susie_alpha, digits = 3), ")", collapse = ", ")
#         )
#       
#       # Add gene name to the summarized data
#       summed_alpha_with_details$gene_name <- genename
#       
#       # Append the result to the details list
#       details[[length(details) + 1]] <- summed_alpha_with_details
#     }
#   }
#   
#   # Combine all results into a single data frame
#   final_details <- bind_rows(details)
#   
#   if(nrow(final_details) > 0){
#     final_details <- final_details[,c("gene_name","susie_set","total_susie_alpha","num_molecular_traits","ids_pip")]
#     colnames(final_details) <- c("gene_name","CS","total_PIP_CS","num_molecular_traits_CS","ids_pip_CS")
#   }
#   
#   
#   return(final_details)
# }

```


# aFib-ebi-a-GCST006414

```{r message=FALSE, warning=FALSE}
trait <- "aFib-ebi-a-GCST006414"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```



# LDL-ukb-d-30780_irnt

```{r message=FALSE, warning=FALSE}
trait <- "LDL-ukb-d-30780_irnt"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```



# IBD-ebi-a-GCST004131

```{r message=FALSE, warning=FALSE}
trait <- "IBD-ebi-a-GCST004131"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)


finemap_res_ldmm_nold <- anno_finemap_res(finemap_res_ldmm_nold,
                                                        snp_map = updated_data_res_regionmerge[["updated_snp_map"]],
                                                        mapping_table = mapping_two,
                                                        add_gene_annot = TRUE,
                                                        map_by = "molecular_id",
                                                        drop_unmapped = TRUE,
                                                        add_position = TRUE,
                                                        use_gene_pos = "mid")
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```

```{r message=FALSE, warning=FALSE, fig.width=12, fig.height=12}
weights_origin <- readRDS(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/",trait,".preprocessed.weights.RDS"))


finemap_res_rm <- anno_finemap_res(finemap_res_rm,
                                          snp_map = updated_data_res_regionmerge[["updated_snp_map"]],
                                          mapping_table = mapping_two,
                                          add_gene_annot = TRUE,
                                          map_by = "molecular_id",
                                          drop_unmapped = TRUE,
                                          add_position = TRUE,
                                          use_gene_pos = "mid")
print("locus plot -- after region merge")
make_locusplot(finemap_res_rm,
               region_id = "9_136047132_136605890",
               ens_db = ens_db,
               weights = weights_origin,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = TRUE,
               color_pval_by = "cs",
               color_pip_by = "cs")




finemap_res_ldmm_nold <- anno_finemap_res(finemap_res_ldmm_nold,
                                          snp_map = updated_data_res_regionmerge[["updated_snp_map"]],
                                          mapping_table = mapping_two,
                                          add_gene_annot = TRUE,
                                          map_by = "molecular_id",
                                          drop_unmapped = TRUE,
                                          add_position = TRUE,
                                          use_gene_pos = "mid")
print("locus plot -- LD mismatch: no LD")

make_locusplot(finemap_res_ldmm_nold,
               region_id = "9_136047132_136605890",
               ens_db = ens_db,
               weights = weights_origin,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = TRUE,
               color_pval_by = "cs",
               color_pip_by = "cs")



finemap_res_ldmm_removesnp <- anno_finemap_res(finemap_res_ldmm_removesnp,
                                   snp_map = updated_data_res_regionmerge[["updated_snp_map"]],
                                   mapping_table = mapping_two,
                                   add_gene_annot = TRUE,
                                   map_by = "molecular_id",
                                   drop_unmapped = TRUE,
                                   add_position = TRUE,
                                   use_gene_pos = "mid")
print("locus plot -- LD mismatch: snp removed")
make_locusplot(finemap_res_ldmm_removesnp,
               region_id = "9_136047132_136605890",
               ens_db = ens_db,
               weights = weights_origin,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = TRUE,
               color_pval_by = "cs",
               color_pip_by = "cs")

```

# SBP-ukb-a-360

```{r message=FALSE, warning=FALSE}
trait <- "SBP-ukb-a-360"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```

# SCZ-ieu-b-5102

```{r message=FALSE, warning=FALSE}
trait <- "SCZ-ieu-b-5102"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```



# WBC-ieu-b-30

```{r message=FALSE, warning=FALSE}
trait <- "WBC-ieu-b-30"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```

## LD-mismatch 

### Diagnosis

```{r message=FALSE, warning=FALSE}


load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres02_", trait, ".rdata"))

pip_02 <- data.frame(
  "PIP Threshold" = "0.2",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_diagnosis_pipthres05_", trait, ".rdata"))


pip_05 <- data.frame(
  "PIP Threshold" = "0.5",
  "Number of Selected Regions" = length(selected_region_ids),
  "Number of Problematic Genes" = length(problematic_genes),
  "Number of Problematic Regions" = length(problematic_region_ids),
  "Number of Problematic SNPs" = length(res_ldmismatch$problematic_snps),
  "Number of Flipped SNPs" = length(res_ldmismatch$flipped_snps)
)


results_table <- rbind(pip_02, pip_05)

DT::datatable(results_table,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','LD mismatch diagnosis table for different gene cutoff'),options = list(pageLength = 10) )

```

### Comparing 2 LD mismatch fixing methods

```{r message=FALSE, warning=FALSE, fig.width=13, fig.height=4}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_nold_",trait,".rdata"))
finemap_res_ldmm_nold <- res_ldmm_nold$finemap_res
load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/ldmismatch_pipthres05_removesnp_",trait,".rdata"))
finemap_res_ldmm_removesnp <- res_ldmm_removesnp$finemap_res

finemap_res_ldmm_nold_problematic_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$region_id %in% problematic_region_ids & finemap_res_ldmm_nold$type != "SNP",]
finemap_res_ldmm_removesnp_problematic_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$region_id %in% problematic_region_ids & finemap_res_ldmm_removesnp$type != "SNP",]

merge_2method <- merge(finemap_res_ldmm_nold_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p1 <- ggplot(data = merge_2method, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_noLD", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

finemap_res_rm_problematic_gene <- finemap_res_rm[finemap_res_rm$region_id %in% problematic_region_ids & finemap_res_rm$type != "SNP",]

merge_rm_ldmm_nold <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_nold_problematic_gene, by ="id")

p2 <- ggplot(data = merge_rm_ldmm_nold, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_noLD") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()


merge_rm_ldmm_removesnp <-  merge(finemap_res_rm_problematic_gene,finemap_res_ldmm_removesnp_problematic_gene, by ="id")

p3 <- ggplot(data = merge_rm_ldmm_removesnp, aes(x= susie_pip.x, y= susie_pip.y)) + 
  geom_point() +
  labs(x="PIP_after_regionmerge", y="PIP_removesnp") + 
  geom_abline(slope = 1, intercept = 0, col ="red") + 
  ggtitle("problematic regions only, genes only") +
  theme_minimal()

grid.arrange(p1,p2,p3, ncol = 3)
```

## Comparing z-scores and susie_pip

```{r message=FALSE, warning=FALSE,fig.width=17, fig.height=4}
finemap_res_origin <- ctwas_res_origin$finemap_res
finemap_res_origin_gene <- finemap_res_origin[finemap_res_origin$type != "SNP",]

p1 <- ggplot(data = finemap_res_origin_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("Original ctwas results") +
  theme_minimal()


finemap_res_rm_gene <- finemap_res_rm[finemap_res_rm$type != "SNP",]

p2 <- ggplot(data = finemap_res_rm_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After region merge") +
  theme_minimal()


finemap_res_ldmm_nold_gene <- finemap_res_ldmm_nold[finemap_res_ldmm_nold$type !="SNP",]

p3 <- ggplot(data = finemap_res_ldmm_nold_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- noLD") +
  theme_minimal()

finemap_res_ldmm_removesnp_gene <- finemap_res_ldmm_removesnp[finemap_res_ldmm_removesnp$type !="SNP",]

p4 <- ggplot(data = finemap_res_ldmm_removesnp_gene, aes(x= abs(z), y= susie_pip)) + 
  geom_point() +
  ggtitle("After LD mismatch fixed -- SNP removed") +
  theme_minimal()


grid.arrange(p1,p2,p3,p4, ncol = 4)
```

