---
title: "Validation for multi-tissue results"
author: "XSun"
date: "2024-01-11"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---


# Overview

We validate [genes with susie pip > 0.8](https://sq-96.github.io/multigroup_ctwas_analysis/multi_tissue_ldmerge.html) by some trait-related pathways. Pathways are selected using MAGMA. Due to the correlation among candidate pathways, we employ SuSiE and logistic SuSiE to fine-map the pathways.

## Model

The model is $y=X*w$

y is an n-dimensional vector representing gene-trait associations (n = number of genes). 

 - For SuSiE, y consists of z-scores computed by MAGMA
 - for logistic SuSiE, y is a binary vector indicating gene-trait relationships (genes with FDR < 0.05 as per MAGMA are marked 1).

X is an n×m matrix (m = number of pathways) indicating gene membership in specific pathways.

## Benchmarks

The model fitting results in pathway weights, from which we predict gene labels $\hat{y}$. We then categorize genes based on these new labels. 

- For SuSiE, we compute the p-values from the new labels(z-scores), then compute FDR. Genes with FDR < 0.5 are considered benchmarks. 
- For logistic SuSiE, genes with labels > 0.5 are considered benchmarks.

## Testing genes

Genes from ctwas results are divided into two groups based on their SuSiE PIPs: high (>0.8) and moderate (0.8 > PIP > 0.5). 

## Fisher exact test

We assess whether high-PIP genes are more enriched in our benchmarks than moderate-PIP genes using Fisher exact tests. 

The testing matrix is: 

```{r}

fisher_matrix <- matrix(c("n1","n2","n3","n4"),nrow = 2,ncol = 2)
rownames(fisher_matrix) <- c("#included","#notincluded")
colnames(fisher_matrix) <- c("pip08","pip05")

print(fisher_matrix)
```

## Pathways

The pathways are from Go Biological Process (gobp), Go Molecular Function (gomf), Go Cellular Component (gocc) and KEGG.


## Functions

```{r warning=F,message=FALSE}
library(gseasusie)
library(tidyverse)

coeftable_linear<- function(linear_fit) {
  coef <- susieR::coef.susie(linear_fit)
  coef <- as.data.frame(cbind(names(coef), coef))
  colnames(coef) <- c("pwy", "beta")
  rownames(coef) <- seq(1,nrow(coef),by=1)
  DT::datatable(coef, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Correct coef for linear fitting'), 
                options = list(pageLength = 5))
}

```


# aFib-ebi-a-GCST006414

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correct")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/aFib-ebi-a-GCST006414_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_aFib-ebi-a-GCST006414_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_aFib-ebi-a-GCST006414_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# IBD-ebi-a-GCST004131
## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/IBD-ebi-a-GCST004131_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_IBD-ebi-a-GCST004131_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_IBD-ebi-a-GCST004131_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# LDL-ukb-d-30780_irnt
## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/LDL-ukb-d-30780_irnt_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_LDL-ukb-d-30780_irnt_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_LDL-ukb-d-30780_irnt_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# SBP-ukb-a-360

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SBP-ukb-a-360_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SBP-ukb-a-360_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SBP-ukb-a-360_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```



# SCZ-ieu-b-5102

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/SCZ-ieu-b-5102_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SCZ-ieu-b-5102_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_SCZ-ieu-b-5102_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


# WBC-ieu-b-30

## Susie & Logistic Susie results

### Go Biological Process

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gobp.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Molecular Function

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gomf.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### Go Cellular Component

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_gocc.rdata")

gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)

```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```


### KEGG

#### Susie

```{r warning=F,message=FALSE}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/susie/WBC-ieu-b-30_kegg.rdata")
gseasusie::enrichment_volcano(linear.fit, linear.ora)
print("please not the beta column (computed by logistic susie package) in the table below is not correct for linear susie, the beta is calculated from colSums(fit$alpha * fit$mu) but for linear fit, it misses a scale factor. Other columns are correctt")
gseasusie::interactive_table(linear.fit, linear.ora)
coeftable_linear(linear_fit = linear.fit)
```

#### Logistice Susie

```{r warning=F,message=FALSE}
gseasusie::enrichment_volcano(logistic.fit, logistic.ora)
gseasusie::interactive_table(logistic.fit, logistic.ora)
```

## Validation

```{r}
load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_WBC-ieu-b-30_linearsusie.rdata")

DT::datatable(df_all, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Gene labels'), 
                options = list(pageLength = 5))

```


### Susie

```{r}
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


### Logistic Susie

```{r}

load("/project/xinhe/xsun/ctwas/4.multi_tissue_process/results/fisher/fisher_WBC-ieu-b-30_logisusie.rdata")
DT::datatable(linear_selected, 
                caption = htmltools::tags$caption(style = 'caption-side: left; text-align: left; color:black; font-size:150%;', 
                                                  'Benchmark genes'), 
                options = list(pageLength = 5))
print(fisher_matrix)
print(fisher_result)
```


