---
title: "tissue selection"
output: html_document
date: '2024-10-22'
editor_options: 
  chunk_output_type: console
---

### Method
1. Run all tissues jointly (very fast if weights have been harmonized).
2. Rank tissues by %h2g and select reasonable top ones.

### Summary
1. For IBD, colon transverse and whole blood have much higher %h2g than other tissues. 
2. For LDL, liver has much higher %h2g than other tissues.
3. For SBP, the top five ones all make sense, which are artery aorta, brain cortex, artery tibial, cell cultured fibroblasts and adrenal gland.
4. For WBC, whole blood has much higher %h2g than other tissues. 
5. For SCZ, the top ones are basal ganglia, cerebellum, hippocampus, hemisphere, cortex ...

```{r echo=FALSE}
get_results <- function(param_file,ctwas_file){
  ctwas_parameters <- readRDS(param_file)
  prop_h2g <- as.data.frame(cbind(names(ctwas_parameters$prop_heritability),ctwas_parameters$prop_heritability,ctwas_parameters$group_pve,c(ctwas_parameters$enrichment,1),ctwas_parameters$group_pvalue,ctwas_parameters$odds_ratio))
  prop_h2g$V2 <- round(as.numeric(prop_h2g$V2),4)
  prop_h2g$V3 <- round(as.numeric(prop_h2g$V3),4)
  prop_h2g$V4 <- round(as.numeric(prop_h2g$V4),4)
  prop_h2g$V5 <- round(as.numeric(prop_h2g$V5),4)
  prop_h2g$V6 <- round(as.numeric(prop_h2g$V6),4)
  rownames(prop_h2g) <- NULL
  prop_h2g <- prop_h2g[order(-prop_h2g$V2),]
  colnames(prop_h2g) <- c("group","%h2g","h2g","enrichment","enrichment_pvalue","odds_ratio")
  prop_h2g <- prop_h2g[prop_h2g$group!="SNP",]
  #pvalue_df <- data.frame()
  #finemap_res <- readRDS(ctwas_file)
  #finemap_res <- finemap_res$finemap_res
  #for(i in unique(finemap_res$group)){
  #  snp_pip <- sum(finemap_res[finemap_res$group=="SNP","susie_pip"])
  #  snp_n <- dim(finemap_res[finemap_res$group=="SNP",])[1]
  #  tissue_pip <- sum(finemap_res[finemap_res$group==i,"susie_pip"])
  #  tissue_n <- dim(finemap_res[finemap_res$group==i,])[1]
    #y <- c(finemap_res[finemap_res$group=="SNP","susie_pip"],finemap_res[finemap_res$group==i,"susie_pip"])
    #x <- as.factor(c(rep(0,snp_n),rep(1,tissue_n)))
    #res <- glm(y ~ x, family = quasibinomial('logit'))
    #res_sum <- summary(res)
    #fractional_pvalue <- res_sum$coefficients[2,4]
  #  data <- matrix(c(tissue_pip, tissue_n, snp_pip, snp_n), nrow = 2, byrow = TRUE)
  #  data <- round(data)
  #  result <- fisher.test(data)
  #  pvalue_df <- rbind(pvalue_df,data.frame(group=i,enrichment_pvalue2=round(-log10(result$p.value),3),odds_ratio2=round(result$estimate,3),low=round(result$conf.int[1],3),up=round(result$conf.int[2],3)))
  #}
  #output <- merge(prop_h2g, pvalue_df, by = "group")
  #output <- output[order(-output$`%h2g`),]
  return(prop_h2g)
}
```

### IBD results (Inflammatory bowel disease)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### WBC results (White blood cell count)
```{r, echo=FALSE, fig.width=10, fig.height=8, eval=FALSE}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### RA results (Rheumatoid arthritis)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ra_all_tissue_E/ra_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ra_all_tissue_E/ra_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### SBP results (Systolic blood pressure)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### DBP results (Diastolic blood pressure)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### HTN results (Hypertension)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/htn_all_tissue_E/htn_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/htn_all_tissue_E/htn_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### SCZ results (Schizophrenia)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### BIP results (Bipolar disorder)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### MDD results (Major depressive disorder)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### LDL results (low-density lipoprotein)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### TG results (Triglycerides)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/tg_all_tissue_E/tg_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/tg_all_tissue_E/tg_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### BMI results (Body mass index)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### T2D results (Type 2 diabetes)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_all_tissue_E/t2d_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_all_tissue_E/t2d_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```


```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_highPVE/"
runtag = "one_tissue"
pvalue <- c()
simutags <- paste(1, 1:20, sep = "-")
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".ctwas_parameters.RDS")
for(j in param_files){
  ctwas_parameters <- readRDS(j)
  pvalue <- c(pvalue,10^(-ctwas_parameters$group_pvalue[1]))
}
```


```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_highPVE/"
runtag = "one_tissue"
enrichment_list <- list()
for(i in 1:7){
  simutags <- paste(i, 1:20, sep = "-")
  param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".ctwas_parameters.RDS")
  enrichment <- c()
  for(j in param_files){
    ctwas_parameters <- readRDS(j)
    enrichment <- c(enrichment,ctwas_parameters$enrichment)
  }
  enrichment_list[[i]]<-enrichment
}

enrichment_df <- as.data.frame(do.call(cbind,enrichment_list))
rownames(enrichment_df) <- 1:20
colnames(enrichment_df) <- c("group1","group10","group20","group40","group60","group80","group100")
```

```{r, echo=FALSE, eval=FALSE}
# Convert the data frame to a long format
library(tidyr)
long_df <- pivot_longer(enrichment_df, cols = everything(), names_to = "Group", values_to = "Value")
long_df$Group <- factor(long_df$Group, levels = c("group1", "group10", "group20", "group40", "group60", "group80", "group100"))
# Plot using ggplot2
library(ggplot2)

ggplot(long_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Groups",
       y = "Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_highPVE/"
runtag = "one_tissue"
enrichment_list <- list()
for(i in 1:7){
  simutags <- paste(i, 1:20, sep = "-")
  param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".ctwas_parameters.RDS")
  enrichment <- c()
  for(j in param_files){
    ctwas_parameters <- readRDS(j)
    enrichment <- c(enrichment,ctwas_parameters$odds_ratio)
  }
  enrichment_list[[i]]<-enrichment
}

enrichment_df <- as.data.frame(do.call(cbind,enrichment_list))
#rownames(enrichment_df) <- 1:20
colnames(enrichment_df) <- c("group1","group10","group20","group40","group60","group80","group100")
```

```{r, echo=FALSE, eval=FALSE}
# Convert the data frame to a long format
library(tidyr)
long_df <- pivot_longer(enrichment_df, cols = everything(), names_to = "Group", values_to = "Value")
long_df$Group <- factor(long_df$Group, levels = c("group1", "group10", "group20", "group40", "group60", "group80", "group100"))
# Plot using ggplot2
library(ggplot2)

ggplot(long_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Groups",
       y = "Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

