---
title: "Real data analysis"
author: "shengqian"
date: "2024-5-26"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
library(tidyverse)
library(ggplot2)
source("/project2/xinhe/shengqian/cTWAS/for_xiaotong/R/ctwas_summarize_finemap_res.R")
load("/project2/xinhe/shared_data/multigroup_ctwas/weights/E_S_A_mapping.RData")
E_S_A_mapping <- E_S_A_mapping[E_S_A_mapping$gene_type=="protein_coding",] #limit to protein coding genes
```

## LDL
```{r echo=FALSE}
gwas_n <- 343621
param <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.param.RDS")
ctwas_parameters <- summarize_param(param, gwas_n)
```

### Heritability contribution by types
```{r}
DT::datatable(sum_pve_across_types(ctwas_parameters))
```

### Heritability contribution by contexts
```{r}
DT::datatable(sum_pve_across_contexts(ctwas_parameters))
```

```{r echo=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.finemap_res.RDS")
combined_pip_by_types <- sum_pip_across_types(finemap_res,E_S_A_mapping)
combined_pip_by_contexts <- sum_pip_across_contexts(finemap_res,E_S_A_mapping)
```

### Combined PIP by types
```{r}
DT::datatable(combined_pip_by_types[combined_pip_by_types$combined_pip>0.8,])
```

### Combined PIP by contexts
```{r}
DT::datatable(combined_pip_by_contexts[combined_pip_by_contexts$combined_pip>0.8,])
```

### Specific molecular traits of top genes
```{r}
draw_gene_piechart(combined_pip_by_types)
```

```{r}
library(EnsDb.Hsapiens.v86)
#finemap_res <- finemap_res[finemap_res$cs_index!=0,]
finemap_SNP_res <- finemap_res[finemap_res$type=="SNP",]
finemap_gene_res <- finemap_res[finemap_res$type!="SNP",]
finemap_gene_res$gene <- sapply(finemap_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
finemap_gene_res <- finemap_gene_res %>% plyr::join(mapping_data, by = "gene") %>% dplyr::select(-gene) %>% na.omit()
finemap_gene_res <- finemap_gene_res %>% group_by(id) %>% mutate(susie_pip_adjusted = ifelse(n() > 1, susie_pip / n(), susie_pip)) %>% ungroup() %>% dplyr::select(-susie_pip) %>% dplyr::rename(susie_pip = susie_pip_adjusted)
finemap_gene_res$pos <- (as.numeric(finemap_gene_res$start) + as.numeric(finemap_gene_res$end))/2
finemap_gene_res <- finemap_gene_res[,c("chrom","pos","id","type","context","group","z","region_id","mu2","cs_index","genename","susie_pip")]
colnames(finemap_gene_res) <- c("chrom","pos","id","type","context","group","z","region_id","mu2","cs_index","gene_name","susie_pip")
finemap_SNP_res$gene_name <- NA
finemap_SNP_res <- finemap_SNP_res[,c("chrom","pos","id","type","context","group","z","region_id","mu2","cs_index","gene_name","susie_pip")]
finemap_res <- rbind(finemap_SNP_res,finemap_gene_res)
weights <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.preprocessed.weights.RDS")
ens_db <- EnsDb.Hsapiens.v86
region_info <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/region_info.RDS")
region_data <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.region_data.RDS")
```

```{r}
make_locusplot(finemap_res = finemap_res,region_id = "19:9127717-11173352",weights=weights,ens_db = ens_db,cor_dir = "/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/LDL-ukb-d-30780_irnt/cor_matrix/",region_info = region_info,region_data = region_data)
```

## IBD
```{r echo=FALSE}
gwas_n <- 59957
param <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/IBD-ebi-a-GCST004131/IBD-ebi-a-GCST004131.param.RDS")
ctwas_parameters <- summarize_param(param, gwas_n)
```

### Heritability contribution by types
```{r}
DT::datatable(sum_pve_across_types(ctwas_parameters))
```

### Heritability contribution by contexts
```{r}
DT::datatable(sum_pve_across_contexts(ctwas_parameters))
```

```{r echo=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/IBD-ebi-a-GCST004131/IBD-ebi-a-GCST004131.finemap_res.RDS")
combined_pip_by_types <- sum_pip_across_types(finemap_res,E_S_A_mapping)
combined_pip_by_contexts <- sum_pip_across_contexts(finemap_res,E_S_A_mapping)
```

### Combined PIP by types
```{r}
DT::datatable(combined_pip_by_types[combined_pip_by_types$combined_pip>0.8,])
```

### Combined PIP by contexts
```{r}
DT::datatable(combined_pip_by_contexts[combined_pip_by_contexts$combined_pip>0.8,])
```

### Specific molecular traits of top genes
```{r}
draw_gene_piechart(combined_pip_by_types)
```

## SCZ
```{r echo=FALSE}
gwas_n <- 127906
param <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/SCZ-ieu-b-5102/SCZ-ieu-b-5102.param.RDS")
ctwas_parameters <- summarize_param(param, gwas_n)
```

### Heritability contribution by types
```{r}
DT::datatable(sum_pve_across_types(ctwas_parameters))
```

### Heritability contribution by contexts
```{r}
DT::datatable(sum_pve_across_contexts(ctwas_parameters))
```

```{r echo=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/SCZ-ieu-b-5102/SCZ-ieu-b-5102.finemap_res.RDS")
combined_pip_by_types <- sum_pip_across_types(finemap_res,E_S_A_mapping)
combined_pip_by_contexts <- sum_pip_across_contexts(finemap_res,E_S_A_mapping)
```

### Combined PIP by types
```{r}
DT::datatable(combined_pip_by_types[combined_pip_by_types$combined_pip>0.8,])
```

### Combined PIP by contexts
```{r}
DT::datatable(combined_pip_by_contexts[combined_pip_by_contexts$combined_pip>0.8,])
```

### Specific molecular traits of top genes
```{r}
draw_gene_piechart(combined_pip_by_types)
```

## SBP 
```{r echo=FALSE}
gwas_n <- 317754
param <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/SBP-ukb-a-360/SBP-ukb-a-360.param.RDS")
ctwas_parameters <- summarize_param(param, gwas_n)
```

### Heritability contribution by types
```{r}
DT::datatable(sum_pve_across_types(ctwas_parameters))
```

### Heritability contribution by contexts
```{r}
DT::datatable(sum_pve_across_contexts(ctwas_parameters))
```

```{r echo=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/SBP-ukb-a-360/SBP-ukb-a-360.finemap_res.RDS")
combined_pip_by_types <- sum_pip_across_types(finemap_res,E_S_A_mapping)
combined_pip_by_contexts <- sum_pip_across_contexts(finemap_res,E_S_A_mapping)
```

### Combined PIP by types
```{r}
DT::datatable(combined_pip_by_types[combined_pip_by_types$combined_pip>0.8,])
```

### Combined PIP by contexts
```{r}
DT::datatable(combined_pip_by_contexts[combined_pip_by_contexts$combined_pip>0.8,])
```

### Specific molecular traits of top genes
```{r}
draw_gene_piechart(combined_pip_by_types)
```
## WBC 
```{r echo=FALSE}
gwas_n <- 563946
param <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/WBC-ieu-b-30/WBC-ieu-b-30.param.RDS")
ctwas_parameters <- summarize_param(param, gwas_n)
```

### Heritability contribution by types
```{r}
DT::datatable(sum_pve_across_types(ctwas_parameters))
```

### Heritability contribution by contexts
```{r}
DT::datatable(sum_pve_across_contexts(ctwas_parameters))
```

```{r echo=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/5.multi_group_testing/results/WBC-ieu-b-30/WBC-ieu-b-30.finemap_res.RDS")
combined_pip_by_types <- sum_pip_across_types(finemap_res,E_S_A_mapping)
combined_pip_by_contexts <- sum_pip_across_contexts(finemap_res,E_S_A_mapping)
```

### Combined PIP by types
```{r}
DT::datatable(combined_pip_by_types[combined_pip_by_types$combined_pip>0.8,])
```

### Combined PIP by contexts
```{r}
DT::datatable(combined_pip_by_contexts[combined_pip_by_contexts$combined_pip>0.8,])
```

### Specific molecular traits of top genes
```{r}
draw_gene_piechart(combined_pip_by_types)
```
