---
title: "tissue selection"
output: html_document
date: '2024-10-22'
editor_options: 
  chunk_output_type: console
---

### Method
1. Run all tissues jointly (very fast if weights have been harmonized).
2. Rank tissues by %h2g and select reasonable top ones.

### Summary
1. For IBD, colon transverse and whole blood have much higher %h2g than other tissues. 
2. For LDL, liver has much higher %h2g than other tissues.
3. For SBP, the top five ones all make sense, which are artery aorta, brain cortex, artery tibial, cell cultured fibroblasts and adrenal gland.
4. For WBC, whole blood has much higher %h2g than other tissues. 
5. For SCZ, the top ones are basal ganglia, cerebellum, hippocampus, hemisphere, cortex ...

```{r echo=FALSE}
get_results <- function(param_file,ctwas_file){
  ctwas_parameters <- readRDS(param_file)
  prop_h2g <- as.data.frame(cbind(names(ctwas_parameters$prop_heritability),ctwas_parameters$prop_heritability,ctwas_parameters$group_pve,c(ctwas_parameters$enrichment,1),ctwas_parameters$group_pvalue,ctwas_parameters$odds_ratio))
  prop_h2g$V2 <- round(as.numeric(prop_h2g$V2),4)
  prop_h2g$V3 <- round(as.numeric(prop_h2g$V3),4)
  prop_h2g$V4 <- round(as.numeric(prop_h2g$V4),4)
  prop_h2g$V5 <- round(as.numeric(prop_h2g$V5),4)
  prop_h2g$V6 <- round(as.numeric(prop_h2g$V6),4)
  rownames(prop_h2g) <- NULL
  prop_h2g <- prop_h2g[order(-prop_h2g$V2),]
  colnames(prop_h2g) <- c("group","%h2g","h2g","enrichment","enrichment_pvalue1","odds_ratio1")
  
  pvalue_df <- data.frame()
  finemap_res <- readRDS(ctwas_file)
  finemap_res <- finemap_res$finemap_res
  for(i in unique(finemap_res$group)){
    snp_pip <- sum(finemap_res[finemap_res$group=="SNP","susie_pip"])
    snp_n <- dim(finemap_res[finemap_res$group=="SNP",])[1]
    tissue_pip <- sum(finemap_res[finemap_res$group==i,"susie_pip"])
    tissue_n <- dim(finemap_res[finemap_res$group==i,])[1]
    #y <- c(finemap_res[finemap_res$group=="SNP","susie_pip"],finemap_res[finemap_res$group==i,"susie_pip"])
    #x <- as.factor(c(rep(0,snp_n),rep(1,tissue_n)))
    #res <- glm(y ~ x, family = quasibinomial('logit'))
    #res_sum <- summary(res)
    #fractional_pvalue <- res_sum$coefficients[2,4]
    data <- matrix(c(tissue_pip, tissue_n, snp_pip, snp_n), nrow = 2, byrow = TRUE)
    data <- round(data)
    result <- fisher.test(data)
    pvalue_df <- rbind(pvalue_df,data.frame(group=i,enrichment_pvalue2=round(-log10(result$p.value),3),odds_ratio2=round(result$estimate,3),low=round(result$conf.int[1],3),up=round(result$conf.int[2],3)))
  }
  output <- merge(prop_h2g, pvalue_df, by = "group")
  output <- output[order(-output$`%h2g`),]
  return(output)
}
```

### IBD results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### LDL results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### SBP results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### DBP results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### WBC results
```{r, echo=FALSE, fig.width=10, fig.height=8, eval=FALSE}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```


### SCZ results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```


### BIP results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### MDD results
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```
