---
title: "real data coloc analysis"
output: html_document
date: '2024-10-22'
editor_options: 
  chunk_output_type: console
---

### Method
1. For each trait, select regions with at lease one high PIP expression/splicing trait (PIP>0.8)
- based on multi-cTWAS results with three molecular traits (eQTL,sQTL,stQTL) from five tissues.
2. Run coloc with eQTL and sQTL full summary statistics from five tissues
- no stQTL full summary statistics
3. Comparing the number of expression and splicing molecular traits identified by coloc (PP4>0.8), single-cTWAS (PIP>0.8) and multi-cTWAS (PIP>0.8)
- don't include stability traits identified by multi-cTWAS

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE, include=FALSE}
library(ggplot2)
library(ggVennDiagram)
library(gridExtra)
library(data.table)
library(ctwas)
library(data.table)
library(tidyverse)
library(RSQLite)
library(dplyr)
library(magrittr)
library(pheatmap)

library(EnsDb.Hsapiens.v86)
ens_db <- EnsDb.Hsapiens.v86

GWAS_tissues <- list("WBC-ieu-b-30" = c("Whole_Blood","Cells_Cultured_fibroblasts","Esophagus_Muscularis","Pancreas","Nerve_Tibial"),
                    "SBP-ukb-a-360" = c("Artery_Aorta","Brain_Cortex","Artery_Tibial","Cells_Cultured_fibroblasts","Brain_Cerebellar_Hemisphere"),
                    "LDL-ukb-d-30780_irnt" = c("Liver","Spleen","Esophagus_Gastroesophageal_Junction","Esophagus_Muscularis","Esophagus_Mucosa"),
                    "aFib-ebi-a-GCST006414" = c("Heart_Atrial_Appendage","Muscle_Skeletal","Heart_Left_Ventricle","Thyroid","Cells_EBV-transformed_lymphocytes"),
                    "IBD-ebi-a-GCST004131" = c("Whole_Blood","Colon_Transverse","Esophagus_Muscularis","Artery_Coronary","Brain_Nucleus_accumbens_basal_ganglia"),
                    "SCZ-ieu-b-5102" = c("Brain_Hippocampus","Brain_Cerebellum","Brain_Cerebellar_Hemisphere","Brain_Nucleus_accumbens_basal_ganglia","Brain_Cortex"),
                    "BMI-panukb" = 419163,
                    "Height-panukb" = 419596,
                    "PLT-panukb" = 407992,
                    "RBC-panukb" = 407995,
                    "HB-panukb" =  407994,
                    "HTN-panukb" = 420473,
                    "RA-panukb" =  376792,
                    "T1D-GCST90014023" = 520580,
                    "ATH_gtexukb" = 337119,
                    "T2D-panukb" = 418949,
                    "MDD-ieu-b-102" = 500199,
                    "BIP-ieu-b-5110" = 413466,
                    "ADHD-ieu-a-1183" = 55374,
                    "ASD-ieu-a-1185" = 46351,
                    "PD-ieu-b-7" = 482730,
                    "NS-ukb-a-230" = 274108)

get_top_mts_coloc <- function(colocf,group){
  coloc_res <- readRDS(colocf)
  #coloc_res <- coloc_res[coloc_res$PP4>0.8,]
  coloc_res$id <- paste0(coloc_res$id,"|",group)
  rownames(coloc_res) <- NULL
  return(coloc_res)
}

get_top_mts_ctwas <- function(ctwasf,regions){
  finemap_res <- readRDS(ctwasf)
  finemap_res <- finemap_res$finemap_res
  finemap_res <- finemap_res[finemap_res$region_id %in% regions,]
  finemap_res <- finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)),]
  return(finemap_res)
}

get_results <- function(gwas_id,gwas_name){
  tissues <- GWAS_tissues[[gwas_id]]
  outputdir = paste0("/project/xinhe/shengqian/coloc_GWAS_analysis/data_test/",gwas_name,"_coloc/")
  weight_tags <- paste0("weight",1:10)
  colocfs <- paste0(outputdir, gwas_name, "_",weight_tags, ".coloc_res.RDS")
  
  coloc_mts <- rbind(get_top_mts_coloc(colocfs[1], paste0(tissues[1],"_eQTL")),
                     get_top_mts_coloc(colocfs[2], paste0(tissues[1],"_sQTL")),
                     get_top_mts_coloc(colocfs[3], paste0(tissues[2],"_eQTL")),
                     get_top_mts_coloc(colocfs[4], paste0(tissues[2],"_sQTL")),
                     get_top_mts_coloc(colocfs[5], paste0(tissues[3],"_eQTL")),
                     get_top_mts_coloc(colocfs[6], paste0(tissues[3],"_sQTL")),
                     get_top_mts_coloc(colocfs[7], paste0(tissues[4],"_eQTL")),
                     get_top_mts_coloc(colocfs[8], paste0(tissues[4],"_sQTL")),
                     get_top_mts_coloc(colocfs[9], paste0(tissues[5],"_eQTL")),
                     get_top_mts_coloc(colocfs[10],paste0(tissues[5],"_sQTL")))
  
  coloc_mts <- coloc_mts[coloc_mts$PP4>0.8,]
  num_coloc_gene <- length(unique(coloc_mts$gene_name))
  
  weights <- readRDS(paste0("/project/xinhe/shengqian/ctwas_GWAS_analysis/results_ES/",gwas_id,"/",gwas_id,".preprocessed.weights.RDS"))
  mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_E_S_M_mapping.RDS")
  finemap_res <- readRDS(paste0("/project/xinhe/shengqian/ctwas_GWAS_analysis/results_ES/",gwas_id,"/",gwas_id,".finemap_regions_res.RDS"))
  finemap_res <- finemap_res$susie_alpha_res
  finemap_res <- anno_susie_alpha_res(finemap_res,
                                      mapping_table = mapping_predictdb,
                                      map_by = "molecular_id",
                                      drop_unmapped = TRUE)
  
  combined_pip <- combine_gene_pips(finemap_res,
                                    group_by = "gene_name",
                                    by = "type",
                                    method = "combine_cs",
                                    filter_cs = TRUE,
                                    include_cs_id = TRUE)
  
  combined_pip$region_id <- sapply(combined_pip$combined_cs_id,function(x){unlist(strsplit(x,"[.]"))[1]})
  combined_pip <- combined_pip[combined_pip$combined_pip>0.8,]
  
  num_multi_ctwas_gene <- length(combined_pip$gene_name)
  
  region_singals <- unique(combined_pip$region_id)
  num_coloc_ctwas_gene <- length(unique(coloc_mts[coloc_mts$region_id %in% region_singals, ]$gene_name))
  
  coloc_data <- as.vector(table(unique(coloc_mts[,c("gene_name","region_id")])$region_id))
  multictwas_data <- as.vector(table(combined_pip$region_id))
  
  # Combine data into a data frame
  df <- data.frame(
    value = c(coloc_data, multictwas_data),
    group = c(rep("Coloc",length(coloc_data)),rep("Multi-cTWAS",length(multictwas_data)))
  )
  
  p1 <- ggplot(df, aes(x = value, fill = group)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = max(coloc_data)) +
    scale_fill_manual(values = c("blue", "red")) +
    labs(title = gwas_id, x = "Value", y = "Frequency", fill = "Dataset") + theme_minimal()
  
  ctwas_coloc_data <- coloc_mts[coloc_mts$region_id %in% region_singals, ]
  ctwas_coloc_data <- as.vector(table(unique(ctwas_coloc_data[,c("gene_name","region_id")])$region_id))
  # Combine data into a data frame
  df <- data.frame(
    value = c(ctwas_coloc_data, multictwas_data),
    group = c(rep("Coloc",length(ctwas_coloc_data)),rep("Multi-cTWAS",length(multictwas_data)))
  )
  
  p2 <- ggplot(df, aes(x = value, fill = group)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = max(coloc_data)) +
    scale_fill_manual(values = c("blue", "red")) +
    labs(title = gwas_id, x = "Value", y = "Frequency", fill = "Dataset") + theme_minimal()
  
  return(list("num_coloc_gene" = num_coloc_gene,
              "num_coloc_ctwas_gene" = num_coloc_ctwas_gene,
              "num_multi_ctwas_gene" = num_multi_ctwas_gene,
              "p1" = p1,
              "p2" = p2))
}
```


```{r, message=FALSE, echo=FALSE}
LDL_results <- get_results("LDL-ukb-d-30780_irnt","LDL")
WBC_results <- get_results("WBC-ieu-b-30","WBC")
SBP_results <- get_results("SBP-ukb-a-360","SBP")
SCZ_results <- get_results("SCZ-ieu-b-5102","SCZ")
IBD_results <- get_results("IBD-ebi-a-GCST004131","IBD")
```

### number of genes identified by each method
```{r echo=FALSE}
library(ggplot2) 

gfg <- data.frame(x = c(LDL_results$num_multi_ctwas_gene,
                        LDL_results$num_coloc_gene,
                        LDL_results$num_coloc_ctwas_gene,
                        WBC_results$num_multi_ctwas_gene,
                        WBC_results$num_coloc_gene,
                        WBC_results$num_coloc_ctwas_gene,
                        SBP_results$num_multi_ctwas_gene,
                        SBP_results$num_coloc_gene,
                        SBP_results$num_coloc_ctwas_gene,
                        SCZ_results$num_multi_ctwas_gene,
                        SCZ_results$num_coloc_gene,
                        SCZ_results$num_coloc_ctwas_gene,
                        IBD_results$num_multi_ctwas_gene,
                        IBD_results$num_coloc_gene,
                        IBD_results$num_coloc_ctwas_gene),  
                  grp = rep(c("LDL","WBC","SBP","SCZ","IBD"),each=3),
                  subgroup = c("multi-ctwas","coloc","coloc-ctwas-locus")) 

gfg$subgroup <- factor(gfg$subgroup,levels=c("multi-ctwas","coloc","coloc-ctwas-locus"))

ggplot(gfg,aes(x = grp, y =x, fill = subgroup)) + 
  geom_bar(stat = "identity", position = "dodge") 
```

### compare number of genes per locus
```{r echo=FALSE}
LDL_results$p1
WBC_results$p1
SBP_results$p1
SCZ_results$p1
IBD_results$p1
```

### compare number of genes per locus (locus with multi-ctwas signals)
```{r echo=FALSE}
LDL_results$p2
WBC_results$p2
SBP_results$p2
SCZ_results$p2
IBD_results$p2
```


```{r echo=FALSE}
get_results_mts <- function(gwas_id,gwas_name){
  tissues <- GWAS_tissues[[gwas_id]]
  outputdir = paste0("/project/xinhe/shengqian/coloc_GWAS_analysis/data_test/",gwas_name,"_coloc/")
  weight_tags <- paste0("weight",1:10)
  colocfs <- paste0(outputdir, gwas_name, "_",weight_tags, ".coloc_res.RDS")
  
  coloc_mts <- rbind(get_top_mts_coloc(colocfs[1], paste0(tissues[1],"_eQTL")),
                     get_top_mts_coloc(colocfs[2], paste0(tissues[1],"_sQTL")),
                     get_top_mts_coloc(colocfs[3], paste0(tissues[2],"_eQTL")),
                     get_top_mts_coloc(colocfs[4], paste0(tissues[2],"_sQTL")),
                     get_top_mts_coloc(colocfs[5], paste0(tissues[3],"_eQTL")),
                     get_top_mts_coloc(colocfs[6], paste0(tissues[3],"_sQTL")),
                     get_top_mts_coloc(colocfs[7], paste0(tissues[4],"_eQTL")),
                     get_top_mts_coloc(colocfs[8], paste0(tissues[4],"_sQTL")),
                     get_top_mts_coloc(colocfs[9], paste0(tissues[5],"_eQTL")),
                     get_top_mts_coloc(colocfs[10],paste0(tissues[5],"_sQTL")))
  
  coloc_mts <- coloc_mts[coloc_mts$PP4>0.8,]
  num_coloc_mts <- length(unique(coloc_mts$id))
  
  finemap_res <- readRDS(paste0("/project/xinhe/shengqian/ctwas_GWAS_analysis/results_ES/",gwas_id,"/",gwas_id,".finemap_regions_res.RDS"))
  finemap_res <- finemap_res$finemap_res
  finemap_res <- finemap_res[finemap_res$susie_pip>0.8,]
  
  num_multi_ctwas_mts <- length(unique(finemap_res$id))
  
  region_singals <- unique(finemap_res$region_id)
  num_coloc_ctwas_mts <- length(unique(coloc_mts[coloc_mts$region_id %in% region_singals, ]$id))
  
  coloc_data <- as.vector(table(unique(coloc_mts[,c("id","region_id")])$region_id))
  multictwas_data <- as.vector(table(finemap_res$region_id))
  
  # Combine data into a data frame
  df <- data.frame(
    value = c(coloc_data, multictwas_data),
    group = c(rep("Coloc",length(coloc_data)),rep("Multi-cTWAS",length(multictwas_data)))
  )
  
  p1 <- ggplot(df, aes(x = value, fill = group)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = max(coloc_data)) +
    scale_fill_manual(values = c("blue", "red")) +
    labs(title = gwas_id, x = "Value", y = "Frequency", fill = "Dataset") + theme_minimal()
  
  ctwas_coloc_data <- coloc_mts[coloc_mts$region_id %in% region_singals, ]
  ctwas_coloc_data <- as.vector(table(unique(ctwas_coloc_data[,c("id","region_id")])$region_id))
  # Combine data into a data frame
  df <- data.frame(
    value = c(ctwas_coloc_data, multictwas_data),
    group = c(rep("Coloc",length(ctwas_coloc_data)),rep("Multi-cTWAS",length(multictwas_data)))
  )
  
  p2 <- ggplot(df, aes(x = value, fill = group)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = max(coloc_data)) +
    scale_fill_manual(values = c("blue", "red")) +
    labs(title = gwas_id, x = "Value", y = "Frequency", fill = "Dataset") + theme_minimal()
  
  return(list("num_coloc_mts" = num_coloc_mts,
              "num_coloc_ctwas_mts" = num_coloc_ctwas_mts,
              "num_multi_ctwas_mts" = num_multi_ctwas_mts,
              "p1" = p1,
              "p2" = p2))
}
```

```{r, message=FALSE, echo=FALSE}
LDL_results <- get_results_mts("LDL-ukb-d-30780_irnt","LDL")
WBC_results <- get_results_mts("WBC-ieu-b-30","WBC")
SBP_results <- get_results_mts("SBP-ukb-a-360","SBP")
SCZ_results <- get_results_mts("SCZ-ieu-b-5102","SCZ")
IBD_results <- get_results_mts("IBD-ebi-a-GCST004131","IBD")
```

### number of molecular traits identified by each method
```{r echo=FALSE}
library(ggplot2) 

gfg <- data.frame(x = c(LDL_results$num_multi_ctwas_mts,
                        LDL_results$num_coloc_mts,
                        LDL_results$num_coloc_ctwas_mts,
                        WBC_results$num_multi_ctwas_mts,
                        WBC_results$num_coloc_mts,
                        WBC_results$num_coloc_ctwas_mts,
                        SBP_results$num_multi_ctwas_mts,
                        SBP_results$num_coloc_mts,
                        SBP_results$num_coloc_ctwas_mts,
                        SCZ_results$num_multi_ctwas_mts,
                        SCZ_results$num_coloc_mts,
                        SCZ_results$num_coloc_ctwas_mts,
                        IBD_results$num_multi_ctwas_mts,
                        IBD_results$num_coloc_mts,
                        IBD_results$num_coloc_ctwas_mts),  
                  grp = rep(c("LDL","WBC","SBP","SCZ","IBD"),each=3),
                  subgroup = c("multi-ctwas","coloc","coloc-ctwas-locus")) 

gfg$subgroup <- factor(gfg$subgroup,levels=c("multi-ctwas","coloc","coloc-ctwas-locus"))

ggplot(gfg,aes(x = grp, y =x, fill = subgroup)) + 
  geom_bar(stat = "identity", position = "dodge") 
```

### compare number of molecular traits per locus
```{r echo=FALSE}
LDL_results$p1
WBC_results$p1
SBP_results$p1
SCZ_results$p1
IBD_results$p1
```

### compare number of molecular traits per locus (locus with multi-ctwas signals)
```{r echo=FALSE}
LDL_results$p2
WBC_results$p2
SBP_results$p2
SCZ_results$p2
IBD_results$p2
```

```{r, echo=FALSE, eval=FALSE}
library(EnsDb.Hsapiens.v86)
ens_db <- EnsDb.Hsapiens.v86
weights <- readRDS("/project/xinhe/shengqian/ctwas_GWAS_analysis/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.preprocessed.weights.RDS")
mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_E_S_M_mapping.RDS")
finemap_res <- readRDS("/project/xinhe/shengqian/ctwas_GWAS_analysis/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.finemap_regions_res.RDS")
finemap_res <- finemap_res$finemap_res
snp_map <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/LD_region_info/snp_map.RDS")
finemap_res_multi <- anno_finemap_res(finemap_res,
                                      snp_map = snp_map,
                                      mapping_table = mapping_predictdb,
                                      add_gene_annot = TRUE,
                                      map_by = "molecular_id",
                                      drop_unmapped = TRUE,
                                      add_position = TRUE,
                                      use_gene_pos = "mid")
```

```{r, echo=FALSE, eval=FALSE}
pdf(file = "/project/xinhe/shengqian/test.pdf",width = 12,height = 10)
make_locusplot(finemap_res_multi,
               region_id = "9_127293231_129403191",
               ens_db = ens_db,
               weights = weights,
               highlight_pip = 0.8,
               filter_protein_coding_genes = TRUE,
               filter_cs = TRUE,
               color_pval_by = "cs",
               color_pip_by = "cs",
               panel.heights = c(4, 4, 1, 4))
dev.off()
```
