---
title: "tissue selection"
output: html_document
date: '2024-10-22'
editor_options: 
  chunk_output_type: console
---

### Method
1. Run all tissues jointly (very fast if weights have been harmonized).
2. Rank tissues by %h2g and select reasonable top ones.

### Summary
1. For IBD, colon transverse and whole blood have much higher %h2g than other tissues. 
2. For LDL, liver has much higher %h2g than other tissues.
3. For SBP, the top five ones all make sense, which are artery aorta, brain cortex, artery tibial, cell cultured fibroblasts and adrenal gland.
4. For WBC, whole blood has much higher %h2g than other tissues. 
5. For SCZ, the top ones are basal ganglia, cerebellum, hippocampus, hemisphere, cortex ...


```{r}
sample_size <- list("WBC-ieu-b-30" = 563946,
                    "SBP-ukb-a-360" = 317754,
                    "LDL-ukb-d-30780_irnt" = 343621,
                    "aFib-ebi-a-GCST006414" = 1030826,
                    "IBD-ebi-a-GCST004131" = 59957,
                    "SCZ-ieu-b-5102" = 127906,
                    "BMI-panukb" = 419163,
                    "Height-panukb" = 419596,
                    "PLT-panukb" = 407992,
                    "RBC-panukb" = 407995,
                    "HB-panukb" =  407994,
                    "HTN-panukb" = 420473,
                    "RA-panukb" =  376792,
                    "T1D-GCST90014023" = 520580,
                    "ATH_gtexukb" = 337119,
                    "T2D-panukb" = 418949,
                    "MDD-ieu-b-102" = 500199,
                    "BIP-ieu-b-5110" = 413466)

for(i in names(sample_size)){
  param <- readRDS(paste0("/project/xinhe/shengqian/all_tissues_screen/results_E/",i,"/",i,".param.RDS"))
  ctwas_parameters <- ctwas:::summarize_param(param,376792)
  prop_h2g <- as.data.frame(cbind(names(ctwas_parameters$prop_heritability),ctwas_parameters$prop_heritability,ctwas_parameters$group_pve, c(ctwas_parameters$enrichment,1), param$group_pvalue))
  prop_h2g$V2 <- round(as.numeric(prop_h2g$V2),4)
  prop_h2g$V3 <- round(as.numeric(prop_h2g$V3),4)
  prop_h2g$V4 <- round(as.numeric(prop_h2g$V4),4)
  rownames(prop_h2g) <- NULL
  prop_h2g <- prop_h2g[order(-prop_h2g$V2),]
  colnames(prop_h2g) <- c("group","%h2g","h2g","enrichment","pvalue")
  prop_h2g <- prop_h2g[prop_h2g$group!="SNP",]
  print(DT::datatable(prop_h2g,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;',i),options = list(pageLength = 10)))
}
```



```{r echo=FALSE}
get_results <- function(param_file,ctwas_file){
  ctwas_parameters <- readRDS(param_file)
  prop_h2g <- as.data.frame(cbind(names(ctwas_parameters$prop_heritability),ctwas_parameters$prop_heritability,ctwas_parameters$group_pve,c(ctwas_parameters$enrichment,1),ctwas_parameters$group_pvalue,ctwas_parameters$odds_ratio))
  prop_h2g$V2 <- round(as.numeric(prop_h2g$V2),4)
  prop_h2g$V3 <- round(as.numeric(prop_h2g$V3),4)
  prop_h2g$V4 <- round(as.numeric(prop_h2g$V4),4)
  prop_h2g$V5 <- round(as.numeric(prop_h2g$V5),4)
  prop_h2g$V6 <- round(as.numeric(prop_h2g$V6),4)
  rownames(prop_h2g) <- NULL
  prop_h2g <- prop_h2g[order(-prop_h2g$V2),]
  colnames(prop_h2g) <- c("group","%h2g","h2g","enrichment","enrichment_pvalue","odds_ratio")
  prop_h2g <- prop_h2g[prop_h2g$group!="SNP",]
  #pvalue_df <- data.frame()
  #finemap_res <- readRDS(ctwas_file)
  #finemap_res <- finemap_res$finemap_res
  #for(i in unique(finemap_res$group)){
  #  snp_pip <- sum(finemap_res[finemap_res$group=="SNP","susie_pip"])
  #  snp_n <- dim(finemap_res[finemap_res$group=="SNP",])[1]
  #  tissue_pip <- sum(finemap_res[finemap_res$group==i,"susie_pip"])
  #  tissue_n <- dim(finemap_res[finemap_res$group==i,])[1]
    #y <- c(finemap_res[finemap_res$group=="SNP","susie_pip"],finemap_res[finemap_res$group==i,"susie_pip"])
    #x <- as.factor(c(rep(0,snp_n),rep(1,tissue_n)))
    #res <- glm(y ~ x, family = quasibinomial('logit'))
    #res_sum <- summary(res)
    #fractional_pvalue <- res_sum$coefficients[2,4]
  #  data <- matrix(c(tissue_pip, tissue_n, snp_pip, snp_n), nrow = 2, byrow = TRUE)
  #  data <- round(data)
  #  result <- fisher.test(data)
  #  pvalue_df <- rbind(pvalue_df,data.frame(group=i,enrichment_pvalue2=round(-log10(result$p.value),3),odds_ratio2=round(result$estimate,3),low=round(result$conf.int[1],3),up=round(result$conf.int[2],3)))
  #}
  #output <- merge(prop_h2g, pvalue_df, by = "group")
  #output <- output[order(-output$`%h2g`),]
  return(prop_h2g)
}
```

### IBD results (Inflammatory bowel disease)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_all_tissue_E/ibd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### GTEx IBD results (Inflammatory bowel disease)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_gtex_all_tissue_E/ibd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ibd_gtex_all_tissue_E/ibd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### WBC results (White blood cell count)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/wbc_all_tissue_E/wbc_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### RA results (Rheumatoid arthritis)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ra_all_tissue_E/ra_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ra_all_tissue_E/ra_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### SBP results (Systolic blood pressure)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/sbp_all_tissue_E/sbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### DBP results (Diastolic blood pressure)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/dbp_all_tissue_E/dbp_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### HTN results (Hypertension)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/htn_all_tissue_E/htn_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/htn_all_tissue_E/htn_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### SCZ results (Schizophrenia)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/scz_all_tissue_E/scz_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### BIP results (Bipolar disorder)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bip_all_tissue_E/bip_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### MDD results (Major depressive disorder)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/mdd_all_tissue_E/mdd_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### LDL results (low-density lipoprotein)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/ldl_all_tissue_E/ldl_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### TG results (Triglycerides)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/tg_all_tissue_E/tg_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/tg_all_tissue_E/tg_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### BMI results (Body mass index)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### BMI results (Body mass index)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/bmi_all_tissue_E/bmi_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### T2D results (Type 2 diabetes)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_all_tissue_E/t2d_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_all_tissue_E/t2d_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```

### T2D results (Type 2 diabetes)
```{r, echo=FALSE, fig.width=10, fig.height=8}
param_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_gtex_all_tissue_E/t2d_all_tissue_E.ctwas_parameters.RDS"
ctwas_file <- "/project/xinhe/shengqian/cTWAS_analysis/data/t2d_gtex_all_tissue_E/t2d_all_tissue_E.finemap_regions_res.RDS"
output <- get_results(param_file,ctwas_file)
DT::datatable(output,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Proportion of PVE'),options = list(pageLength = 10) )
```


```{r}
gwas_n <- 59957
finemap_res <- readRDS("/project/xinhe/shengqian/cTWAS_analysis/data/ra_all_tissue_E_heritable/ra_all_tissue_E.finemap_regions_res.RDS")
gene_annot <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
susie_alpha_res <- anno_susie_alpha_res(finemap_res$susie_alpha_res,
                                        mapping_table = gene_annot,
                                        map_by = "molecular_id",
                                        drop_unmapped = TRUE)

combined_pip_by_group <- combine_gene_pips(susie_alpha_res, 
                                             group_by = "gene_name",
                                             by = "group",
                                             method = "combine_cs",
                                             filter_cs = TRUE,
                                             include_cs_id = FALSE)

DT::datatable(combined_pip_by_group,caption = htmltools::tags$caption( style = 'caption-side: topleft; text-align = left; color:black;','Combined PIP by modalities and contexts'),options = list(pageLength = 10) )
```

```{r}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_enrichment/"
runtag = "one_tissue"
pvalue = c()
simutags <- paste(8, 1:20, sep = "-")
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp0.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    pvalue <- c(pvalue,ctwas_parameters$group_pvalue[1])
  }
}
```


```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_enrichment/"
runtag = "one_tissue"
enrichment_df = data.frame()
simutags <- paste(8, 1:20, sep = "-")
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp0.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    enrichment_df <- rbind(enrichment_df,c("group1",ctwas_parameters$enrichment))
  }
}

param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    enrichment_df <- rbind(enrichment_df,c("group2",ctwas_parameters$enrichment))
  }
}
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.mingene1.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    enrichment_df <- rbind(enrichment_df,c("group3",ctwas_parameters$enrichment))
  }
}

colnames(enrichment_df) <- c("Group", "Value")
enrichment_df$Value <- log10(as.numeric(enrichment_df$Value))
```

```{r}
# Load ggplot2 library
enrichment_df$Group <- factor(enrichment_df$Group, levels = c("group1", "group2", "group3"))
ggplot(enrichment_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Group",
       y = "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_enrichment/"
runtag = "one_tissue"
pvalue_df = data.frame()
simutags <- paste(8, 1:20, sep = "-")
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp0.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    pvalue_df <- rbind(pvalue_df,c("group1",ctwas_parameters$group_pvalue[1]))
  }
}

param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    pvalue_df <- rbind(pvalue_df,c("group2",ctwas_parameters$group_pvalue[1]))
  }
}
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.mingene1.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    ctwas_parameters <- readRDS(j)
    pvalue_df <- rbind(pvalue_df,c("group3",ctwas_parameters$group_pvalue[1]))
  }
}

colnames(pvalue_df) <- c("Group", "Value")
pvalue_df$Value <- as.numeric(pvalue_df$Value)
```

```{r}
# Load ggplot2 library
pvalue_df$Group <- factor(pvalue_df$Group, levels = c("group1", "group2", "group3"))
ggplot(pvalue_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Group",
       y = "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_enrichment/"
runtag = "one_tissue"
prior_df = data.frame()
simutags <- paste(8, 1:20, sep = "-")
param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp0.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    print(j)
    ctwas_parameters <- readRDS(j)
    prior_df <- rbind(prior_df,c("group1","gene prior",ctwas_parameters$group_prior[1]))
    prior_df <- rbind(prior_df,c("group1","snp prior",ctwas_parameters$group_prior[2]))
  }
}

param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.allregion.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    print(j)
    ctwas_parameters <- readRDS(j)
    prior_df <- rbind(prior_df,c("group2","gene prior",ctwas_parameters$group_prior[1]))
    prior_df <- rbind(prior_df,c("group2","snp prior",ctwas_parameters$group_prior[2]))
  }
}

param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.mingene1.minp08.ctwas_parameters.RDS")
for(j in param_files){
  if(file.exists(j)){
    print(j)
    ctwas_parameters <- readRDS(j)
    prior_df <- rbind(prior_df,c("group3","gene prior",ctwas_parameters$group_prior[1]))
    prior_df <- rbind(prior_df,c("group3","snp prior",ctwas_parameters$group_prior[2]))
  }
}

colnames(prior_df) <- c("Group","Type","Value")
prior_df$Value <- as.numeric(prior_df$Value)

```

```{r, echo=FALSE, eval=FALSE}
# Load necessary library
library(ggplot2)
# Ensure group order based on size
prior_df$Group <- factor(data$Group, levels = c("group1", "group2", "group3"))
# Plot with separated features within each group
ggplot(prior_df, aes(x = Group, y = Value, color = Type)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  labs(title = "Scatter Plot of Groups vs. Prior with Separated Features",
       x = "Group",
       y = "Prior Value") +
  theme_minimal()
```

```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_same_variance/"
runtag = "one_tissue"
enrichment_df <- data.frame()
for(i in c(1,7)){
  simutags <- paste(i, 1:20, sep = "-")
  param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".thin1.ctwas_parameters.RDS")
  for(j in param_files){
    if(file.exists(j)){
      ctwas_parameters <- readRDS(j)
      enrichment_df <- rbind(enrichment_df,c(paste0('group',i),ctwas_parameters$group_prior[1]))
    }
  }
}
colnames(enrichment_df) <- c("Group","Enrichment")
enrichment_df$Enrichment <- as.numeric(enrichment_df$Enrichment)
```

```{r}
# Load ggplot2 library
enrichment_df$Group <- factor(enrichment_df$Group, levels = c("group1", "group7"))
ggplot(enrichment_df, aes(x = Group, y = Enrichment, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Groups",
       y = "Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_same_variance/"
runtag = "one_tissue"
enrichment_list <- list()
for(i in 1:7){
  simutags <- paste(i, 1:20, sep = "-")
  param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".ctwas_parameters.RDS")
  enrichment <- c()
  for(j in param_files){
    ctwas_parameters <- readRDS(j)
    enrichment <- c(enrichment,ctwas_parameter)
  }
  enrichment_list[[i]]<-enrichment
}

enrichment_df <- as.data.frame(do.call(cbind,enrichment_list))
rownames(enrichment_df) <- 1:20
colnames(enrichment_df) <- c("group1","group10","group20","group40","group60","group80","group100")
```

```{r, echo=FALSE, eval=FALSE}
# Convert the data frame to a long format
library(tidyr)
long_df <- pivot_longer(enrichment_df, cols = everything(), names_to = "Group", values_to = "Value")
long_df$Group <- factor(long_df$Group, levels = c("group1", "group10", "group20", "group40", "group60", "group80", "group100"))
# Plot using ggplot2
library(ggplot2)

ggplot(long_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Groups",
       y = "Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, echo=FALSE, eval=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue_highPVE/"
runtag = "one_tissue"
enrichment_list <- list()
for(i in 1:20){
  simutags <- paste(i, 1:20, sep = "-")
  param_files <- paste0(results_dir, runtag, "_simu",simutags, "_UKBBLD", ".ctwas_parameters.RDS")
  enrichment <- c()
  for(j in param_files){
    ctwas_parameters <- readRDS(j)
    enrichment <- c(enrichment,ctwas_parameters$odds_ratio)
  }
  enrichment_list[[i]]<-enrichment
}

enrichment_df <- as.data.frame(do.call(cbind,enrichment_list))
#rownames(enrichment_df) <- 1:20
colnames(enrichment_df) <- c("group1","group10","group20","group40","group60","group80","group100")
```

```{r, echo=FALSE, eval=FALSE}
# Convert the data frame to a long format
library(tidyr)
long_df <- pivot_longer(enrichment_df, cols = everything(), names_to = "Group", values_to = "Value")
long_df$Group <- factor(long_df$Group, levels = c("group1", "group10", "group20", "group40", "group60", "group80", "group100"))
# Plot using ggplot2
library(ggplot2)

ggplot(long_df, aes(x = Group, y = Value, color = Group)) +
  geom_point() +
  labs(title = "Scatter Plot of Enrichment Data",
       x = "Groups",
       y = "Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
sample_size <- list("WBC-ieu-b-30" = 563946,
                    "SBP-ukb-a-360" = 317754,
                    "LDL-ukb-d-30780_irnt" = 343621,
                    "aFib-ebi-a-GCST006414" = 1030826,
                    "IBD-ebi-a-GCST004131" = 59957,
                    "SCZ- ieu-b-5102" = 127906,
                    "BMI-panukb" = 419163,
                    "Height-panukb" = 419596,
                    "PLT-panukb" = 407992,
                    "RBC-panukb" = 407995,
                    "HB-panukb" =  407994,
                    "HTN-panukb" = 420473,
                    "RA-panukb" =  376792,
                    "T1D-GCST90014023" = 520580,
                    "ATH_gtexukb" = 337119,
                    "T2D-panukb" = 418949,
                    "MDD-ieu-b-102" = 500199,
                    "BIP-ieu-b-5110" = 413466)
```

