---
title: "real data coloc analysis"
output: html_document
date: '2024-10-22'
editor_options: 
  chunk_output_type: console
---

### Method
1. For each trait, select regions with at lease high PIP expression/splicing trait (PIP>0.8)
- based on multi-cTWAS results with three molecular traits (eQTL,sQTL,stQTL) from five tissues.
2. Run coloc with eQTL and sQTL full summary statistics from five tissues
- no stQTL full summary statistics
3. Comparing the number of expression and splicing molecular traits identified by coloc (PP4>0.8) and multi-cTWAS (PIP>0.8)
- don't include stability traits identified by multi-cTWAS

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(ggplot2)
library(ggVennDiagram)
library(gridExtra)
library(data.table)
library(ctwas)
library(data.table)
library(tidyverse)
library(RSQLite)
library(dplyr)
library(magrittr)
library(pheatmap)

get_top_genes_coloc <- function(colocf){
  coloc_res <- readRDS(colocf)
  coloc_res <- coloc_res[coloc_res$PP4>0.8,]
  return(coloc_res$id)
}
```

#### LDL
```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/LDL-ukb-d-30780_irnt/LDL-ukb-d-30780_irnt.ctwas.res.RDS")
z_gene <- finemap_res$z_gene
finemap_res <- finemap_res$finemap_res
alpha <- 0.05
sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
twas_genes <- z_gene$id[(abs(z_gene$z)>sig_thresh) & (z_gene$type!="stQTL")]
region_singals <- unique(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),]$region_id)
#length(intersect(twas_genes,finemap_res[finemap_res$region_id %in% region_singals,]$id))
#dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])

runtag = "LDL"
outputdir = "/project/xinhe/shengqian/cTWAS_analysis/data/LDL_coloc/"
weight_tags <- paste0("weight",1:10)
colocfs <- paste0(outputdir, runtag, "_",weight_tags, ".coloc_res.RDS")

coloc_genes <- c(get_top_genes_coloc(colocfs[1]),
                 get_top_genes_coloc(colocfs[2]),
                 get_top_genes_coloc(colocfs[3]),
                 get_top_genes_coloc(colocfs[4]),
                 get_top_genes_coloc(colocfs[5]),
                 get_top_genes_coloc(colocfs[6]),
                 get_top_genes_coloc(colocfs[7]),
                 get_top_genes_coloc(colocfs[8]),
                 get_top_genes_coloc(colocfs[9]),
                 get_top_genes_coloc(colocfs[10]))

#length(coloc_genes)
num_ctwas <- dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])[1]
num_coloc <- length(coloc_genes)
plot_data <- c(num_coloc,num_ctwas)
names(plot_data) <- c("coloc","multi-cTWAS")
barplot(plot_data,col = c("#ffff99","#fb8072"))
```

#### SBP
```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/SBP-ukb-a-360/SBP-ukb-a-360.ctwas.res.RDS")
z_gene <- finemap_res$z_gene
finemap_res <- finemap_res$finemap_res
alpha <- 0.05
sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
twas_genes <- z_gene$id[(abs(z_gene$z)>sig_thresh) & (z_gene$type!="stQTL")]
region_singals <- unique(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),]$region_id)
#length(intersect(twas_genes,finemap_res[finemap_res$region_id %in% region_singals,]$id))
#dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])

runtag = "SBP"
outputdir = "/project/xinhe/shengqian/cTWAS_analysis/data/SBP_coloc/"
weight_tags <- paste0("weight",1:10)
colocfs <- paste0(outputdir, runtag, "_",weight_tags, ".coloc_res.RDS")

coloc_genes <- c(get_top_genes_coloc(colocfs[1]),
                 get_top_genes_coloc(colocfs[2]),
                 get_top_genes_coloc(colocfs[3]),
                 get_top_genes_coloc(colocfs[4]),
                 get_top_genes_coloc(colocfs[5]),
                 get_top_genes_coloc(colocfs[6]),
                 get_top_genes_coloc(colocfs[7]),
                 get_top_genes_coloc(colocfs[8]),
                 get_top_genes_coloc(colocfs[9]),
                 get_top_genes_coloc(colocfs[10]))

num_ctwas <- dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])[1]
num_coloc <- length(coloc_genes)
plot_data <- c(num_coloc,num_ctwas)
names(plot_data) <- c("coloc","multi-cTWAS")
barplot(plot_data,col = c("#ffff99","#fb8072"))
```

#### IBD
```{r}
finemap_res <- readRDS("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/IBD-ebi-a-GCST004131/IBD-ebi-a-GCST004131.ctwas.res.RDS")
z_gene <- finemap_res$z_gene
finemap_res <- finemap_res$finemap_res
alpha <- 0.05
sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
twas_genes <- z_gene$id[(abs(z_gene$z)>sig_thresh) & (z_gene$type!="stQTL")]
region_singals <- unique(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),]$region_id)
#length(intersect(twas_genes,finemap_res[finemap_res$region_id %in% region_singals,]$id))
#dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])

runtag = "IBD"
outputdir = "/project/xinhe/shengqian/cTWAS_analysis/data/IBD_coloc/"
weight_tags <- paste0("weight",1:10)
colocfs <- paste0(outputdir, runtag, "_",weight_tags, ".coloc_res.RDS")

coloc_genes <- c(get_top_genes_coloc(colocfs[1]),
                 get_top_genes_coloc(colocfs[2]),
                 get_top_genes_coloc(colocfs[3]),
                 get_top_genes_coloc(colocfs[4]),
                 get_top_genes_coloc(colocfs[5]),
                 get_top_genes_coloc(colocfs[6]),
                 get_top_genes_coloc(colocfs[7]),
                 get_top_genes_coloc(colocfs[8]),
                 get_top_genes_coloc(colocfs[9]),
                 get_top_genes_coloc(colocfs[10]))

num_ctwas <- dim(finemap_res[(finemap_res$susie_pip>0.8) & (finemap_res$type!="SNP") & !is.na((finemap_res$cs)) & (finemap_res$type!="stQTL"),])[1]
num_coloc <- length(coloc_genes)
plot_data <- c(num_coloc,num_ctwas)
names(plot_data) <- c("coloc","multi-cTWAS")
barplot(plot_data,col = c("#ffff99","#fb8072"))
```




