---
title: "Weighted pathway-based gene set enrichment"
author: "XSun"
date: "2025-06-04"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

```{r}

library(kableExtra)
library(tidyverse)


```


# Introduction

We validate genes with susie pip > 0.8 here: https://sq-96.github.io/multigroup_ctwas_analysis/realdata_final_multigroup_summary.html

The basic idea is:

Some biological pathways are related to the traits. Genes within these pathways are more likely to be associated with these traits. Our approach involves aggregating these genes into a collective group. This allows us to assess whether the genes identified by cTWAS are overrepresented in this group. 

However, the presence of common genes across multiple pathways presents a challenge to this straightforward aggregation approach. To address this, we propose weighting the pathways, assigning a unique score to each gene. By selecting genes that meet a specific score threshold, we can form a more refined group. We can then evaluate the enrichment of cTWAS-identified genes within this selectively grouped set.

## Model

The model is $y=X*w$

y is an n-dimensional vector representing gene-trait associations (n = number of genes), which can be:

 - z-scores computed by MAGMA
 - a binary vector indicating gene-trait relationships. 

We tried different settings for the binary vector: 
 
 - genes with FDR 0.05 as per MAGMA are marked 1.
 - Genes ranked in the top 500 by MAGMA p-values or meeting the FDR 0.05 threshold were labeled as 1.
 - Genes ranked in the top 1000 by MAGMA p-values or meeting the FDR 0.05 threshold were labeled as 1.

X is an n×m matrix (m = number of pathways) indicating gene membership in specific pathways.

We fitted this model using different models.

If y is a z-score vector, it can be fitted using 

 <!-- - linear Susie -->
 - XGBoost: regression with squared loss

If y is a binarized vector, the model can be fitted using 

 <!-- - logistic Susie -->
 - XGBoost: logistic regression for binary classification, output probability

## Benchmarks

The model fitting results in pathway weights, from which we predict gene labels $\hat{y}$. We then categorize genes based on these new labels. 

- For z-score model, we compute the p-values from the new labels(z-scores), then compute FDR. Then we tested different cutoffs for gene selection. The cutoffs are: 0.05,0.1,0.2

- For binarized model. Genes with labels > 0.5/0.6/0.7/0.8 are considered benchmarks.

## Testing genes

Genes from ctwas results are divided into different groups based on their SuSiE PIPs: 

- high (>0.8) 
- moderate (0.8 > PIP > 0.5)
- low (<0.5)

## Fisher exact test

We assess whether high-PIP genes are more enriched in our benchmarks than other groups using Fisher exact tests. 

The testing matrix is: 

```{r}

fisher_matrix <- matrix(c("n1","n2","n3","n4"),nrow = 2,ncol = 2)
rownames(fisher_matrix) <- c("#included","#notincluded")
colnames(fisher_matrix) <- c("pip08","other group")

print(fisher_matrix)
```

## Pathways

The pathways are from Go Biological Process (gobp), Go Molecular Function (gomf), Go Cellular Component (gocc) and KEGG.


# Results



## GOBP

### Binary, not truncated 

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.5_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.6_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.7_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.8_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```




### Binary, truncated top 500 genes

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.5_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.6_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.7_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.8_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```
 


### Binary, truncated top 1000 genes

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.5_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.6_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.7_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.8_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```




### Zscores

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.05_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff FDR 0.05, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.1_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff FDR 0.1, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.2_gobp.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff FDR 0.2, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```

## GOBP + GOCC + GOMF + KEGG jointly

### Binary, not truncated 

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.5_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.6_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.7_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_prob0.8_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```




### Binary, truncated top 500 genes

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.5_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.6_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.7_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.8_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```
 


### Binary, truncated top 1000 genes

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.5_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.5, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc500_prob0.6_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.6, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.7_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.7, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_binary/results_y_pred_xgboost_gene_score_bin_trunc1000_prob0.8_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (XGboost prediction): 0.8, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```



### Zscores

```{r}


df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.05_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff (FDR  0.05); significant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.1_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff FDR 0.1, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)

df <- readRDS("/project/xinhe/xsun/multi_group_ctwas/25.multi_group_validation_classfier_0602/results/fisher_xgboost_zscore/results_zfdr0.2_all.RDS")

df %>%
  mutate(across(starts_with("pval_"), 
                ~ifelse(. < 0.05, 
                        cell_spec(sprintf("%.5f", .), color = "red"), 
                        sprintf("%.5f", .)))) %>%
  kable(escape = FALSE, format = "html", 
        caption = "Benchmark gene cutoff FDR 0.2, sigificant ones are highlighted") %>%
  kable_styling(full_width = FALSE)


```
