---
title: "Expression and Splicing from three tissues simulations"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of expression and splicing traits from three tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Three tissues used in this simulation are Liver, Adipose and Lung. 
Only expression and splicing from liver are causal, each with 3% PVE, 0.9% $\pi$. SNPs have 30% PVE, 2.5e-4 $\pi$.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")
#load("/project2/xinhe/shared_data/multigroup_ctwas/weights/E_S_A_mapping.RData")

plot_PIP <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_estimated_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, "_newpack.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_true_parameter <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_true_parameter_true_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.true.effects.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_true_parameter_estimated_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.estimated.effects.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_estimated_parameter_true_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.estimated.parameter.true.effects.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_estimated_parameter_estimated_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.estimated.parameter.estimated.effects.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_merged <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type,".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP <- function(configtag, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_estimated_L <- function(configtag, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, "_newpack.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_true_parameter <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_true_parameter_true_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.true.effects.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_true_parameter_estimated_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.true.parameter.estimated.effects.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_estimated_parameter_true_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.estimated.parameter.true.effects.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_combined_PIP_estimated_parameter_estimated_L <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.estimated.parameter.estimated.effects.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined_merged <- function(configtag, runtag, simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}
```

### Get parameters

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_three_tissues_expression_splicing//"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
param_UKBB_df <- load_parameters(results_dir, runtag, simutags, "UKBBLD")
```


### Compare number of screen regions

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_three_tissues_expression_splicing/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
for(simutag in simutags){
    regions <- readRDS(paste0(results_dir,runtag,"_simu",simutag,"_","UKBBLD",".estimatedL.screened_region_data.RDS"))
    print(length(regions))
}
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_three_tissues_expression_splicing/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
for(simutag in simutags){
    regions <- readRDS(paste0(results_dir,runtag,"_simu",simutag,"_","UKBBLD",".nonSNPpip.screened_region_data.RDS"))
    print(length(regions))
}
```

```{r}
f1 <- pip_partition_across_tissue(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
f1
```

### Number of causal genes detected (GTEX LD)
```{r, echo=FALSE, eval=FALSE}
check_n_detected_multiomics(results_dir, runtag, simutags, "GTEXLD", PIP_threshold = 0.8)
```

### Number of causal genes detected (UKBB LD)
```{r, echo=FALSE, eval=FALSE}
check_n_detected_multiomics(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
```

### Estimated Prior Inclusion Probability and PVE (UKBB LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_UKBB_df$`prior_Liver|expression`
y2 <- param_UKBB_df$`prior_Liver|splicing`
y3 <- param_UKBB_df$`prior_var_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`prior_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`prior_Lung|expression`
y6 <- param_UKBB_df$`prior_Lung|splicing`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_UKBB_df$`pve_Liver|expression`
y2 <- param_UKBB_df$`pve_Liver|splicing`
y3 <- param_UKBB_df$`pve_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`pve_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`pve_Lung|expression`
y6 <- param_UKBB_df$`prior_Lung|splicing`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_UKBB_df$`enrichment_Liver|expression`
y2 <- param_UKBB_df$`enrichment_Liver|splicing`
y3 <- param_UKBB_df$`enrichment_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`enrichment_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`enrichment_Lung|expression`
y6 <- param_UKBB_df$`enrichment_Lung|splicing`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### PIP attribution among tissues by QTL types (UKBBLD)
```{r, echo=FALSE, fig.width= 8, fig.height= 4, warning=FALSE, eval=FALSE}
f1 <- pip_partition_across_tissue_by_QTLtype(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8, "eQTL","Expression")
f2 <- pip_partition_across_tissue_by_QTLtype(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8, "sQTL","Splicing")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of molecular traits - Estimated Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "UKBBLD", main = "L=5")
f2 <- plot_PIP_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated L")
gridExtra::grid.arrange(f1, f2, ncol = 2)
```

### PIP Calibration Plot of molecular traits - Estimated Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_combined_PIP(results_dir, runtag, simutags, "UKBBLD", main = "L=5")
f2 <- plot_combined_PIP_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated L")
gridExtra::grid.arrange(f1, f2, ncol = 2)
```

### PIP Calibration Plot of molecular traits - Estimated Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter Default L")
f2 <- plot_PIP_estimated_parameter_true_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter True L")
f3 <- plot_PIP_estimated_parameter_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter Estimated L")
gridExtra::grid.arrange(f1, f2, f3, ncol = 3)
```

### PIP Calibration Plot of molecular traits - True Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_true_parameter(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter Default L")
f2 <- plot_PIP_true_parameter_true_L(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter True L")
f3 <- plot_PIP_true_parameter_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter Estimated L")
gridExtra::grid.arrange(f1, f2, f3, ncol = 3)
```

### PIP Calibration Plot of gene level PIP - Estimated Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_combined_PIP(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter Default L")
f2 <- plot_combined_PIP_estimated_parameter_true_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter True L")
f3 <- plot_combined_PIP_estimated_parameter_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "Estimated Parameter Estimated L")
gridExtra::grid.arrange(f1, f2, f3, ncol = 3)
```

### PIP Calibration Plot of gene level PIP - True Parameter (filter out cs index 0)
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_combined_PIP_true_parameter(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter Default L")
f2 <- plot_combined_PIP_true_parameter_true_L(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter True L")
f3 <- plot_combined_PIP_true_parameter_estimated_L(results_dir, runtag, simutags, "UKBBLD", main = "True Parameter Estimated L")
gridExtra::grid.arrange(f1, f2, f3, ncol = 3)
```
