---
title: "Expression and Splicing from three tissues simulations"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of expression and splicing traits from three tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Three tissues used in this simulation are Liver, Adipose and Lung. 
Only expression and splicing from liver are causal, each with 3% PVE, 0.9% $\pi$. SNPs have 30% PVE, 2.5e-4 $\pi$.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")
#source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")

plot_PIP_estimatedL <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".estimatedL.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_nonSNPpip <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".nonSNPpip.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_gene_PIP_estimatedL <- function(configtag, runtag,  simutags, LD_type, mapping_table, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".estimatedL.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_multi_omics(phenofs, susieIfs, mapping_table, ...) 
   return(f1)
}

plot_gene_PIP_nonSNPpip <- function(configtag, runtag,  simutags, LD_type, mapping_table, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".nonSNPpip.finemap_regions_res.RDS")
   f1 <- caliPIP_plot_multi_omics(phenofs, susieIfs, mapping_table, ...) 
   return(f1)
}
```

### Compare number of screen regions
```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_three_tissues_expression_splicing/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
num_estimatedL <- c()
for(simutag in simutags){
    regions <- readRDS(paste0(results_dir,runtag,"_simu",simutag,"_","UKBBLD",".estimatedL.screened_region_data.RDS"))
    num_estimatedL <- c(num_estimatedL,length(regions))
}
num_nonSNPpip <- c()
for(simutag in simutags){
    regions <- readRDS(paste0(results_dir,runtag,"_simu",simutag,"_","UKBBLD",".nonSNPpip.screened_region_data.RDS"))
    num_nonSNPpip <- c(num_nonSNPpip,length(regions))
}
data.frame(cbind(simutags,num_estimatedL,num_nonSNPpip))
```


```{r}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_three_tissues_expression_splicing/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
param_UKBB_df <- load_parameters(results_dir, runtag, simutags, "UKBBLD")
```

### Estimated Prior Inclusion Probability and PVE (UKBB LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_UKBB_df$`prior_Liver|expression`
y2 <- param_UKBB_df$`prior_Liver|splicing`
y3 <- param_UKBB_df$`prior_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`prior_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`prior_Lung|expression`
y6 <- param_UKBB_df$`prior_Lung|splicing`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_UKBB_df$`pve_Liver|expression`
y2 <- param_UKBB_df$`pve_Liver|splicing`
y3 <- param_UKBB_df$`pve_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`pve_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`pve_Lung|expression`
y6 <- param_UKBB_df$`pve_Lung|splicing`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_UKBB_df$`enrichment_Liver|expression`
y2 <- param_UKBB_df$`enrichment_Liver|splicing`
y3 <- param_UKBB_df$`enrichment_Adipose_Subcutaneous|expression`
y4 <- param_UKBB_df$`enrichment_Adipose_Subcutaneous|splicing`
y5 <- param_UKBB_df$`enrichment_Lung|expression`
y6 <- param_UKBB_df$`enrichment_Lung|splicing`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```


### PIP Calibration Plot of expression traits
```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_estimatedL(results_dir, runtag, simutags, "UKBBLD", main = "Estimated L")
f2 <- plot_PIP_nonSNPpip(results_dir, runtag, simutags, "UKBBLD", main = "nonSNPpip")
gridExtra::grid.arrange(f1, f2, ncol = 2)
```


```{r, fig.width= 12, fig.height= 4, echo=FALSE, warning=FALSE}
mapping_table <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
f1 <- plot_gene_PIP_estimatedL(results_dir, runtag, simutags, "UKBBLD", mapping_table, main = "Estimated L")
f2 <- plot_gene_PIP_nonSNPpip(results_dir, runtag, simutags, "UKBBLD", mapping_table, main = "nonSNPpip")
gridExtra::grid.arrange(f1, f2, ncol = 2)
```
