---
title: "simulation_summary"
output: html_document
date: '2024-10-02'
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, message=FALSE}
library(ctwas)
library(tidyr)
library(dplyr)
library(ggplot2)

get_parameter <- function(results_dir,runtag,simutags,null_weight_method,parameter){
  param_vec <- c()
  for(i in simutags){
    param <- readRDS(paste0(results_dir, "/",runtag,"_","simu",i,"_UKBBLD.thin1.",null_weight_method,"_null.parameters.RDS"))
    param <- param[[parameter]][1]
    param_vec <- c(param_vec,param)
  }
  return(param_vec)
}

get_parameter_allregion <- function(results_dir,runtag,simutags,null_weight_method,parameter){
  param_vec <- c()
  for(i in simutags){
    param <- readRDS(paste0(results_dir, "/",runtag,"_","simu",i,"_UKBBLD.thin1.allregion.",null_weight_method,"_null.parameters.RDS"))
    param <- param[[parameter]][1]
    param_vec <- c(param_vec,param)
  }
  return(param_vec)
}

get_plot <- function(ctwas_param,susie_param,true_value,title_name){
  data <- data.frame(ctwas_null_weight = ctwas_param, susie_null_weight = susie_param)
  data_long <- data %>% pivot_longer(cols = everything(), names_to = "group", values_to = "value")
  ggplot(data_long, aes(x = group, y = value, color = group)) +
  geom_point(size = 4, alpha = 0.7) +  # Add points
  geom_hline(yintercept = true_value, linetype = "dashed", color = "red") +  # Add horizontal line at y = 1
  labs(
    x = "Group",
    y = title_name,
  ) +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "none")  # Hide the legend
}
```


### Parameter estimation on selected regions (min_gene=1, min_p_single_effect=0.8, min_var=2)
#### Enrichment = 1
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,1,"Enrichment")
```

#### Enrichment = 10
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,10,"Enrichment")
```

#### Enrichment = 40
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,40,"Enrichment")
```

#### Enrichment = 80
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,80,"Enrichment")
```

#### Gene Prior = 0.00025
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.00025,"Gene Prior")
```

#### Gene Prior = 0.0025
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.0025,"Gene Prior")
```

#### Gene Prior = 0.01
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.01,"Gene Prior")
```

#### Gene Prior = 0.02
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.02,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter_allregion(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter_allregion(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

### Parameter estimation on all regions (min_gene=0, min_p_single_effect=0, min_var=1)
#### Enrichment = 1
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,1,"Enrichment")
```

#### Enrichment = 10
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,10,"Enrichment")
```

#### Enrichment = 40
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,40,"Enrichment")
```

#### Enrichment = 80
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","enrichment")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","enrichment")
get_plot(ctwas_param,susie_param,80,"Enrichment")
```

#### Gene Prior = 0.00025
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.00025,"Gene Prior")
```

#### Gene Prior = 0.0025
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.0025,"Gene Prior")
```

#### Gene Prior = 0.01
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.01,"Gene Prior")
```

#### Gene Prior = 0.02
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior")
get_plot(ctwas_param,susie_param,0.02,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```

#### Gene Variance = 10.2
```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")

ctwas_param <- get_parameter(results_dir,runtag,simutags,"ctwas","group_prior_var")
susie_param <- get_parameter(results_dir,runtag,simutags,"susie","group_prior_var")
get_plot(ctwas_param,susie_param,10.2,"Gene Prior")
```