---
title: "Expression and Splicing from three tissues simulations"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of expression and splicing traits from three tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Three tissues used in this simulation are Liver, Adipose and Lung. 
Only expression and splicing from liver are causal, each with 3% PVE, 0.9% $\pi$. SNPs have 30% PVE, 2.5e-4 $\pi$.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
source("/project/xinhe/shengqian/cTWAS_simulation/help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_ctwas_plots.R")
#source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")
load("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mashr_sqtl/sqtl/mashr/intron_mapping.RData")

plot_PIP <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_merged <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type,".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined <- function(configtag, runtag, simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined_merged <- function(configtag, runtag, simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}
```

### Simulation 1: Expression and Splicing from Liver (3% PVE)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_E_S_three_tissues/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
param_GTEX_df <- load_parameters(results_dir, runtag, simutags, "GTEXLD")
param_UKBB_df <- load_parameters(results_dir, runtag, simutags, "UKBBLD")
```

### Number of causal genes detected (GTEX LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "GTEXLD", PIP_threshold = 0.8)
```

### Number of causal genes detected (UKBB LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
```

### Estimated Prior Inclusion Probability and PVE (GTEX LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_GTEX_df$`prior_eQTL|Liver`
y2 <- param_GTEX_df$`prior_sQTL|Liver`
y3 <- param_GTEX_df$`prior_eQTL|Adipose`
y4 <- param_GTEX_df$`prior_sQTL|Adipose`
y5 <- param_GTEX_df$`prior_eQTL|Lung`
y6 <- param_GTEX_df$`prior_sQTL|Lung`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_GTEX_df$`pve_eQTL|Liver`
y2 <- param_GTEX_df$`pve_sQTL|Liver`
y3 <- param_GTEX_df$`pve_eQTL|Adipose`
y4 <- param_GTEX_df$`pve_sQTL|Adipose`
y5 <- param_GTEX_df$`pve_eQTL|Lung`
y6 <- param_GTEX_df$`pve_sQTL|Lung`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_GTEX_df$`enrichment_eQTL|Liver`
y2 <- param_GTEX_df$`enrichment_sQTL|Liver`
y3 <- param_GTEX_df$`enrichment_eQTL|Adipose`
y4 <- param_GTEX_df$`enrichment_sQTL|Adipose`
y5 <- param_GTEX_df$`enrichment_eQTL|Lung`
y6 <- param_GTEX_df$`enrichment_sQTL|Lung`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### Estimated Prior Inclusion Probability and PVE (UKBB LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_UKBB_df$`prior_eQTL|Liver`
y2 <- param_UKBB_df$`prior_sQTL|Liver`
y3 <- param_UKBB_df$`prior_eQTL|Adipose`
y4 <- param_UKBB_df$`prior_sQTL|Adipose`
y5 <- param_UKBB_df$`prior_eQTL|Lung`
y6 <- param_UKBB_df$`prior_sQTL|Lung`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_UKBB_df$`pve_eQTL|Liver`
y2 <- param_UKBB_df$`pve_sQTL|Liver`
y3 <- param_UKBB_df$`pve_eQTL|Adipose`
y4 <- param_UKBB_df$`pve_sQTL|Adipose`
y5 <- param_UKBB_df$`pve_eQTL|Lung`
y6 <- param_UKBB_df$`pve_sQTL|Lung`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_UKBB_df$`enrichment_eQTL|Liver`
y2 <- param_UKBB_df$`enrichment_sQTL|Liver`
y3 <- param_UKBB_df$`enrichment_eQTL|Adipose`
y4 <- param_UKBB_df$`enrichment_sQTL|Adipose`
y5 <- param_UKBB_df$`enrichment_eQTL|Lung`
y6 <- param_UKBB_df$`enrichment_sQTL|Lung`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### PIP attribution among tissues by QTL types (UKBBLD)
```{r, echo=FALSE, fig.width= 8, fig.height= 4, warning=FALSE}
f1 <- pip_partition_across_tissue_by_QTLtype(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8, "eQTL","Expression")
f2 <- pip_partition_across_tissue_by_QTLtype(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8, "sQTL","Splicing")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot based on GTEX LD (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "GTEXLD", main = "molecular traits PIPs")
f2 <- plot_PIP_combined(results_dir, runtag, simutags, "GTEXLD", main = "Gene level PIPs")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of expression traits (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of expression traits with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_merged(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_merged(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of gene level PIP (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of gene level PIP with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined_merged(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined_merged(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```
