---
title: "simulation_pip_calibration"
output: html_document
date: '2024-2-13'
editor_options: 
  chunk_output_type: console
---

## One tissue simulation
```{r echo=FALSE}
library(ctwas)
library(tidyr)
library(dplyr)
library(ggplot2)
library(data.table)
library(ggbreak) 
library(ggpubr)
library(gridExtra)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")

plot_PIP_shared_all_ctwas <- function(results_dir, runtag,  simutags, ...){
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_all.ctwas.true_parameter.finemap_regions_res.RDS")
  f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
  return(f1)
}

plot_PIP_shared_type_ctwas <- function(results_dir, runtag,  simutags, ...){
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_type.ctwas.true_parameter.finemap_regions_res.RDS")
  f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
  return(f1)
}

plot_PIP_shared_all_susie <- function(results_dir, runtag,  simutags, ...){
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_all.susie.true_parameter.finemap_regions_res.RDS")
  f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
  return(f1)
}

plot_PIP_shared_type_susie <- function(results_dir, runtag,  simutags, ...){
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_type.susie.true_parameter.finemap_regions_res.RDS")
  f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
  return(f1)
}

plot_power <- function(results_dir,runtag,simutags){
  pipfs_all_ctwas <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_all.ctwas.true_parameter.finemap_regions_res.RDS")
  pipfs_type_ctwas <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_type.ctwas.true_parameter.finemap_regions_res.RDS")
  pipfs_all_susie <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_all.susie.true_parameter.finemap_regions_res.RDS")
  pipfs_type_susie <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_type.susie.true_parameter.finemap_regions_res.RDS")
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")

  cau <- lapply(phenofs, function(x) {load(x);get_causal_id(phenores)})
  df_all_ctwas <- NULL
  for (i in 1:length(pipfs_all_ctwas)) {
    res <- readRDS(pipfs_all_ctwas[i])
    res <- res$finemap_res
    res <- data.frame(res[res$type!="SNP", ])
    res$runtag <- i
    res$ifcausal <- ifelse(res$id %in% cau[[i]], 1, 0)
    df_all_ctwas <- rbind(df_all_ctwas, res)
  }

  df_type_ctwas <- NULL
  for (i in 1:length(pipfs_type_ctwas)) {
    res <- readRDS(pipfs_type_ctwas[i])
    res <- res$finemap_res
    res <- data.frame(res[res$type!="SNP", ])
    res$runtag <- i
    res$ifcausal <- ifelse(res$id %in% cau[[i]], 1, 0)
    df_type_ctwas <- rbind(df_type_ctwas, res)
  }

  df_all_susie <- NULL
  for (i in 1:length(pipfs_all_susie)) {
    res <- readRDS(pipfs_all_susie[i])
    res <- res$finemap_res
    res <- data.frame(res[res$type!="SNP", ])
    res$runtag <- i
    res$ifcausal <- ifelse(res$id %in% cau[[i]], 1, 0)
    df_all_susie <- rbind(df_all_susie, res)
  }

  df_type_susie <- NULL
  for (i in 1:length(pipfs_type_susie)) {
    res <- readRDS(pipfs_type_susie[i])
    res <- res$finemap_res
    res <- data.frame(res[res$type!="SNP", ])
    res$runtag <- i
    res$ifcausal <- ifelse(res$id %in% cau[[i]], 1, 0)
    df_type_susie <- rbind(df_type_susie, res)
  }

  breaks_ranges = rbind(c(0.5, 1), c(0.8,1))
  power_df <- data.frame()
  for(i in 1:nrow(breaks_ranges)){
    breaks = breaks_ranges[i,]
    n_all_ctwas = length(which(df_all_ctwas$susie_pip >= breaks[1] & df_all_ctwas$susie_pip < breaks[2]))
    n_all_ctwas_causal = length(which(df_all_ctwas$susie_pip >= breaks[1] & df_all_ctwas$susie_pip < breaks[2] & df_all_ctwas$ifcausal > 0))
    n_type_ctwas = length(which(df_type_ctwas$susie_pip >= breaks[1] & df_type_ctwas$susie_pip < breaks[2]))
    n_type_ctwas_causal = length(which(df_type_ctwas$susie_pip >= breaks[1] & df_type_ctwas$susie_pip < breaks[2] & df_type_ctwas$ifcausal > 0))
    n_all_susie = length(which(df_all_susie$susie_pip >= breaks[1] & df_all_susie$susie_pip < breaks[2]))
    n_all_susie_causal = length(which(df_all_susie$susie_pip >= breaks[1] & df_all_susie$susie_pip < breaks[2] & df_all_susie$ifcausal > 0))
    n_type_susie = length(which(df_type_susie$susie_pip >= breaks[1] & df_type_susie$susie_pip < breaks[2]))
    n_type_susie_causal = length(which(df_type_susie$susie_pip >= breaks[1] & df_type_susie$susie_pip < breaks[2] & df_type_susie$ifcausal > 0))
    tmp_df <- data.frame(
      "pip_bin" = paste0("PIP: ", breaks[1], "-", breaks[2]),
      "method" = rep(c("ctwas shared all","ctwas shared type","susie shared all","susie shared type"), 2),
      "group" = rep(c("total", "causal"), each = 4),
      "n_var" = c(n_all_ctwas,n_type_ctwas,n_all_susie,n_type_susie,n_all_ctwas_causal,n_type_ctwas_causal,n_all_susie_causal,n_type_susie_causal)     )
    power_df <- rbind(power_df, tmp_df)
  }
  power_df$method <- factor(power_df$method, levels = c("ctwas shared all","ctwas shared type","susie shared all","susie shared type"))
  ggplot(power_df) +
  geom_bar(aes(x = method, y = n_var, fill = group),
           position = "identity", stat = "identity", alpha=0.5, width=0.5) +
  facet_grid(~ pip_bin) +
  labs(x = "", y = "number of variables") +
  theme_cowplot()
}
```

## Enrichment=1 (same variance=10)
gene prior = 2.5e-4, snp prior = 2.5e-4, gene variance = 10, snp variance = 10, gene pve=4.2e-4, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```


```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=10 (same variance=10)
gene prior = 2.5e-3, snp prior = 2.5e-4, gene variance = 10, snp variance = 10, gene pve=4.2e-3, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=40 (same variance=10)
gene prior = 0.01, snp prior = 2.5e-4, gene variance = 10, snp variance = 10, gene pve=0.0168, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=40 (same variance=20)
gene prior = 0.005, snp prior = 1.25e-4, gene variance = 20, snp variance = 20, gene pve=0.0168, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(5, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=40 (same variance=40)
gene prior = 0.0025, snp prior = 6.25e-5, gene variance = 40, snp variance = 40, gene pve=0.0168, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(6, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=40 (gene variance=20, snp variance=10)
gene prior = 0.01, snp prior = 2.5e-4, gene variance = 20, snp variance = 10, gene pve=0.0336, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(7, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=40 (gene variance=40, snp variance=10)
gene prior = 0.01, snp prior = 2.5e-4, gene variance = 40, snp variance = 10, gene pve=0.0672, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(8, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```

## Enrichment=80 (same variance=10)
gene prior = 0.02, snp prior = 2.5e-4, gene variance = 10, snp variance = 10, gene pve=0.0336, snp pve=0.3

```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")
```

```{r, echo=FALSE, fig.width= 8, fig.height= 8}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f2 <- plot_PIP_shared_type_ctwas(results_dir, runtag, simutags, main = "ctwas shared type")
f3 <- plot_PIP_shared_all_susie(results_dir, runtag, simutags, main = "susie shared all")
f4 <- plot_PIP_shared_type_susie(results_dir, runtag, simutags, main = "susie shared type")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol = 2)
```

```{r, echo=FALSE, fig.width= 8, fig.height= 4}
plot_power(results_dir, runtag, simutags)
```