---
title: "Seven Uncorrelated Tissues Simulation"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of seven uncorrelated tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Seven tissues used in this simulation are Liver, Lung, Whole_Blood, Adipose_Subcutaneous, Artery_Tibial, Heart_Left_Ventricle, Stomach. The first three tissues are set to be causal and the other four tissues are non-causal. 

```{r echo=FALSE}
load("/project/xinhe/xsun/ctwas/1.matching_tissue/data/tissue_cor.rdata")
data <- lat[colnames(lat)%in%c("Liver","Lung","Whole_Blood","Adipose_Subcutaneous","Artery_Tibial","Heart_Left_Ventricle","Stomach"),rownames(lat)%in%c("Liver","Lung","Whole_Blood","Adipose_Subcutaneous","Artery_Tibial","Heart_Left_Ventricle","Stomach")]
colnames(data) <- c("Adipose","Lung","Artery","Stomach","Heart","Whole_Blood","Liver")
rownames(data) <- c("Adipose","Lung","Artery","Stomach","Heart","Whole_Blood","Liver")
data <- round(data,3)
data
```

```{r echo=FALSE}
library(ctwas)
library(data.table)
require(latex2exp)
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_ctwas_plots.R")
source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")
plot_PIP <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".susieIrss.txt")
   f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_combined <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".susieIrss.txt")
   f1 <- caliPIP_plot_combined(phenofs, susieIfs, ...) 
   return(f1)
}
```

## Simulation 1: 3% PVE for Causal Tissues and 0% PVE for Non-causal Tissues. 

### Shared Prior Variance Parameters

```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_uncorrelated_seven_tissues/"
runtag = "ukb-s80.45-3_7uncorr"
configtag <- 1

simutags <- paste(1, 1:5, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8

results_df <- get_sim_joint_res(results_dir,runtag,configtag,simutags,thin,sample_size,PIP_threshold)[[1]]
group_size <- get_sim_joint_res(results_dir,runtag,configtag,simutags,thin,sample_size,PIP_threshold)[[2]]
```

### Results using PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)
```

### Results using Combined PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)
```

### Estimated Prior Inclusion Probability
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_Liver
y2 <- results_df$prior_Lung
y3 <- results_df$prior_Whole_Blood
y4 <- results_df$prior_Adipose_Subcutaneous
y5 <- results_df$prior_Artery_Tibial
y6 <- results_df$prior_Heart_Left_Ventricle
y7 <- results_df$prior_Stomach

truth <- rbind(c(1,0.009),c(2,0.009),c(3,0.009),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,0.025),ylab="Prior inclusion")
```

### Estimated PVE
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver
y2 <- results_df$pve_Lung
y3 <- results_df$pve_Whole_Blood
y4 <- results_df$pve_Adipose_Subcutaneous
y5 <- results_df$pve_Artery_Tibial
y6 <- results_df$pve_Heart_Left_Ventricle
y7 <- results_df$pve_Stomach

truth <- rbind(c(1,0.03),c(2,0.03),c(3,0.03),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,0.06),ylab="PVE")
```

### Estimated Prior Variance
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_var_Liver
y2 <- results_df$prior_var_Lung
y3 <- results_df$prior_var_Whole_Blood
y4 <- results_df$prior_var_Adipose_Subcutaneous
y5 <- results_df$prior_var_Artery_Tibial
y6 <- results_df$prior_var_Heart_Left_Ventricle
y7 <- results_df$prior_var_Stomach

t1 <- 0.03*sample_size/(group_size[2]*0.009)
t2 <- 0.03*sample_size/(group_size[3]*0.009)
t3 <- 0.03*sample_size/(group_size[4]*0.009)
t4 <- 0
t5 <- 0
t6 <- 0
t7 <- 0

truth <- rbind(c(1,t1),c(2,t2),c(3,t3),c(4,t4),c(5,t5),c(6,t6),c(7,t7))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,30),ylab=TeX("$sigma^2$"))
```

### Estimated Enrichment
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver/results_df$prior_SNP
y2 <- results_df$pve_Lung/results_df$prior_SNP
y3 <- results_df$pve_Whole_Blood/results_df$prior_SNP
y4 <- results_df$pve_Adipose_Subcutaneous/results_df$prior_SNP
y5 <- results_df$pve_Artery_Tibial/results_df$prior_SNP
y6 <- results_df$pve_Heart_Left_Ventricle/results_df$prior_SNP
y7 <- results_df$pve_Stomach/results_df$prior_SNP

truth <- rbind(c(1,120),c(2,120),c(3,120),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,250),ylab= TeX("Enrichment $\\pi_G/\\pi_V$"))
```

### PIP Calibration Plot
```{r, fig.width= 8, fig.height= 4, echo=FALSE, message=FALSE}
f1 <- plot_PIP(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### Separate effect size parameters

```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_uncorrelated_seven_tissues/"
runtag = "ukb-s80.45-3_7uncorr"
configtag <- 2

simutags <- paste(1, 1:5, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8

results_df <- get_sim_joint_res(results_dir,runtag,configtag,simutags,thin,sample_size,PIP_threshold)
group_size <- results_df[[2]]
results_df <- results_df[[1]]
```

### Results using PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)
```

### Results using Combined PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)
```

### Estimated Prior Inclusion Probability
```{r, fig.width= 8, fig.height= 5, echo=FALSE}
y1 <- results_df$prior_Liver
y2 <- results_df$prior_Lung
y3 <- results_df$prior_Whole_Blood
y4 <- results_df$prior_Adipose_Subcutaneous
y5 <- results_df$prior_Artery_Tibial
y6 <- results_df$prior_Heart_Left_Ventricle
y7 <- results_df$prior_Stomach

truth <- rbind(c(1,0.009),c(2,0.009),c(3,0.009),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Whole_Blood","Adipose_Subcutaneous","Artery_Tibial","Heart_Left_Ventricle","Stomach"),ylim=c(0,0.025),ylab="Prior inclusion")
```

### Estimated PVE
```{r, fig.width= 8, fig.height= 5, echo=FALSE}
y1 <- results_df$pve_Liver
y2 <- results_df$pve_Lung
y3 <- results_df$pve_Whole_Blood
y4 <- results_df$pve_Adipose_Subcutaneous
y5 <- results_df$pve_Artery_Tibial
y6 <- results_df$pve_Heart_Left_Ventricle
y7 <- results_df$pve_Stomach

truth <- rbind(c(1,0.03),c(2,0.03),c(3,0.03),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Whole_Blood","Adipose_Subcutaneous","Artery_Tibial","Heart_Left_Ventricle","Stomach"),ylim=c(0,0.06),ylab="PVE")
```

### Estimated Prior Variance
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_var_Liver
y2 <- results_df$prior_var_Lung
y3 <- results_df$prior_var_Whole_Blood
y4 <- results_df$prior_var_Adipose_Subcutaneous
y5 <- results_df$prior_var_Artery_Tibial
y6 <- results_df$prior_var_Heart_Left_Ventricle
y7 <- results_df$prior_var_Stomach

t1 <- 0.03*sample_size/(group_size[2]*0.009)
t2 <- 0.03*sample_size/(group_size[3]*0.009)
t3 <- 0.03*sample_size/(group_size[4]*0.009)
t4 <- 0
t5 <- 0
t6 <- 0
t7 <- 0

truth <- rbind(c(1,t1),c(2,t2),c(3,t3),c(4,t4),c(5,t5),c(6,t6),c(7,t7))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,30),ylab=TeX("$sigma^2$"))
```

### Estimated Enrichment
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver/results_df$prior_SNP
y2 <- results_df$pve_Lung/results_df$prior_SNP
y3 <- results_df$pve_Whole_Blood/results_df$prior_SNP
y4 <- results_df$pve_Adipose_Subcutaneous/results_df$prior_SNP
y5 <- results_df$pve_Artery_Tibial/results_df$prior_SNP
y6 <- results_df$pve_Heart_Left_Ventricle/results_df$prior_SNP
y7 <- results_df$pve_Stomach/results_df$prior_SNP

truth <- rbind(c(1,120),c(2,120),c(3,120),c(4,0),c(5,0),c(6,0),c(7,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6),cbind(7,y7))
plot_par_7(truth,est,xlabels = c("Liver","Lung","Blood","Adipose","Artery","Heart","Stomach"),ylim=c(0,250),ylab= TeX("Enrichment $\\pi_G/\\pi_V$"))
```

### PIP Calibration Plot
```{r, fig.width= 8, fig.height= 4, echo=FALSE, message=FALSE}
f1 <- plot_PIP(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```