---
title: "Expression and Splicing from three tissues simulations"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of expression and splicing traits from three tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Three tissues used in this simulation are Liver, Adipose and Lung. 
Only expression and splicing from liver are causal, each with 3% PVE, 0.9% $\pi$. SNPs have 30% PVE, 2.5e-4 $\pi$.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
source("/project/xinhe/shengqian/cTWAS_simulation/help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_ctwas_plots.R")
source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")

plot_PIP <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_merged <- function(results_dir, runtag,  simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type,".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined <- function(configtag, runtag, simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}

plot_PIP_combined_merged <- function(configtag, runtag, simutags, LD_type, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_", LD_type, ".finemap_merged_regions.res.RDS")
   f1 <- caliPIP_plot_E_S_combined_csindex(phenofs, susieIfs, ...) 
   return(f1)
}
```

### Simulation 1: Expression and Splicing from Liver (3% PVE)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_E_S_three_tissues/"
runtag = "E_S_three_tissues"
simutags <- paste(1, 1:5, sep = "-")
param_GTEX_df <- load_parameters(results_dir, runtag, simutags, "GTEXLD")
param_UKBB_df <- load_parameters(results_dir, runtag, simutags, "UKBBLD")
```

### Number of causal genes detected (GTEX LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "GTEXLD", PIP_threshold = 0.8)
```

### Number of causal genes detected (UKBB LD)
```{r echo=FALSE}
check_n_detected_multi(results_dir, runtag, simutags, "UKBBLD", PIP_threshold = 0.8)
```

### Estimated Prior Inclusion Probability and PVE (GTEX LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_GTEX_df$`prior_eQTL|Liver`
y2 <- param_GTEX_df$`prior_sQTL|Liver`
y3 <- param_GTEX_df$`prior_eQTL|Adipose`
y4 <- param_GTEX_df$`prior_sQTL|Adipose`
y5 <- param_GTEX_df$`prior_eQTL|Lung`
y6 <- param_GTEX_df$`prior_sQTL|Lung`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_GTEX_df$`pve_eQTL|Liver`
y2 <- param_GTEX_df$`pve_sQTL|Liver`
y3 <- param_GTEX_df$`pve_eQTL|Adipose`
y4 <- param_GTEX_df$`pve_sQTL|Adipose`
y5 <- param_GTEX_df$`pve_eQTL|Lung`
y6 <- param_GTEX_df$`pve_sQTL|Lung`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_GTEX_df$`enrichment_eQTL|Liver`
y2 <- param_GTEX_df$`enrichment_sQTL|Liver`
y3 <- param_GTEX_df$`enrichment_eQTL|Adipose`
y4 <- param_GTEX_df$`enrichment_sQTL|Adipose`
y5 <- param_GTEX_df$`enrichment_eQTL|Lung`
y6 <- param_GTEX_df$`enrichment_sQTL|Lung`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### Estimated Prior Inclusion Probability and PVE (UKBB LD)
`````{r, fig.width= 15, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
par(mfrow = c(1, 3))
y1 <- param_UKBB_df$`prior_eQTL|Liver`
y2 <- param_UKBB_df$`prior_sQTL|Liver`
y3 <- param_UKBB_df$`prior_eQTL|Adipose`
y4 <- param_UKBB_df$`prior_sQTL|Adipose`
y5 <- param_UKBB_df$`prior_eQTL|Lung`
y6 <- param_UKBB_df$`prior_sQTL|Lung`
truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.025),ylab="Prior inclusion", main="Prior Inclusion Probability")

y1 <- param_UKBB_df$`pve_eQTL|Liver`
y2 <- param_UKBB_df$`pve_sQTL|Liver`
y3 <- param_UKBB_df$`pve_eQTL|Adipose`
y4 <- param_UKBB_df$`pve_sQTL|Adipose`
y5 <- param_UKBB_df$`pve_eQTL|Lung`
y6 <- param_UKBB_df$`pve_sQTL|Lung`
truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,0.06),ylab="PVE", main="PVE")

y1 <- param_UKBB_df$`enrichment_eQTL|Liver`
y2 <- param_UKBB_df$`enrichment_sQTL|Liver`
y3 <- param_UKBB_df$`enrichment_eQTL|Adipose`
y4 <- param_UKBB_df$`enrichment_sQTL|Adipose`
y5 <- param_UKBB_df$`enrichment_eQTL|Lung`
y6 <- param_UKBB_df$`enrichment_sQTL|Lung`
truth <- rbind(c(1,36),c(2,36),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver E", "Liver S", "Adipose E", "Adipose S", "Lung E", "Lung S"),ylim=c(0,80),ylab="Enrichment", main="Enrichment")
```

### PIP attribution among tissues (GTEXLD)
```{r, echo=FALSE, fig.width= 5, fig.height= 4, warning=FALSE}
plot_df <- data.frame()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
  finemap_res <- readRDS(paste0(results_dir, runtag, "_simu",simutag, "_", "GTEXLD", ".finemap_regions.res.RDS"))
  finemap_sQTL_res <- finemap_res[finemap_res$type=="sQTL",]
  finemap_sQTL_res$gene <- sapply(finemap_sQTL_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  finemap_sQTL_res <- finemap_sQTL_res %>% join(intron_info, by = "gene") %>% dplyr::select(-gene)
  finemap_eQTL_res <- finemap_res[finemap_res$type=="eQTL",]
  finemap_eQTL_res$gene_id <- sapply(finemap_eQTL_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  finemap_gene_res <- rbind(finemap_eQTL_res,finemap_sQTL_res)
  df_gene <- aggregate(finemap_gene_res$susie_pip, by=list(finemap_gene_res$gene_id), FUN=sum)
  colnames(df_gene) <- c("gene_id", "combined_pip")
  for(j in unique(finemap_gene_res$context)){
    tmp_res <- finemap_gene_res[finemap_gene_res$context==j,]
    tmp_res <- tmp_res[,c("gene_id","susie_pip")]
    tmp_res <- aggregate(tmp_res$susie_pip, by=list(tmp_res$gene_id), FUN=sum)
    colnames(tmp_res) <- c("gene_id",j)
    df_gene <- df_gene %>% join(tmp_res, by = "gene_id") %>% replace(is.na(.), 0)
  }
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
  df_gene[,c(3:ncol(df_gene))] <- df_gene[,c(3:ncol(df_gene))]/df_gene$combined_pip
  plot_df <- rbind(plot_df,df_gene)
}
contexts <- colnames(plot_df)[-c(1,2)]
data <- data.frame()
for(i in contexts){
  data <- rbind(data,cbind(i,plot_df[,i]))
}
colnames(data) <- c("tissue","attribution")
data$attribution <- as.numeric(data$attribution)
data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```


```{r}
plot_df <- data.frame()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
  finemap_res <- readRDS(paste0(results_dir, runtag, "_simu",simutag, "_", "GTEXLD", ".finemap_regions.res.RDS"))
  finemap_sQTL_res <- finemap_res[finemap_res$type=="sQTL",]
  finemap_sQTL_res$gene <- sapply(finemap_sQTL_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  finemap_sQTL_res <- finemap_sQTL_res %>% join(intron_info, by = "gene") %>% dplyr::select(-gene)
  finemap_eQTL_res <- finemap_res[finemap_res$type=="eQTL",]
  finemap_eQTL_res$gene_id <- sapply(finemap_eQTL_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  finemap_gene_res <- rbind(finemap_eQTL_res,finemap_sQTL_res)
  df_gene <- aggregate(finemap_gene_res$susie_pip, by=list(finemap_gene_res$gene_id), FUN=sum)
  colnames(df_gene) <- c("gene_id", "combined_pip")
  for(j in unique(finemap_gene_res$type)){
    tmp_res <- finemap_gene_res[finemap_gene_res$type==j,]
    tmp_res <- tmp_res[,c("gene_id","susie_pip")]
    tmp_res <- aggregate(tmp_res$susie_pip, by=list(tmp_res$gene_id), FUN=sum)
    colnames(tmp_res) <- c("gene_id",j)
    df_gene <- df_gene %>% join(tmp_res, by = "gene_id") %>% replace(is.na(.), 0)
  }
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
  df_gene[,c(3:ncol(df_gene))] <- df_gene[,c(3:ncol(df_gene))]/df_gene$combined_pip
  plot_df <- rbind(plot_df,df_gene)
}
types <- colnames(plot_df)[-c(1,2)]
data <- data.frame()
for(i in types){
  data <- rbind(data,cbind(i,plot_df[,i]))
}
colnames(data) <- c("QTLtype","attribution")
data$attribution <- as.numeric(data$attribution)
data$QTLtype <- factor(data$QTLtype, levels=unique(data$QTLtype))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "QTLtype", 
          y = "attribution", 
          add = "mean_se", 
          fill = "QTLtype", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```


### PIP Calibration Plot based on GTEX LD (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
load("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mashr_sqtl/sqtl/mashr/intron_mapping.RData")
f1 <- plot_PIP(results_dir, runtag, simutags, "GTEXLD", main = "molecular traits PIPs")
f2 <- plot_PIP_combined(results_dir, runtag, simutags, "GTEXLD", main = "Gene level PIPs")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of expression traits (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of expression traits with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_merged(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_merged(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of gene level PIP (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```

### PIP Calibration Plot of gene level PIP with region merge (filter out cs index 0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_combined_merged(results_dir, runtag, simutags, "GTEXLD", main = "GTEX LD")
f2 <- plot_PIP_combined_merged(results_dir, runtag, simutags, "UKBBLD", main = "UKBB LD")
gridExtra::grid.arrange(f1, f2, ncol=2)
```
