---
title: "Simulation Results using simulated (correlated)"
author: "shengqian"
date: "2023-12-3"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r}
source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")
```

## Simulation 1: Liver and three 95% correlated tissues

### Shared effect size parameters

30% PVE and 2.5e-4 prior inclusion for SNPs, 5% PVE and 0.015 prior inclusion for Liver, 1% PVE and 0.003 prior inclusion for other three mixed groups. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_95/"
runtag = "ukb-s80.45-3_corr"
configtag <- 1
simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1
sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_95_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_95_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_95_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_95_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_95_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_95_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_95_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_95_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_95_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,0.07),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```

### Separate effect size parameters

For the cTWAS analysis, each tissue had its own prior inclusion parameter end effect size parameter. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_95/"
runtag = "ukb-s80.45-3_corr"
configtag <- 2
simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1
sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_95_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_95_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_95_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_95_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_95_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_95_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_95_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_95_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_95_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","95-1","95-2","95-3"),ylim=c(0,0.1),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_95_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```
## Simulation 2: Liver and 50% correlated tissues 

### Shared effect size parameters

30% PVE and 2.5e-4 prior inclusion for SNPs, 5% PVE and 0.015 prior inclusion for Liver, 1% PVE and 0.003 prior inclusion for other three mixed groups. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_50/"
runtag = "ukb-s80.45-3_corr"
configtag <- 1
simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1
sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_50_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_50_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_50_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_50_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_50_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_50_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_50_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_50_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_50_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,0.1),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```

### Separate effect size parameters

For the cTWAS analysis, each tissue had its own prior inclusion parameter end effect size parameter. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_50/"
runtag = "ukb-s80.45-3_corr"
configtag <- 2

simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_50_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_50_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_50_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_50_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_50_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_50_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_50_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_50_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_50_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","50-1","50-2","50-3"),ylim=c(0,0.1),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_50_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```

## Simulation 3: Liver and 5% correlated tissues 

### Shared effect size parameters

30% PVE and 2.5e-4 prior inclusion for SNPs, 5% PVE and 0.015 prior inclusion for Liver, 1% PVE and 0.003 prior inclusion for other three mixed groups. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_05/"
runtag = "ukb-s80.45-3_corr"
configtag <- 1

simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_05_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_05_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_05_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_05_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_05_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_05_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_05_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_05_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_05_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,0.1),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```

### Separate effect size parameters

For the cTWAS analysis, each tissue had its own prior inclusion parameter end effect size parameter. 

```{r}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/simulation_uncorrelated_four_tissues_05/"
runtag = "ukb-s80.45-3_corr"
configtag <- 2

simutags <- paste(1, 1:3, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8
```

```{r echo=FALSE}
results_df <- data.frame(simutag=as.character(),
                              n_causal=as.integer(),
                              n_causal_combined=as.integer(),
                              n_detected_pip=as.integer(),
                              n_detected_pip_in_causal=as.integer(),
                              n_detected_comb_pip=as.integer(),
                              n_detected_comb_pip_in_causal=as.integer(),
                              pve_snp=as.numeric(),
                              pve_weight1=as.numeric(),
                              pve_weight2=as.numeric(),
                              pve_weight3=as.numeric(),
                              pve_weight4=as.numeric(),
                              prior_weight1=as.numeric(),
                              prior_weight2=as.numeric(),
                              prior_weight3=as.numeric(),
                              prior_weight4=as.numeric(),
                              prior_var_snp=as.numeric(),
                              prior_var_weight1=as.numeric(),
                              prior_var_weight2=as.numeric(),
                              prior_var_weight3=as.numeric(),
                              prior_var_weight4=as.numeric(),
                              n_detected_twas=as.integer(),
                              n_detected_twas_in_causal=as.integer(),
                              n_detected_comb_twas=as.integer(),
                              n_detected_comb_twas_in_causal=as.integer())

for (i in 1:length(simutags)){
  simutag <- simutags[i]
  
  #load genes with true simulated effect
  load(paste0(results_dir, runtag, "_simu", simutag, "-pheno.Rd"))
  true_genes <- unlist(sapply(1:22, function(x){phenores$batch[[x]]$id.cgene}))
  true_genes_combined <- unique(sapply(true_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
  
  #number of causal genes
  n_causal <- length(true_genes)
  n_causal_combined <- length(true_genes_combined)
  
  #number of gene+tissue combinations with cTWAS PIP > threshold
  n_ctwas_genes <- sum(ctwas_gene_res$susie_pip > PIP_threshold)
  
  #number of cTWAS genes that are causal
  n_causal_detected <- sum(ctwas_gene_res$id[ctwas_gene_res$susie_pip > PIP_threshold] %in% true_genes)
  
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
  ctwas_gene_res_combined <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(ctwas_gene_res_combined) <- c("gene", "pip_combined")
  
  #number of genes with combined PIP > threshold
  n_ctwas_genes_combined <- sum(ctwas_gene_res_combined$pip_combined > PIP_threshold)
  
  #number of cTWAS genes using combined PIP that are causal
  n_causal_detected_combined <- sum(ctwas_gene_res_combined$gene[ctwas_gene_res_combined$pip_combined > PIP_threshold] %in% true_genes_combined)
  
  #collect number of SNPs analyzed by cTWAS
  ctwas_res_s1 <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s1.susieIrss.txt"))
  n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
  rm(ctwas_res_s1)
  
  #load estimated parameters
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.s2.susieIrssres.Rd"))
  
  #estimated group prior (all iterations)
  estimated_group_prior_all <- group_prior_rec
  estimated_group_prior_all["SNP",] <- estimated_group_prior_all["SNP",]*thin #adjust parameter to account for thin argument
  
  #estimated group prior variance (all iterations)
  estimated_group_prior_var_all <- group_prior_var_rec
  
  #set group size
  group_size <- c(table(ctwas_gene_res$type), structure(n_snps, names="SNP"))
  group_size <- group_size[rownames(estimated_group_prior_all)]
  
  #estimated group PVE (all iterations)
  estimated_group_pve_all <- estimated_group_prior_var_all*estimated_group_prior_all*group_size/sample_size #check PVE calculation
  
  #multitissue TWAS analysis with bonferroni adjusted threshold for z scores
  load(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag,"_LDR_z_gene.Rd"))
  alpha <- 0.05
  sig_thresh <- qnorm(1-(alpha/nrow(z_gene)/2), lower=T)
  twas_genes <- z_gene$id[abs(z_gene$z)>sig_thresh]
  twas_genes_combined <- unique(sapply(twas_genes, function(x){unlist(strsplit(x, "[|]"))[1]}))
  
  n_twas_genes <- length(twas_genes)
  n_twas_genes_combined <- length(twas_genes_combined)
  
  n_twas_genes_in_causal <- sum(twas_genes %in% true_genes)
  n_twas_genes_in_causal_combined <- sum(twas_genes_combined %in% true_genes_combined)

  results_current <- data.frame(simutag=as.character(simutag),
                                n_causal=as.integer(n_causal),
                                n_causal_combined=as.integer(n_causal_combined),
                                n_detected_pip=as.integer(n_ctwas_genes),
                                n_detected_pip_in_causal=as.integer(n_causal_detected),
                                n_detected_comb_pip=as.integer(n_ctwas_genes_combined),
                                n_detected_comb_pip_in_causal=as.integer(n_causal_detected_combined),
                                pve_snp=as.numeric(rev(estimated_group_pve_all["SNP",])[1]),
                                pve_weight1=as.numeric(rev(estimated_group_pve_all["Liver",])[1]),
                                pve_weight2=as.numeric(rev(estimated_group_pve_all["weight_05_1",])[1]),
                                pve_weight3=as.numeric(rev(estimated_group_pve_all["weight_05_2",])[1]),
                                pve_weight4=as.numeric(rev(estimated_group_pve_all["weight_05_3",])[1]),
                                prior_snp=as.numeric(rev(estimated_group_prior_all["SNP",])[1]),
                                prior_weight1=as.numeric(rev(estimated_group_prior_all["Liver",])[1]),
                                prior_weight2=as.numeric(rev(estimated_group_prior_all["weight_05_1",])[1]),
                                prior_weight3=as.numeric(rev(estimated_group_prior_all["weight_05_2",])[1]),
                                prior_weight4=as.numeric(rev(estimated_group_prior_all["weight_05_3",])[1]),
                                prior_var_snp=as.numeric(rev(estimated_group_prior_var_all["SNP",])[1]),
                                prior_var_weight1=as.numeric(rev(estimated_group_prior_var_all["Liver",])[1]),
                                prior_var_weight2=as.numeric(rev(estimated_group_prior_var_all["weight_05_1",])[1]),
                                prior_var_weight3=as.numeric(rev(estimated_group_prior_var_all["weight_05_2",])[1]),
                                prior_var_weight4=as.numeric(rev(estimated_group_prior_var_all["weight_05_3",])[1]),
                                n_detected_twas=as.integer(n_twas_genes),
                                n_detected_twas_in_causal=as.integer(n_twas_genes_in_causal),
                                n_detected_comb_twas=as.integer(n_twas_genes_combined),
                                n_detected_comb_twas_in_causal=as.integer(n_twas_genes_in_causal_combined))
  
  results_df <- rbind(results_df, results_current)
}
```

```{r}
#results using PIP threshold (gene+tissue)
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]

#mean percent causal using PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)

#results using combined PIP threshold
results_df[,c("simutag", "n_causal_combined", "n_detected_comb_pip", "n_detected_comb_pip_in_causal")]

#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_comb_pip_in_causal)/sum(results_df$n_detected_comb_pip)

#prior inclusion and mean prior inclusion
results_df[,c(which(colnames(results_df)=="simutag"), setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df))))]

colMeans(results_df[,setdiff(grep("prior", names(results_df)), grep("prior_var", names(results_df)))])

#prior variance and mean prior variance
results_df[,c(which(colnames(results_df)=="simutag"), grep("prior_var", names(results_df)))]

colMeans(results_df[,grep("prior_var", names(results_df))])

#PVE and mean PVE
results_df[,c(which(colnames(results_df)=="simutag"), grep("pve", names(results_df)))]

colMeans(results_df[,grep("pve", names(results_df))])

#TWAS results
results_df[,c(which(colnames(results_df)=="simutag"), grep("twas", names(results_df)))]

sum(results_df$n_detected_comb_twas_in_causal)/sum(results_df$n_detected_comb_twas)
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1
y2 <- results_df$prior_weight2
y3 <- results_df$prior_weight3
y4 <- results_df$prior_weight4

truth <- rbind(c(1,0.015),c(2,0.003),c(3,0.003),c(4,0.003))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,0.025),ylab="Prior inclusion")
```

```{r echo=FALSE}
y1 <- results_df$prior_weight1/results_df$prior_snp
y2 <- results_df$prior_weight2/results_df$prior_snp
y3 <- results_df$prior_weight3/results_df$prior_snp
y4 <- results_df$prior_weight4/results_df$prior_snp

truth <- rbind(c(1,60),c(2,12),c(3,12),c(4,12))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,100),ylab="Enrichment")
```

```{r echo=FALSE}
y1 <- results_df$pve_weight1
y2 <- results_df$pve_weight2
y3 <- results_df$pve_weight3
y4 <- results_df$pve_weight4

truth <- rbind(c(1,0.05),c(2,0.01),c(3,0.01),c(4,0.01))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
plot_par_4(truth,est,xlabels = c("Liver","05-1","05-2","05-3"),ylim=c(0,0.1),ylab="PVE")
```

```{r echo=FALSE}
Liver_attr <- c()
mix1_attr <- c()
mix2_attr <- c()
mix3_attr <- c()
for (i in 1:length(simutags)){
  simutag <- simutags[i]
    
  #load cTWAS results
  ctwas_res <- data.table::fread(paste0(results_dir, runtag, "_simu", simutag, "_config", configtag, "_LDR.susieIrss.txt"))
  ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
    
  #collapse gene+tissues to genes and compute combined PIP
  ctwas_gene_res$gene <- sapply(ctwas_gene_res$id, function(x){unlist(strsplit(x,"[|]"))[1]})
    
  df_Liver <- ctwas_gene_res[ctwas_gene_res$type=="Liver",]
  df_mix1 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_1",]
  df_mix2 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_2",]
  df_mix3 <- ctwas_gene_res[ctwas_gene_res$type=="weight_05_3",]
  
  df_gene <- aggregate(ctwas_gene_res$susie_pip, by=list(ctwas_gene_res$gene), FUN=sum)
  colnames(df_gene) <- c("gene", "combined_pip")
  df_gene$Liver_pip <-0
  df_gene$mix1_pip <-0
  df_gene$mix2_pip <-0
  df_gene$mix3_pip <-0
    
  for(i in df_gene$gene){
    if(i %in% df_Liver$gene){
      df_gene[df_gene$gene==i,"Liver_pip"] <- round(df_Liver[df_Liver$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix1$gene){
      df_gene[df_gene$gene==i,"mix1_pip"] <- round(df_mix1[df_mix1$gene==i,"susie_pip"],3)
    }
  }
    
  for(i in df_gene$gene){
    if(i %in% df_mix2$gene){
      df_gene[df_gene$gene==i,"mix2_pip"] <- round(df_mix2[df_mix2$gene==i,"susie_pip"],3)
    }
  }
  
  for(i in df_gene$gene){
    if(i %in% df_mix3$gene){
      df_gene[df_gene$gene==i,"mix3_pip"] <- round(df_mix3[df_mix3$gene==i,"susie_pip"],3)
    }
  }
  
  df_gene$combined_pip <- round(df_gene$combined_pip,3)
  #sort by combined PIP
  df_gene <- df_gene[order(-df_gene$combined_pip),]
  #genes with PIP>0.8 or 20 highest PIPs
  df_gene <- df_gene[df_gene$combined_pip>0.8,]
    
  Liver_attr <- c(Liver_attr,df_gene$Liver_pip/df_gene$combined_pip)
  mix1_attr <- c(mix1_attr,df_gene$mix1_pip/df_gene$combined_pip)
  mix2_attr <- c(mix2_attr,df_gene$mix2_pip/df_gene$combined_pip)
  mix3_attr <- c(mix3_attr,df_gene$mix3_pip/df_gene$combined_pip)
}

pip_df <- list(Liver_attr,mix1_attr,mix2_attr,mix3_attr)
```

```{r echo=FALSE}
data <- data.frame(
  tissue=c(rep("Liver",length(pip_df[[1]])), rep("mix1",length(pip_df[[2]])), rep("mix2",length(pip_df[[3]])), rep("mix3",length(pip_df[[4]]))),
  attribution=c(pip_df[[1]],pip_df[[2]],pip_df[[3]],pip_df[[4]])
)

data$tissue <- factor(data$tissue, levels=unique(data$tissue))

#pdf(file = "./primary_set2.pdf", width = 5, height = 5)
ggbarplot(data, 
          x = "tissue", 
          y = "attribution", 
          add = "mean_se", 
          fill = "tissue", 
          legend = "none", 
          ylab="Proportion", 
          xlab="",
          palette = c("#7fc97f", "#beaed4", "#fdc086", "#92c5de")) + grids(linetype = "dashed") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#dev.off()
```