---
title: "simulation_one_tissue_no_enrichment"
output: html_document
date: '2024-3-18'
editor_options: 
  chunk_output_type: console
---

## One tissue simulation
```{r echo=FALSE}
library(ctwas)
library(tidyr)
library(dplyr)
library(ggplot2)
library(data.table)
library(ggbreak) 
library(ggpubr)
library(gridExtra)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")

plot_prior_inclusion <- function(results_dir,runtag,simutags,thins,group_prior_var_structures, null_methods, file_name, true_value_gene1, true_value_gene2, true_value_SNP){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas", file_name)
      y1 <- param_df_ctwas$`prior_liver|expression`
      y2 <- param_df_ctwas$`prior_adipose|expression`
      y3 <- param_df_ctwas$prior_SNP
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie", file_name)
      y4 <- param_df_susie$`prior_liver|expression`
      y5 <- param_df_susie$`prior_adipose|expression`
      y6 <- param_df_susie$prior_SNP
      truth <- rbind(c(1,true_value_gene1),c(2,true_value_gene2),c(3,true_value_SNP),c(4,true_value_gene1),c(5,true_value_gene2),c(6,true_value_SNP))
      est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
      plot_par_6(truth,est,xlabels = c("ctwas liver", "ctwas adipose", "ctwas SNP", "susie liver", "susie adipose", "susie SNP"),ylim=c(0,max(est[,2],truth[,2])),ylab="Prior inclusion", main=group_prior_var_structure)
    }
  }
}

plot_prior_variance <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas", file_name)
      y1 <- param_df_ctwas$`prior_var_liver|expression`
      y2 <- param_df_ctwas$`prior_var_adipose|expression`
      y3 <- param_df_ctwas$prior_var_SNP
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie", file_name)
      y4 <- param_df_susie$`prior_var_liver|expression`
      y5 <- param_df_susie$`prior_var_adipose|expression`
      y6 <- param_df_susie$prior_var_SNP
      truth <- rbind(c(1,true_value_gene1),c(2,true_value_gene2),c(3,true_value_SNP),c(4,true_value_gene1),c(5,true_value_gene2),c(6,true_value_SNP))
      est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
      plot_par_6(truth,est,xlabels = c("ctwas liver", "ctwas adipose", "ctwas SNP", "susie liver", "susie adipose", "susie SNP"),ylim=c(0,max(est[,2],truth[,2])),ylab="Prior variance", main=group_prior_var_structure)
    }
  }
}

plot_enrichment <- function(results_dir, runtag, thins, group_prior_var_structures, null_methods, file_name, enrichment_true) {
  plots <- list()  # Store plots in a list
  plot_idx <- 1
  
  for (group_prior_var_structure in group_prior_var_structures) {
    for (thin in thins) {
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas", file_name)
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie", file_name)
      #param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie", file_name)

      df <- data.frame(null_method = rep(c("ctwas liver", "ctwas adipose", "susie liver", "susie adipose"), each = 10),
                       pos = c(rep(1, 10), rep(2, 10), rep(3, 10), rep(4, 10)),
                       enrichment = c(param_df_ctwas$`enrichment_liver|expression`, param_df_ctwas$`enrichment_adipose|expression`,
                                      param_df_susie$`enrichment_liver|expression`, param_df_susie$`enrichment_adipose|expression`),
                       se = c(param_df_ctwas$`enrichment_se_liver|expression`, param_df_ctwas$`enrichment_se_adipose|expression`, 
                              param_df_susie$`enrichment_se_liver|expression`, param_df_susie$`enrichment_se_adipose|expression`))  # Fix repeated `se` values
      
      df$pos <- jitter(df$pos, amount = 0.2)
      
      p <- ggplot(df, aes(x = pos, y = enrichment, group = null_method, color = null_method)) +
        geom_point() +
        geom_errorbar(aes(ymin = enrichment - 1.96 * se, ymax = enrichment + 1.96 * se), width = 0.01) +
        geom_hline(yintercept = enrichment_true, linetype = "dashed", color = "blue") +
        labs(x = "", y = "log(Enrichment)", title = paste("Enrichment -", group_prior_var_structure, "Thin =", thin)) +
        scale_x_continuous(breaks = c(1, 2), labels = c("Gene (ctwas)", "Gene (susie)")) +
        ylim(c(-5,5)) +
        theme_minimal()
      
      plots[[plot_idx]] <- p  # Store plot in the list
      plot_idx <- plot_idx + 1
    }
  }
  
  # Arrange plots side by side
  if (length(plots) > 1) {
    grid.arrange(grobs = plots, ncol = length(plots))  # Using gridExtra
    # print(plots[[1]] + plots[[2]])  # Alternative using patchwork (uncomment if using patchwork)
  } else {
    print(plots[[1]])  # Just print a single plot if there's only one
  }
}

plot_power <- function(results_dir,runtag,simutags){
  pipfs_all_ctwas <- paste0(results_dir, runtag, "_simu",simutags,".thin1.shared_all.ctwas.Gtest.minp0.mingene0.estimated_parameter.finemap_regions_res.RDS")
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")

  cau <- lapply(phenofs, function(x) {load(x);get_causal_id(phenores)})
  df_all_ctwas <- NULL
  for (i in 1:length(pipfs_all_ctwas)) {
    res <- readRDS(pipfs_all_ctwas[i])
    res <- res$finemap_res
    res <- data.frame(res[res$type!="SNP", ])
    res$runtag <- i
    res$ifcausal <- ifelse(res$id %in% cau[[i]], 1, 0)
    df_all_ctwas <- rbind(df_all_ctwas, res)
  }

  breaks_ranges = rbind(c(0.5, 1), c(0.8,1))
  power_df <- data.frame()
  for(i in 1:nrow(breaks_ranges)){
    breaks = breaks_ranges[i,]
    n_all_ctwas = length(which(df_all_ctwas$susie_pip >= breaks[1] & df_all_ctwas$susie_pip < breaks[2]))
    n_all_ctwas_causal = length(which(df_all_ctwas$susie_pip >= breaks[1] & df_all_ctwas$susie_pip < breaks[2] & df_all_ctwas$ifcausal > 0))
    tmp_df <- data.frame(
      "pip_bin" = paste0("PIP: ", breaks[1], "-", breaks[2]),
      "method" = rep(c("ctwas shared all"), 2),
      "group" = rep(c("total", "causal"), each = 1),
      "n_var" = c(n_all_ctwas,n_all_ctwas_causal))
    power_df <- rbind(power_df, tmp_df)
  }
  power_df$method <- factor(power_df$method, levels = c("ctwas shared all"))
  ggplot(power_df) +
  geom_bar(aes(x = method, y = n_var, fill = group),
           position = "identity", stat = "identity", alpha=0.5, width=0.5) +
  facet_grid(~ pip_bin) +
  labs(x = "", y = "number of variables") +
  theme_cowplot()
}

check_power <- function(results_dir,runtag,simutags,screen_region){
  if(screen_region==TRUE){
    pipfs_all_ctwas <- paste0(results_dir, runtag, "_simu",simutags,".thin1.shared_all.ctwas.Gtest.minp0.mingene0.estimated_parameter.screened_region.finemap_regions_res.RDS")
  }
  else{
    pipfs_all_ctwas <- paste0(results_dir, runtag, "_simu",simutags,".thin1.shared_all.ctwas.Gtest.minp0.mingene0.estimated_parameter.finemap_regions_res.RDS")
  }
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")

  cau <- lapply(phenofs, function(x) {load(x);get_causal_id(phenores)})
  df_all_ctwas <- NULL
  for (i in 1:length(pipfs_all_ctwas)) {
    res <- readRDS(pipfs_all_ctwas[i])
    res <- res$finemap_res
    res <- res[res$susie_pip>0.8,]
    res <- data.frame(res[res$type!="SNP", ])
    causal_genes <- cau[[i]]
    causal_genes <- causal_genes[!grepl("^rs\\d+$", causal_genes)]
    df_all_ctwas <- rbind(df_all_ctwas,c(length(intersect(res$id,causal_genes)), length(causal_genes)))
  }
  return(df_all_ctwas)
}

plot_PIP_shared_all_ctwas <- function(results_dir, runtag,  simutags, ...){
  phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
  susieIfs <- paste0(results_dir, runtag, "_simu",simutags, ".thin1.shared_all.ctwas.Gtest.minp0.mingene0.estimated_parameter.finemap_regions_res.RDS")
  f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
  return(f1)
}
```
 
 
```{r}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(3, 1:10, sep = "-")
aa<-check_power(results_dir, runtag, simutags,screen_region = FALSE)
bb<-check_power(results_dir, runtag, simutags,screen_region = TRUE)
```
 
```{r}
f1 <- plot_PIP_shared_all_ctwas(results_dir, runtag, simutags, main = "ctwas shared all")
f1
```
 
## Enrichment=1 (two causal tissues)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(1, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- 0
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.0025
true_value_gene2 <- 0.0025
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 10.81125
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=10 (two causal tissues)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(2, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(10)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.025
true_value_gene2 <- 0.025
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 10.81125
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=20 (two causal tissues)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(3, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(20)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.05
true_value_gene2 <- 0.05
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 10.81125
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=40 (two causal tissues)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(4, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(40)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.1
true_value_gene2 <- 0.1
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 10.81125
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=80 (two causal tissues)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(5, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_all")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(80)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.2
true_value_gene2 <- 0.2
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=1 (one causal tissue)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(6, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(1)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.0025
true_value_gene2 <- 0
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=10 (one causal tissue)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(7, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(10)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.025
true_value_gene2 <- 0
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=20 (one causal tissue)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(8, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(20)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.05
true_value_gene2 <- 0
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=40 (one causal tissue)
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(9, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(40)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.1
true_value_gene2 <- 0
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

## Enrichment=80 (one causal tissue)
gene prior = 2.5e-3, snp prior = 2.5e-3, sigma_gene = 0.0215, sigma_snp = 0.0155, 7395 genes and 500000 SNPs
```{r,echo=FALSE,fig.width= 8, fig.height= 4}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_two_tissues_expression_enrichment/"
runtag = "two_tissues"
simutags <- paste(10, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene <- log(80)
file_name <- ".Gtest.minp0.mingene0.parameters.RDS"
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene)
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 0.2
true_value_gene2 <- 0
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,simutags,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 10, fig.height= 5}
true_value_gene1 <- 10.81125
true_value_gene2 <- 0
true_value_SNP <- 10.81125
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,file_name,true_value_gene1,true_value_gene2,true_value_SNP)
```