---
title: "Expression and Splicing from three tissues simulations"
author: "shengqian"
date: "2023-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

A simulation of expression and splicing traits from three tissues is conducted to evaluate cTWAS performance (parameter estimation, PIP calibration ...). Three tissues used in this simulation are Liver, Lung, Spleen.

It current has two setting:

* One tissue case: 3% PVE, 0.9% $\pi$ for E and S from Liver and 30% PVE, 2.5e-4 $\pi$ for SNP.
* 3% PVE, 0.9% $\pi$ for Liver E and Liver S. 0% PVE, 0% $\pi$ for the others and 30% PVE, 2.5e-4 $\pi$ for SNP.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ctwas)
library(data.table)
require(latex2exp)
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/summarize_ctwas_plots.R")
source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/analysis/simulation_help_functions.R")
plot_PIP <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".susieIrss.txt")
   f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_combined <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".susieIrss.txt")
   f1 <- caliPIP_plot_E_S_combined(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_L1 <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".L1.susieIrss.txt")
   f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_L1_combined <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".L1.susieIrss.txt")
   f1 <- caliPIP_plot_E_S_combined(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_true <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".true.susieIrss.txt")
   f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_true_combined <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".true.susieIrss.txt")
   f1 <- caliPIP_plot_E_S_combined(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_trueL1 <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".trueL1.susieIrss.txt")
   f1 <- caliPIP_plot(phenofs, susieIfs, ...) 
   return(f1)
}
plot_PIP_trueL1_combined <- function(configtag, runtag,  simutags, ...){
   phenofs <- paste0(results_dir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(results_dir, runtag, "_simu",simutags, "_config", configtag,"_LDR",".trueL1.susieIrss.txt")
   f1 <- caliPIP_plot_E_S_combined(phenofs, susieIfs, ...) 
   return(f1)
}
```

### Simulation 1: Expression and Splicing from Liver (3% PVE)

```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_E_S_one_tissue/"
runtag = "ukb-s80.45-3"
configtag <- 1

simutags <- paste(1, 1:5, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8

results_df <- get_sim_joint_res(results_dir,runtag,configtag,simutags,thin,sample_size,PIP_threshold)
group_size <- results_df[[2]]
results_df <- results_df[[1]]
```

### Results using PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)
```

### Estimated Prior Inclusion Probability
```{r, fig.width= 4, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_Liver_Expression
y2 <- results_df$prior_Liver_Splicing

truth <- rbind(c(1,0.009),c(2,0.009))
est <- rbind(cbind(1,y1),cbind(2,y2))
plot_par_2(truth,est,xlabels = c("Liver_E","Liver_S"),ylim=c(0,0.025),ylab="Prior inclusion")
```

### Estimated PVE
```{r, fig.width= 4, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver_Expression
y2 <- results_df$pve_Liver_Splicing

truth <- rbind(c(1,0.03),c(2,0.03))
est <- rbind(cbind(1,y1),cbind(2,y2))
plot_par_2(truth,est,xlabels = c("Liver_E","Liver_S"),ylim=c(0,0.1),ylab="PVE")
```

### Estimated Prior Variance
```{r, fig.width= 4, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_var_Liver_Expression
y2 <- results_df$prior_var_Liver_Splicing

t1 <- 0.03*sample_size/(group_size[2]*0.009)
t2 <- 0.03*sample_size/(group_size[3]*0.009)

truth <- rbind(c(1,t1),c(2,t2))
est <- rbind(cbind(1,y1),cbind(2,y2))
plot_par_2(truth,est,xlabels = c("Liver_E","Liver_S"),ylim=c(0,80),ylab=TeX("$sigma^2$"))
```

### Estimated Enrichment
```{r, fig.width= 4, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver_Expression/results_df$prior_SNP
y2 <- results_df$pve_Liver_Splicing/results_df$prior_SNP

truth <- rbind(c(1,120),c(2,120))
est <- rbind(cbind(1,y1),cbind(2,y2))
plot_par_2(truth,est,xlabels = c("Liver_E","Liver_S"),ylim=c(0,300),ylab= TeX("Enrichment $\\pi_G/\\pi_V$"))
```

### PIP Calibration Plot
```{r, fig.width= 4, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
f1 <- plot_PIP(configtag, runtag, paste(1, 1:5, sep = "-"), main = "")
f1
```

### Simulation 2: Expression and Splicing traits from Liver are causal(3% PVE).  

```{r echo=FALSE}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_E_S_three_tissues/"
runtag = "ukb-s80.45"
configtag <- 1

simutags <- paste(5, 1:5, sep = "-")
thin <- 0.1

sample_size <- 45000
PIP_threshold <- 0.8

results_df <- get_sim_joint_res(results_dir,runtag,configtag,simutags,thin,sample_size,PIP_threshold)
group_size <- results_df[[2]]
results_df <- results_df[[1]]
```

### Results using PIP Threshold
```{r echo=FALSE}
results_df[,c("simutag", "n_causal", "n_detected_pip", "n_detected_pip_in_causal")]
#mean percent causal using combined PIP > 0.8
sum(results_df$n_detected_pip_in_causal)/sum(results_df$n_detected_pip)
```

### Estimated Prior Inclusion Probability
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_Liver_Expression
y2 <- results_df$prior_Liver_Splicing
y3 <- results_df$prior_Lung_Expression
y4 <- results_df$prior_Lung_Splicing
y5 <- results_df$prior_Spleen_Expression
y6 <- results_df$prior_Spleen_Splicing

truth <- rbind(c(1,0.009),c(2,0.009),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver_E","Liver_S","Lung_E","Lung_S","Spleen_E","Spleen_S"),ylim=c(0,0.025),ylab="Prior inclusion")
```

### Estimated PVE
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver_Expression
y2 <- results_df$pve_Liver_Splicing
y3 <- results_df$pve_Lung_Expression
y4 <- results_df$pve_Lung_Splicing
y5 <- results_df$pve_Spleen_Expression
y6 <- results_df$pve_Spleen_Splicing

truth <- rbind(c(1,0.03),c(2,0.03),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver_E","Liver_S","Lung_E","Lung_S","Spleen_E","Spleen_S"),ylim=c(0,0.06),ylab="PVE")
```

### Estimated Prior Variance
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$prior_var_Liver_Expression
y2 <- results_df$prior_var_Liver_Splicing
y3 <- results_df$prior_var_Lung_Expression
y4 <- results_df$prior_var_Lung_Splicing
y5 <- results_df$prior_var_Spleen_Expression
y6 <- results_df$prior_var_Spleen_Splicing

t1 <- 0.03*sample_size/(group_size[2]*0.009)
t2 <- 0.03*sample_size/(group_size[3]*0.009)
t3 <- 0
t4 <- 0
t5 <- 0
t6 <- 0

truth <- rbind(c(1,t1),c(2,t2),c(3,t3),c(4,t4),c(5,t5),c(6,t6))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver_E","Liver_S","Lung_E","Lung_S","Spleen_E","Spleen_S"),ylim=c(0,30),ylab=TeX("$sigma^2$"))
```

### Estimated Enrichment
```{r, fig.width= 8, fig.height= 5, message=FALSE, warning=FALSE, echo=FALSE}
y1 <- results_df$pve_Liver_Expression/results_df$prior_SNP
y2 <- results_df$pve_Liver_Splicing/results_df$prior_SNP
y3 <- results_df$pve_Lung_Expression/results_df$prior_SNP
y4 <- results_df$pve_Lung_Splicing/results_df$prior_SNP
y5 <- results_df$pve_Spleen_Expression/results_df$prior_SNP
y6 <- results_df$pve_Spleen_Splicing/results_df$prior_SNP

truth <- rbind(c(1,120),c(2,120),c(3,0),c(4,0),c(5,0),c(6,0))
est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4),cbind(5,y5),cbind(6,y6))
plot_par_6(truth,est,xlabels = c("Liver_E","Liver_S","Lung_E","Lung_S","Spleen_E","Spleen_S"),ylim=c(0,250),ylab= TeX("Enrichment $\\pi_G/\\pi_V$"))
```

### PIP Calibration Plot
```{r, fig.width= 4, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
f1 <- plot_PIP(configtag, runtag, paste(5, 1:5, sep = "-"), main = "")
f1
```

### PIP Calibration Plot (L1=1)
```{r, fig.width= 4, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
f1 <- plot_PIP_L1(configtag, runtag, paste(5, 1:5, sep = "-"), main = "")
f1
```

### PIP Calibration Plot (True parameters)
```{r, fig.width= 4, fig.height= 4, message=FALSE, warning=FALSE, echo=FALSE}
f1 <- plot_PIP_true(configtag, runtag, paste(5, 1:5, sep = "-"), main = "")
f1
```

### PIP Calibration Plot
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
load("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mashr_sqtl/sqtl/mashr/intron_mapping.RData")
f1 <- plot_PIP(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot (cs_index!=0)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
load("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/mashr_sqtl/sqtl/mashr/intron_mapping.RData")
f1 <- plot_PIP_csindex(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_combined_csindex(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot (L1=1)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_L1(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_L1_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot (True parameters)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_true(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_true_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```

### PIP Calibration Plot (True parameters, L=1)
```{r, fig.width= 8, fig.height= 4, echo=FALSE, warning=FALSE}
f1 <- plot_PIP_trueL1(configtag, runtag, simutags, main = "Expression Trait PIP Calibration")
f2 <-  plot_PIP_trueL1_combined(configtag, runtag, simutags, main = "Gene PIP Calibration")
gridExtra::grid.arrange(f1, f2, ncol =2)
```