---
title: "simulation_summary"
output: html_document
date: '2024-2-13'
editor_options: 
  chunk_output_type: console
---

## One tissue simulation
```{r}
library(ctwas)
library(tidyr)
library(dplyr)
library(ggplot2)
library(data.table)
library(ggbreak) 
library(ggpubr)
library(gridExtra)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")

plot_prior_inclusion <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      y1 <- param_df_ctwas$`prior_Liver|expression`
      y2 <- param_df_ctwas$prior_SNP
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")
      y3 <- param_df_susie$`prior_Liver|expression`
      y4 <- param_df_susie$prior_SNP
      truth <- rbind(c(1,true_value_gene),c(2,true_value_gene),c(3,true_value_gene),c(4,true_value_SNP))
      est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
      plot_par_4(truth,est,xlabels = c("Liver (ctwas)", "SNP (ctwas)", "Liver (susie)","SNP (susie)"),ylim=c(0,max(est[,2],truth[,2])),ylab="Prior inclusion", main=group_prior_var_structure)
    }
  }
}

plot_prior_variance <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      y1 <- param_df_ctwas$`prior_var_Liver|expression`
      y2 <- param_df_ctwas$prior_var_SNP
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")
      y3 <- param_df_susie$`prior_var_Liver|expression`
      y4 <- param_df_susie$prior_var_SNP
      truth <- rbind(c(1,true_value_gene),c(2,true_value_SNP),c(3,true_value_gene),c(4,true_value_SNP))
      est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
      plot_par_4(truth,est,xlabels = c("Liver (ctwas)", "SNP (ctwas)", "Liver (susie)","SNP (susie)"),ylim=c(0,max(est[,2],truth[,2])),ylab="Prior variance", main=group_prior_var_structure)
    }
  }
}

plot_pve <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      y1 <- param_df_ctwas$`pve_Liver|expression`
      y2 <- param_df_ctwas$pve_SNP
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")
      y3 <- param_df_susie$`pve_Liver|expression`
      y4 <- param_df_susie$pve_SNP
      truth <- rbind(c(1,true_value_gene),c(2,true_value_SNP),c(3,true_value_gene),c(4,true_value_SNP))
      est <- rbind(cbind(1,y1),cbind(2,y2),cbind(3,y3),cbind(4,y4))
      plot_par_4(truth,est,xlabels = c("Liver (ctwas)", "SNP (ctwas)", "Liver (susie)","SNP (susie)"),ylim=c(0,max(est[,2],truth[,2])),ylab="PVE", main=group_prior_var_structure)
    }
  }
}

plot_enrichment <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      y1 <- param_df_ctwas$`enrichment_Liver|expression`
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")
      y2 <- param_df_susie$`enrichment_Liver|expression`
      truth <- rbind(c(1,log2(true_value_gene)),c(2,log2(true_value_gene)))
      est <- rbind(cbind(1,y1),cbind(2,y2))
      plot_par_2(truth,est,xlabels = c("Liver (ctwas)","Liver (susie)"),ylim=c(min(est[,2],truth[,2]),max(est[,2],truth[,2])),ylab="log(Enrichment)", main=group_prior_var_structure)
    }
  }
}

plot_enrichment <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,enrichment_true){
  par(mfrow = c(1, 2))
  for(group_prior_var_structure in group_prior_var_structures){
    for(thin in thins){
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")
      df <- data.frame(null_method = rep(c("ctwas", "susie"), each = 10),
                       pos = c(rep(1, 10), rep(2, 10)),
                       enrichment = c(param_df_ctwas$`enrichment_Liver|expression`, param_df_susie$`enrichment_Liver|expression`),
                       se = c(param_df_ctwas$`enrichment_se_Liver|expression`, param_df_ctwas$`enrichment_se_Liver|expression`))
      df$pos <- jitter(df$pos, amount = 0.2)
      ggplot(df, aes(x=pos, y=enrichment, group = null_method, color=null_method)) + 
      geom_point()+
      geom_errorbar(aes(ymin=enrichment-1.96*se, ymax=enrichment+1.96*se), width=0.01) + 
      geom_hline(yintercept=enrichment_true, linetype="dashed", color = "blue") + 
      ylim(min(c(y1,y2))-1, max(c(y1,y2))+1) +
      labs(x = "", y = "log(Enrichment)", title = "Enrichment") +
      scale_x_continuous(breaks = c(1:2), 
                     labels = c("Liver (ctwas)","Liver (susie)")) +theme_minimal()
    }
  }
}


plot_enrichment <- function(results_dir, runtag, thins, group_prior_var_structures, null_methods, enrichment_true) {
  plots <- list()  # Store plots in a list
  plot_idx <- 1
  
  for (group_prior_var_structure in group_prior_var_structures) {
    for (thin in thins) {
      param_df_ctwas <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "ctwas")
      param_df_susie <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, "susie")

      df <- data.frame(null_method = rep(c("ctwas", "susie"), each = 10),
                       pos = c(rep(1, 10), rep(2, 10)),
                       enrichment = c(param_df_ctwas$`enrichment_Liver|expression`, param_df_susie$`enrichment_Liver|expression`),
                       se = c(param_df_ctwas$`enrichment_se_Liver|expression`, param_df_susie$`enrichment_se_Liver|expression`))  # Fix repeated `se` values
      
      df$pos <- jitter(df$pos, amount = 0.2)
      
      p <- ggplot(df, aes(x = pos, y = enrichment, group = null_method, color = null_method)) +
        geom_point() +
        geom_errorbar(aes(ymin = enrichment - 1.96 * se, ymax = enrichment + 1.96 * se), width = 0.01) +
        geom_hline(yintercept = enrichment_true, linetype = "dashed", color = "blue") +
        labs(x = "", y = "log(Enrichment)", title = paste("Enrichment -", group_prior_var_structure, "Thin =", thin)) +
        scale_x_continuous(breaks = c(1, 2), labels = c("Liver (ctwas)", "Liver (susie)")) +
        theme_minimal()
      
      plots[[plot_idx]] <- p  # Store plot in the list
      plot_idx <- plot_idx + 1
    }
  }
  
  # Arrange plots side by side
  if (length(plots) > 1) {
    grid.arrange(grobs = plots, ncol = length(plots))  # Using gridExtra
    # print(plots[[1]] + plots[[2]])  # Alternative using patchwork (uncomment if using patchwork)
  } else {
    print(plots[[1]])  # Just print a single plot if there's only one
  }
}
```

## Enrichment=1 (same variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(1, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0025
true_value_SNP <- 0.0025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 20
true_value_SNP <- 20
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00042
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=1 (same variance=20)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(10, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.000125
true_value_SNP <- 0.000125
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 10
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00042
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=1 (same variance=40)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(11, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0000625
true_value_SNP <- 0.0000625
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
true_value_SNP <- 40
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00042
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=1 (gene variance=20, snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(12, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00025
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 20
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00084
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=1 (gene variance=40, snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(13, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00025
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00168
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=1 (gene variance=80, snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(14, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00025
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 80
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.00336
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 1
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=10 (same variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(2, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0025
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 10
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0042
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 10
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (same variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(3, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.01
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 10
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0168
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (same variance=20)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(5, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.005
true_value_SNP <- 0.000125
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 20
true_value_SNP <- 20
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0168
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (same variance=40)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(6, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0025
true_value_SNP <- 0.0000625
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
true_value_SNP <- 40
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0168
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (gene variance=20,snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(7, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.01
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 20
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0336
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (gene variance=40, snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(8, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.01
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0672
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=40 (gene variance=80, snp variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(9, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.01
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 80
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.1344
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```

## Enrichment=80 (same variance=10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_one_tissue/"
runtag = "one_tissue"
simutags <- paste(4, 1:10, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```

### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.02
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 10
true_value_SNP <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0336
true_value_SNP <- 0.3
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene, true_value_SNP)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 80
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene)
```


```{r, echo=FALSE, message=FALSE}
library(ctwas)
library(tidyr)
library(dplyr)
library(ggplot2)
library(data.table)
library(ggbreak) 
library(ggpubr)
source("/project/xinhe/shengqian/cTWAS_simulation/code/simulation_help_functions.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_basic_plots.R")
source("/project/xinhe/shengqian/cTWAS_simulation/code/summarize_ctwas_plots.R")

plot_prior_inclusion <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP){
  par(mfrow = c(2, 2))
  for(null_method in null_methods){
    for(group_prior_var_structure in group_prior_var_structures){
      for(thin in thins){
        param_df <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, null_method)
        y1 <- param_df$`prior_Liver|eQTL`
        y2 <- param_df$`prior_Adipose_Subcutaneous|eQTL`
        y3 <- param_df$`prior_Lung|eQTL`
        y4 <- param_df$`prior_Stomach|eQTL`
        y5 <- param_df$prior_SNP
        truth <- rbind(c(1,true_value_gene),c(2,true_value_gene),c(3,0),c(4,0),c(5,true_value_SNP))
        est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4), cbind(5,y5))
        plot_par_5(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach", "SNP"),ylim=c(0,max(est[,2],truth[,2])),ylab="Prior inclusion", main=paste0("thin",thin,",",group_prior_var_structure,",",null_method))
      }
    }
  }
}

plot_prior_variance <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value){
  par(mfrow = c(2, 2))
  for(null_method in null_methods){
    for(group_prior_var_structure in group_prior_var_structures){
      for(thin in thins){
        param_df <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, null_method)
        y1 <- param_df$`prior_var_Liver|eQTL`
        y2 <- param_df$`prior_var_Adipose_Subcutaneous|eQTL`
        y3 <- param_df$`prior_var_Lung|eQTL`
        y4 <- param_df$`prior_var_Stomach|eQTL`
        truth <- rbind(c(1,true_value),c(2,true_value),c(3,0),c(4,0))
        est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
        plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,max(est[,2])),ylab="Prior variance", main=paste0("thin",thin,",",group_prior_var_structure,",",null_method))
      }
    }
  }
}

plot_pve <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value){
  par(mfrow = c(2, 2))
  for(null_method in null_methods){
    for(group_prior_var_structure in group_prior_var_structures){
      for(thin in thins){
        param_df <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, null_method)
        y1 <- param_df$`pve_Liver|eQTL`
        y2 <- param_df$`pve_Adipose_Subcutaneous|eQTL`
        y3 <- param_df$`pve_Lung|eQTL`
        y4 <- param_df$`pve_Stomach|eQTL`
        truth <- rbind(c(1,true_value),c(2,true_value),c(3,0),c(4,0))
        est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
        plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,max(est[,2])),ylab="PVE", main=paste0("thin",thin,",",group_prior_var_structure,",",null_method))
      }
    }
  }
}

plot_enrichment <- function(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value){
  par(mfrow = c(2, 2))
  for(null_method in null_methods){
    for(group_prior_var_structure in group_prior_var_structures){
      for(thin in thins){
        param_df <- load_parameters(results_dir, runtag, simutags, thin, group_prior_var_structure, null_method)
        y1 <- param_df$`enrichment_Liver|eQTL`
        y2 <- param_df$`enrichment_Adipose_Subcutaneous|eQTL`
        y3 <- param_df$`enrichment_Lung|eQTL`
        y4 <- param_df$`enrichment_Stomach|eQTL`
        truth <- rbind(c(1,true_value),c(2,true_value),c(3,0),c(4,0))
        est <- rbind(cbind(1,y1),cbind(2,y2), cbind(3,y3), cbind(4,y4))
        plot_par_4(truth,est,xlabels = c("Liver", "Adipose", "Lung", "Stomach"),ylim=c(0,max(est[,2])),ylab="Enrichment", main=paste0("thin",thin,",",group_prior_var_structure,",",null_method))
      }
    }
  }
}
```

## Enrichment=10
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(1, 1:5, sep = "-")
thins <- c(1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value_gene <- 0.0025
true_value_SNP <- 0.00025
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value_gene,true_value_SNP)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.005
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 10
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

## Enrichment=40
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(2, 1:5, sep = "-")
thins <- c(0.1,1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.01
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.02
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

## Enrichment=80
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(3, 1:5, sep = "-")
thins <- c(0.1,1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.02
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 10
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.04
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 80
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

## Enrichment=80
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(4, 1:5, sep = "-")
thins <- c(0.1,1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.01
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 20
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.04
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 80
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

## Enrichment=40 (gene variance 20, snp variance 10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(5, 1:5, sep = "-")
thins <- c(0.1,1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.01
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 20
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.04
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 40
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

## Enrichment=40 (gene variance 30, snp variance 10)
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
results_dir <- "/project/xinhe/shengqian/cTWAS_simulation/simulation_four_tissues_expression/"
runtag = "four_tissues"
simutags <- paste(6, 1:5, sep = "-")
thins <- c(0.1,1)
group_prior_var_structures <- c("shared_all","shared_type")
null_methods <- c("ctwas","susie")
```
### Prior Inclusion Probability
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.01
plot_prior_inclusion(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Prior Variance
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 30
plot_prior_variance(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### PVE
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 0.04
plot_pve(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```

### Enrichment
```{r,echo=FALSE,fig.width= 8, fig.height= 8}
true_value <- 80
plot_enrichment(results_dir,runtag,thins,group_prior_var_structures,null_methods,true_value)
```