 ---
title: "6 Traits, 5 tissues, eQTL + sQTL + stQTL – compute ukbb LD, eqtl, sqtl from predictdb; stQTL from Munro et al; post-processing"
author: "XSun"
date: "2024-12-09"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

We compare post-processed results with the original results: https://sq-96.github.io/multigroup_ctwas_analysis/multi_group_6traits_15weights_ess.html

The post-processing steps include the following:

1. **Region Merging**  

   For the regions with `susie_pip > 0.5` 
   
2. **LD Mismatch Fixing**

-   Regions were selected where nonSNP_PIP > 0.5.
-   For genes with `susie_pip > thresholds` (0.5 and 0.2), we performed LD mismatch diagnosis.
-   To address LD mismatches, two strategies were employed:
    -   Fine-mapping the region without LD.
    -   Removing mismatched SNPs, updating gene Z-scores, and re-fine-mapping with LD.
```{r message=FALSE, warning=FALSE}
library(ctwas)
library(EnsDb.Hsapiens.v86)
library(ggplot2)
library(gridExtra)
library(dplyr)

ens_db <- EnsDb.Hsapiens.v86

mapping_predictdb <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/PredictDB_mapping.RDS")
mapping_munro <- readRDS("/project2/xinhe/shared_data/multigroup_ctwas/weights/mapping_files/Munro_mapping.RDS")
mapping_two <- rbind(mapping_predictdb,mapping_munro)
# 
# 
# compute_pip_per_cs <- function(combined_data, susie_data) {
#   # Initialize an empty list to store results
#   details <- list()
#   
#   # Iterate over each unique gene name in the combined data
#   unique_genes <- unique(combined_data$gene_name)
#   
#   for (genename in unique_genes) {
#     # dplyr::filter susie data for the current gene
#     susie_alpha_res_multi_per_gene <- susie_data %>%
#       dplyr::filter(gene_name == genename)
#     
#     # Get all unique credible sets for the current gene
#     cs_all <- unique(susie_alpha_res_multi_per_gene$susie_set[susie_alpha_res_multi_per_gene$in_cs])
#     
#     if (length(cs_all) > 1) {
#       # dplyr::filter complete cases and those in credible sets
#       susie_alpha_res_multi_per_gene <- susie_alpha_res_multi_per_gene %>%
#         dplyr::filter(complete.cases(cs), in_cs)
#       
#       # Summarize the data
#       summed_alpha_with_details <- susie_alpha_res_multi_per_gene %>%
#         group_by(susie_set) %>%
#         summarise(
#           total_susie_alpha = round(sum(susie_alpha, na.rm = TRUE), digits = 3),
#           num_molecular_traits = n(),
#           ids_pip = paste0(id, "(", round(susie_alpha, digits = 3), ")", collapse = ", ")
#         )
#       
#       # Add gene name to the summarized data
#       summed_alpha_with_details$gene_name <- genename
#       
#       # Append the result to the details list
#       details[[length(details) + 1]] <- summed_alpha_with_details
#     }
#   }
#   
#   # Combine all results into a single data frame
#   final_details <- bind_rows(details)
#   
#   if(nrow(final_details) > 0){
#     final_details <- final_details[,c("gene_name","susie_set","total_susie_alpha","num_molecular_traits","ids_pip")]
#     colnames(final_details) <- c("gene_name","CS","total_PIP_CS","num_molecular_traits_CS","ids_pip_CS")
#   }
#   
#   
#   return(final_details)
# }

```


# aFib-ebi-a-GCST006414

```{r message=FALSE, warning=FALSE}
trait <- "aFib-ebi-a-GCST006414"

results_dir_origin <- paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/results/",trait,"/")
ctwas_res_origin <- readRDS(paste0(results_dir_origin,trait,".ctwas.res.RDS"))

finemap_res_origin <- ctwas_res_origin$finemap_res
```

## Region merge. 

```{r message=FALSE, warning=FALSE}

load(paste0("/project/xinhe/xsun/multi_group_ctwas/11.multi_group_1008/post_process_rm_ld/rm_",trait,".rdata"))

finemap_res_rm <- res_regionmerge$finemap_res
finemap_res_rm_boundary_genes <- finemap_res_rm[finemap_res_rm$id %in%selected_boundary_genes$id,]
finemap_res_rm_boundary_genes_pip <- finemap_res_rm_boundary_genes[,c("id","susie_pip","cs")]


finemap_res_origin_boundary_genes <- finemap_res_origin[finemap_res_origin$id %in%selected_boundary_genes$id,]
finemap_res_origin_boundary_genes_pip <- finemap_res_origin_boundary_genes[,c("id","susie_pip","cs")]

finemap_res_compare_regionmerge <- merge(finemap_res_origin_boundary_genes_pip,finemap_res_rm_boundary_genes_pip, by = "id")
colnames(finemap_res_compare_regionmerge) <- c("id","susie_pip_origin","cs_origin","susie_pip_reginmerge","cs_reginmerge")

DT::datatable(finemap_res_compare_regionmerge,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','Selected boundary genes (susie_pip > 0.5)'),options = list(pageLength = 10) )
```


