---
title: "Deciding matching tissue -- extra tissue contribution"
author: "XSun"
date: "2024-11-27"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---

# Introduction

- For each trait, we select some baseline tissues that well known related to the trait. 
- Take the rest of tissues with sample size >=200, one at a time, as extra tissue and run multi-tissue eQTL ctwas. 
- Evaluate the percent of h2g in the extra tissue, conditioned on the known ones. 

```{r message=F, warning=F}
library(ctwas)
library(dplyr)

load("/project2/xinhe/shared_data/multigroup_ctwas/gwas/samplesize.rdata")

```

# IBD-ebi-a-GCST004131

## Round 1 -- baseline_tissue : Whole_Blood,Colon_Sigmoid,Colon_Transverse

```{r message=F, warning=F}

trait <- "IBD-ebi-a-GCST004131"
baseline_tissue <- c("Whole_Blood","Colon_Sigmoid","Colon_Transverse")


gwas_n <- samplesize[trait]

result_dir <- paste0("/project/xinhe/xsun/multi_group_ctwas/12.tissue_selection/results/", trait, "/")

extra_tissue <- list.files(path = result_dir)
extra_tissue <- extra_tissue[-which(extra_tissue == "baseline")]

all <- c()
for (tissue in c("baseline",extra_tissue)) {
  
  para_file <- paste0(result_dir,tissue,"/",trait,"_",tissue,".param.RDS")
  param <- readRDS(para_file)
  
  ctwas_parameters <- summarize_param(param, gwas_n)
  
  if(tissue == "baseline") {
    
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g_baseline <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g_baseline,NA,prob_h2g,total_pve,NA)
  }else {
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    nonSNP_prob_h2g_gain <- total_nonSNP_prob_h2g - total_nonSNP_prob_h2g_baseline
    
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue,tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g,nonSNP_prob_h2g_gain,prob_h2g,total_pve,NA)
    
  }
  
  all <- rbind(all,h2g_v_tissue)
  
}


colnames(all) <- c("extra_tissue","total_nonSNP_prob_h2g(%)","nonSNP_prob_h2g_gain(%)",paste0("%h2g_",c(baseline_tissue)),"%h2g_extra_tissue","pve_gain")
all <- as.data.frame(all)

all <- all %>%
  dplyr::mutate(across(where(is.character), ~ as.numeric(.x))) %>%  # Convert character columns to numeric
  dplyr::mutate(across(where(is.numeric), ~ round(.x, digits = 4))) # Round numeric columns

all$extra_tissue <- c("baseline",extra_tissue)
rownames(all) <- seq(1:nrow(all))

DT::datatable(all,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','PVE change after adding extra tissue'),options = list(pageLength = 10) )
```








## Round 2 -- baseline_tissue : Whole_Blood,Colon_Sigmoid,Colon_Transverse,Artery_Coronary

```{r message=F, warning=F}

trait <- "IBD-ebi-a-GCST004131"
baseline_tissue <- c("Whole_Blood","Colon_Sigmoid","Colon_Transverse","Artery_Coronary")

gwas_n <- samplesize[trait]

result_dir <- paste0("/project/xinhe/xsun/multi_group_ctwas/12.tissue_selection/results/", trait,"_round2", "/")

extra_tissue <- list.files(path = result_dir)
extra_tissue <- extra_tissue[-which(extra_tissue == "baseline")]

all <- c()
for (tissue in c("baseline",extra_tissue)) {
  
  para_file <- paste0(result_dir,tissue,"/",trait,"_",tissue,".param.RDS")
  param <- readRDS(para_file)
  
  ctwas_parameters <- summarize_param(param, gwas_n)
  
  if(tissue == "baseline") {
    
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g_baseline <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g_baseline,NA,prob_h2g,total_pve,NA)
  }else {
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    nonSNP_prob_h2g_gain <- total_nonSNP_prob_h2g - total_nonSNP_prob_h2g_baseline
    
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue,tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g,nonSNP_prob_h2g_gain,prob_h2g,total_pve,NA)
    
  }
  
  all <- rbind(all,h2g_v_tissue)
  
}


colnames(all) <- c("extra_tissue","total_nonSNP_prob_h2g(%)","nonSNP_prob_h2g_gain(%)",paste0("%h2g_",c(baseline_tissue)),"%h2g_extra_tissue","pve_gain")
all <- as.data.frame(all)

all <- all %>%
  dplyr::mutate(across(where(is.character), ~ as.numeric(.x))) %>%  # Convert character columns to numeric
  dplyr::mutate(across(where(is.numeric), ~ round(.x, digits = 4))) # Round numeric columns

all$extra_tissue <- c("baseline",extra_tissue)
rownames(all) <- seq(1:nrow(all))

DT::datatable(all,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','PVE change after adding extra tissue'),options = list(pageLength = 10) )
```







## Round 3 -- baseline_tissue : Whole_Blood,Colon_Sigmoid,Colon_Transverse,Artery_Coronary,Heart_Left_Ventricle

```{r message=F, warning=F}

trait <- "IBD-ebi-a-GCST004131"
baseline_tissue <- c("Whole_Blood","Colon_Sigmoid","Colon_Transverse","Artery_Coronary","Heart_Left_Ventricle")

gwas_n <- samplesize[trait]

result_dir <- paste0("/project/xinhe/xsun/multi_group_ctwas/12.tissue_selection/results/", trait,"_round3", "/")

extra_tissue <- list.files(path = result_dir)
extra_tissue <- extra_tissue[-which(extra_tissue == "baseline")]

all <- c()
for (tissue in c("baseline",extra_tissue)) {
  
  para_file <- paste0(result_dir,tissue,"/",trait,"_",tissue,".param.RDS")
  param <- readRDS(para_file)
  
  ctwas_parameters <- summarize_param(param, gwas_n)
  
  if(tissue == "baseline") {
    
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g_baseline <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g_baseline,NA,prob_h2g,total_pve,NA)
  }else {
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    nonSNP_prob_h2g_gain <- total_nonSNP_prob_h2g - total_nonSNP_prob_h2g_baseline
    
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue,tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g,nonSNP_prob_h2g_gain,prob_h2g,total_pve,NA)
    
  }
  
  all <- rbind(all,h2g_v_tissue)
  
}


colnames(all) <- c("extra_tissue","total_nonSNP_prob_h2g(%)","nonSNP_prob_h2g_gain(%)",paste0("%h2g_",c(baseline_tissue)),"%h2g_extra_tissue","pve_gain")
all <- as.data.frame(all)

all <- all %>%
  dplyr::mutate(across(where(is.character), ~ as.numeric(.x))) %>%  # Convert character columns to numeric
  dplyr::mutate(across(where(is.numeric), ~ round(.x, digits = 4))) # Round numeric columns

all$extra_tissue <- c("baseline",extra_tissue)
rownames(all) <- seq(1:nrow(all))

DT::datatable(all,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','PVE change after adding extra tissue'),options = list(pageLength = 10) )
```







## Round 4 -- baseline_tissue : Whole_Blood,Colon_Sigmoid,Colon_Transverse,Artery_Coronary,Heart_Left_Ventricle,Cells_Cultured_fibroblasts

```{r message=F, warning=F}

trait <- "IBD-ebi-a-GCST004131"
baseline_tissue <- c("Whole_Blood","Colon_Sigmoid","Colon_Transverse","Artery_Coronary","Heart_Left_Ventricle","Cells_Cultured_fibroblasts")

gwas_n <- samplesize[trait]

result_dir <- paste0("/project/xinhe/xsun/multi_group_ctwas/12.tissue_selection/results/", trait,"_round4", "/")

extra_tissue <- list.files(path = result_dir)
extra_tissue <- extra_tissue[-which(extra_tissue == "baseline")]

all <- c()
for (tissue in c("baseline",extra_tissue)) {
  
  para_file <- paste0(result_dir,tissue,"/",trait,"_",tissue,".param.RDS")
  param <- readRDS(para_file)
  
  ctwas_parameters <- summarize_param(param, gwas_n)
  
  if(tissue == "baseline") {
    
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g_baseline <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g_baseline,NA,prob_h2g,total_pve,NA)
  }else {
    total_pve <- ctwas_parameters$total_pve
    
    total_nonSNP_prob_h2g <- (1- ctwas_parameters$prop_heritability["SNP"])*100
    nonSNP_prob_h2g_gain <- total_nonSNP_prob_h2g - total_nonSNP_prob_h2g_baseline
    
    
    prob_h2g <- round(as.numeric(ctwas_parameters$prop_heritability[paste0(c(baseline_tissue,tissue),"|eQTL")]*100),digits = 4)
    
    h2g_v_tissue <- c(tissue, total_nonSNP_prob_h2g,nonSNP_prob_h2g_gain,prob_h2g,total_pve,NA)
    
  }
  
  all <- rbind(all,h2g_v_tissue)
  
}


colnames(all) <- c("extra_tissue","total_nonSNP_prob_h2g(%)","nonSNP_prob_h2g_gain(%)",paste0("%h2g_",c(baseline_tissue)),"%h2g_extra_tissue","pve_gain")
all <- as.data.frame(all)

all <- all %>%
  dplyr::mutate(across(where(is.character), ~ as.numeric(.x))) %>%  # Convert character columns to numeric
  dplyr::mutate(across(where(is.numeric), ~ round(.x, digits = 4))) # Round numeric columns

all$extra_tissue <- c("baseline",extra_tissue)
rownames(all) <- seq(1:nrow(all))

DT::datatable(all,caption = htmltools::tags$caption( style = 'caption-side: left; text-align: left; color:black;  font-size:150% ;','PVE change after adding extra tissue'),options = list(pageLength = 10) )
```





